### 2017-12-24 paper.tex
First commit

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\usepackage{bm}
\usepackage{float}
\usepackage{subfig}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{array}
\usepackage[export]{adjustbox}
\usepackage{lineno,hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{graphicx}
\modulolinenumbers[5]
\usepackage[margin=1.5in]{geometry}
\journal{Journal of \LaTeX\ Templates}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Accelerated Magnetic Resonance Imaging by Adversarial Neural Network}

%% Group authors per affiliation:
\author{Ohad Shitrit, Tammy Riklin Raviv}
\address{$^1$Department of Electrical Engineering, 
	     $^2$The Zlotowski Center for Neuroscience
	     Ben-Gurion University of the Negev, Israel}

\begin{abstract}
A main challenge in Magnetic Resonance Imaging (MRI) for clinical
applications is speeding up scan time. Beyond the improvement of patient
experience and the reduction of operational costs, faster scans are
essential for time-sensitive imaging, where target movement is unavoidable,
yet must be significantly lessened, e.g., fetal MRI, cardiac cine,
and lungs imaging. Moreover, short scan time can enhance temporal
resolution in dynamic scans, such as functional MRI or dynamic contrast
enhanced MRI. Current imaging methods facilitate MRI acquisition at
the price of lower spatial resolution and costly hardware solutions.

We introduce a practical, software-only framework, based on deep learning,
for accelerating MRI scan time allows maintaining good quality imaging.
This is accomplished by partial MRI sampling, while using an adversarial
neural network to estimate the missing samples. The inter-play between
the generator and the discriminator networks enables the introduction
of an adversarial cost in addition to a fidelity loss used for optimizing
the peak signal-to-noise ratio (PSNR). Promising image reconstruction
results are obtained for 1.5T MRI where only 52\% of the original
data are used. 
\end{abstract}

\begin{keyword}
\texttt MRI \sep GAN \sep Imaging
%\MSC[2010] 00-01\sep  99-00
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}
Magnetic Resonance Imaging (MRI) is a non-ionizing imaging modality,
and is therefore widely used in diagnostic medicine and biomedical
research. The physical principles of MRI are based on a strong magnetic
field and pulses of radio frequency (RF) electromagnetic radiation.
Images are produced when hydrogen atoms, which are prevalent in living
organisms, emit the absorbed RF energy that is then received by antennas
in close proximity to the anatomy being examined. Spatial localization
of the detected MRI signals is obtained by varying the magnetic field
gradients. The discretized RF output is presented in a Fourier space
(called K-space), where the x-axis is refers to the frequency and
the y-axis to the phase. An inverse fast Fourier transform (IFFT)
of the K-space is then used for generating anatomically meaningful
MRI scans. Figure \ref{fig:pair_of_k_space_mri} presents K-space
traversal patterns used in conventional imaging. Each row of the k-space
is acquired after one RF excitation pulse. The number of rows multiplied
by the number of slices (z-axis) determines the total scan time.

The duration of standard single structural MRI acquisition is approximately
5 minutes. Usually, several scans of different modalities or a sequence
of scans are acquired such that the overall scan time is much longer.
Lengthy imaging process reduces patient comfort and is more vulnerable
to motion artifacts. In cases where motion is inevitable, e.g., fetal
MRI, cardiac cine, and lungs imaging, scan time must be significantly
shortened, otherwise the produced images might be useless. Moreover,
in dynamic MRI sequences, acquisition must be brief such that the
temporal resolution of the sequence would allow capturing significant
temporal changes, e.g., instantaneous increment of the contrast-enhanced
material concentration in DCE-MRI or differences in hemodynamic response
expressed in fMRI \cite{moeller2010multiband}.

A straight forward reduction of the scan time can be obtained by sampling
fewer slices, thus reducing the spatial resolution in the z-axis.
Spatial distances between adjacent slices of fetal MRI or fMRI, for
example, are often as high as 0.5 centimeters. Therefore, a significant
portion of the potential input is not conveyed through imaging. On
the other hand, under-sampling in the x-y domain leads to aliasing,
as predicted by the Nyquist sampling theorem.

Numerous research groups as well as leading MRI scanner manufacturers
make significant efforts to accelerate the MRI acquisition process.
Hardware solutions allow parallel imaging by using multiple coils
\cite{roemer1990nmr} to sample k-space data. There exist two major
approaches~\cite{Deshmane2012} that are currently implemented in
commercial MRI machines. Both reconstruct an image from the under-sampled
k-space data provided by each of the coils. The sensitivity encoder
(SENSE) transforms the partial k-spaces into images, then merges the
resulting aliased images into one coherent image~\cite{pruessmann1999sense}.
The GeneRalized Autocalibrating Partial Parallel Acquisition (GRAPPA)
techniques~\cite{griswold2002generalized} operate on signal data
within the complex frequency domain before the IFFT.

The compressed sensing (CS) technique~\cite{donoho2006compressed}
allows efficient acquisition and reconstruction of a signal with fewer
samples than the Nyquist-Shannon sampling theorem requires, if the
signal has sparse representation in a known transform domain. Using
CS for MRI reconstruction by sampling a small subset of the k-space
grid had been proposed in~\cite{lustig2007sparse}. The underlying
assumption is that the undersampling is random, such that the zero-filled
Fourier reconstruction exhibits incoherent artifacts that behave similarly
to additive random noise. This, however, would require specified pulse
programming.

Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast}
and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary}
were suggested for MRI reconstruction. MRI reconstruction using convolutional
neural networks (CNN) was introduced in \cite{wang2016accelerating}.
The network learns the mapping between zero-filled and fully-sampled
MR images. In \cite{Oktay2016}, residual network was proposed for
MRI super-resolution. Their model is able to receive multiple inputs
acquired from different viewing planes for better image reconstruction.
Both works address the reconstruction problems in the image domain
rather than the k-space domain. The proposed framework utilizes recent
advances in deep learning, while similarly to the CS methods addresses
MRI reconstruction directly from the k-space. Specifically, we use
generative adversarial networks (GAN) \cite{goodfellow2014generative,radford2015unsupervised,pathak2016context}.
GANs are based on the inter-play between two networks: a generator
and a discriminator. The generator is capable of learning the distribution
over a data-base, and sample realizations of this distribution. The
discriminator is trained to distinguish between `generated' samples
and real ones. This powerful combination has been used for generating
Computed Tomography (CT)-like images from MRIs~\cite{nie2016medical}.
Here, the generator is used for reconstruction of the entire k-space
grid from under-sampled data. Its loss is a combination of an adversarial
loss, based on the discriminator output and a fidelity loss with respect
to the fully sampled MRI. Promising results are obtained for brain
MRI reconstruction using only 52\% of the data.

The paper is organized as follows. Section 2 presents some theoretical
foundation and our method. Section 3 describes the experimental results.
Conclusions and future directions are describes in section 4.

%--------------------- METHOD --------------------%
\section{Method}

\subsection{K-space}
Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained
by the IFFT of the complex k-space signal $s_{0}$. Let $M_{F}$ denote
a full sampling mask such that the reconstructed MR image is: 
\begin{equation}
\bm{u}=F^{H}M_{F}\odot s_{0}
\end{equation}
where $H$ is the Hermitian transpose operation, $\odot$ denotes
element-wise multiplication, and $F^{H}$ is an orthonormal 2D IFFT
operator, such that $F^{H}F=I$. While sampling part of the k-space,
using $M_{p}$ as a sampling mask, the reconstructed MR image suffers
from artifacts and aliasing. An example of the under-sampling (52\%)
artifacts is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.

\begin{figure}
	\centering
	\begin{tabular}{cccc}
		\subfloat[\textcolor{black}{\scriptsize{}raw k-space}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_kspace_with_arrows}

		} & \subfloat[\textcolor{black}{\scriptsize{}fully sampled MRI}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mri}

		} & \subfloat[\textcolor{black}{\scriptsize{}sampling mask}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mask}

		} & \subfloat[\textcolor{black}{\scriptsize{}Zero-filled}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mri_rec}
}\tabularnewline
\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Under-sampling artifacts: the
	arrows illustrate the sampling methodology}}
\label{fig:pair_of_k_space_mri} 
\end{figure}

\subsection{Objective}

Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space. Given
a sampling mask and a model $f$, defined by the set of parameters
$\Theta$, our goal is to estimate the missing k-space samples such
that: 
\begin{equation}
\Theta=\arg\min_{\Theta}L(F^{H}f\left(s_{p};\Theta\right),\boldsymbol{u})
\end{equation}
where $L\left(\cdot\right)$ is the loss function. While choosing
the loss to be L2 norm is reasonable for natural images, for the k-space,
which has different spatial features, this may not be enough. As mentioned
in \cite{pathak2016context}, L2 minimization provides a blurry solution.
Averaging the high frequency details in the k-space domain results
in very poor reconstruction. In order to address this problem, we
used the adversarial loss, based on GAN.

We trained our model using the adversarial strategy, as described
in \cite{goodfellow2014generative,radford2015unsupervised}. This
method is based on a generator $G$, which takes noise \textbf{$z$
}with uniform distribution \textbf{$p_{u}\left(z\right)$} as input
and generates samples from the data distribution. A discriminator
$D$ is trained to distinguish between ``real'' examples from the
data and generated (``fake'') examples from $G.$ During the training
process, we optimize $G$ to maximize the discriminator's probability
of error. Simultaneously, $D$ is getting better and provides more
accurate predictions.

Let $s_{0}$ denote a ``real'' k-space sample from the distribution
$p_{r}\left(s_{0}\right)$. The following optimization process can
be described by two-players min-max game:

\begin{equation}
\min_{G}\max_{D}\mathbb{E_{\mathrm{s_{0}\sim p_{r}\left(s_{0}\right)}}\mathrm{\log\left[D\left(x\right)\right]}}+\mathbb{E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(G(z)\right)\right]}}
\end{equation}

In equilibrium, the generator $G$ is able to generate samples that
look like the real data. In our case, $G$ estimates the missing k-space
samples from a linear combination of the sampled data and a uniform
noise with distribution $p_{u}\left(z\right)$. An L2 fidelity constraint
is added to the adverbial loss of the generator, as follows:

\begin{equation}
\begin{aligned}L_{G}=\alpha\cdot E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(F^{-1}\left(\hat{s}_{0}\right)\right)\right]}+\\
\beta\cdot||\left(1-M_{p}\right)\odot\left(\hat{s}_{0}-s_{0}\right)||_{2}^{2}
\end{aligned}
\end{equation}
where $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=0.8$
are hyperparameters tuned by a cross-validation process. The discriminator's
input is the reconstructed MR image,\textbf{ }i.e.,\textbf{ }after
IFFT. By that, we are integrating the reconstruction phase in our
optimization.

\subsection{Network Architecture}

The generator input is a two-channel image representing the real and
the imaginary parts of the partially sampled k-space image, $s_{p}$.
Each missing sample is initialized by uniform i.i.d. noise. The pixel
$\left(i,j\right)$ in the generator input image is: 
\begin{equation}
G_{in}\left(i,j\right)=s_{p_{i,j}}+\left(1-M_{p}\right)_{i,j}z_{i,j}
\end{equation}

Due to the combination of the adversarial and the fidelity loss, $G$
produces reasonable k-space samples from a given samples and noise
distribution $p_{u}\left(z\right)$. In order to use the sampled data,
$s_{p}$, and estimate only the missing samples we used a residual
network \cite{he2016deep} as used in \cite{Oktay2016}, such that:
\begin{equation}
\hat{s}_{0}=s_{p}+\left(1-M_{p}\right)\odot G_{out}
\end{equation}
where $G_{out}$ is the generator output. Figure \ref{fig:system}
describes our framework:

\begin{figure}[H]
	\centering{}\includegraphics[width=7.8cm,height=4cm]{include/grp1/chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
			architecture: $G$ and $D$ are the generator and discriminator networks,
			respectively. $F$ is a $2D$ IFFT operator.}}
\end{figure}

A common architecture is used for the discriminator, composed of convolutional
layers, batch normalization, and leaky-ReLU as suggested in \cite{radford2015unsupervised}.
For the generator, we compose a dedicated architecture based on multi-channel
input for representing the real and imaginary components. Both architectures
are shown in Figure \ref{fig:test}.\textbf{ }The training methodology
is doing $k_{g}$ generator update steps for each discriminator single
step.

\begin{figure*}
	\centering{}%
	\begin{tabular}{|c|}
		\hline 
		\subfloat[\textcolor{black}{\footnotesize{}Generator}]{\centering{}\includegraphics[width=12cm,height=2cm]{include/grp1/arch_generator}

		}\tabularnewline
		\hline 
		\hline 
		\subfloat[\textcolor{black}{\footnotesize{}Discriminator}]{\centering{}\includegraphics[width=9cm,height=2cm]{include/grp1/arch_discriminator}

		}\tabularnewline
		\hline 
	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Networks architecture. The generator
		input is a two-channel signal, real and imaginary. For each layer,
		$k$ is the kernel size and $C$ is the number of output channels.}}
\label{fig:test} 
\end{figure*}

%--------------------- Experiments --------------------%
\section{Experiments}

The training data consists of 500 $3D$ brain MRI (T1) scans of different patients from the IXI dataset\footnote{\url{http://brain-development.org/ixi-dataset/}}. The data has been acquired by three MR machines, Philips 1.5T, 3T and GE 1.5. All images padded to resolution of $256\times256$ pixels.
From each $3D$ volume we extract 93 $2D$ saggital slices. We used $37.2k$ $(80\%)$ 2D slices for training and $9.2k$ $(20\%)$ for testing (100 $3D$ volumes).
In order to create k-space images for training, inverse orthonormal
2D FFT is applied to the fully-sampled MR images. We sample the k-space
using $2D$ Gaussian mask with sampling factor of 2.5, 4 and 6. Data augmentation
is created by random offsets of the proposed mask and image flipping.
This leads us to reconstruction of the MR image from 16.6\%-40\% of
the original k-space data.

The generator is composed of $5$ blocks of CONV-BatchNorm-ReLU, with
output channels $16,32,64,32,8,$ respectively. The last layer is
CONV with two outputs channels (for real and imaginary parts). The
discriminator is composed of $4$ blocks of CONV-Pool-BatchNorm-LReLU
with output channels $8,16,32,16$ and one fully-connected layer.
All CONV layers kernel size is $3\times3$. All weights was initialized
by Xavier \cite{glorot2010understanding}. We used RMSprop solver with
fixed learning rate of $5\mathrm{e}{-6}$ and set $k_{d}$ to 1.

We compare the proposed method to reconstruction results obtained
by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse}
and Zero-filling. In addition, we trained a generator (G) using only
L2 loss (CNN-L2). The same sampling masks was used for all cases.

A common metric used to quantify the reconstructed image quality is the PSNR. In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, brain's shape measure and segmentation.

\subsection{Peak signal-to-noise ratio (PSNR)}
The first measure and the most basic one. PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image. Therefore, this measure might no be a good metric for edges and general shape. For example, a model can provides a good reconstruction in the sense of PSNR but with blurry edges, results in a poor performance of algorithms that are based on them, for example segmentation.
However, PSNR is still a good indication for the image quality, especially if an expert should view it.
Quantitative evaluation is presented in~Table~\ref{tbl:PSNR_NO_MASK} and a graphical visualization in ~Figure~\ref{fig:error_psnr_errorbar}. The PSNR calculated on the whole image without masking. Note that the proposed method outperforms the other.

\begin{table}[H]
	\centering{}
\begin{tabular}{|c||c|c||c|c||c|c|}
	\hline 
	\textbf{PSNR} & \multicolumn{2}{c||}{Factor 2.5} & \multicolumn{2}{c||}{Factor 4} & \multicolumn{2}{c|}{Factor 6}\tabularnewline \cline{2-7}

	\textbf{Method}     &Mean   &std    &Mean   &std     &Mean   &std \tabularnewline \hline 	
	Zero-filled         &32.044 &2.616  &26.447 &1.997   &16.470 &2.181\tabularnewline
	CS-MRI              &39.053 &2.479  &33.273 &2.452   &26.951 &3.380\tabularnewline
	CNN-L2              &38.978 &2.454  &33.405 &2.232   &31.010 &2.299\tabularnewline
	\textbf{Proposed}   &39.802 &2.489  &34.595 &2.519   &31.555 &2.487\tabularnewline
		\hline 
	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, without masking}{\footnotesize{}\label{tbl:PSNR_NO_MASK}}}
\end{table}

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{include/grp2/error_psnr_errorbar}
\caption{PSNR without masking error-bar}
\end{figure}\label{fig:error_psnr_errorbar}

An extended validation of our model done by calculating the PSNR measure for different brain tissues. We applied an image segmentation algorithm, FAST \cite{zhang2001segmentation}, on the original fully-sampled MR image and then use it for calculating the masked-PSNR on gray matters, white matters and the Cerebrospinal Fluid (CSF). results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}.

\begin{table}[H]
	\centering
\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
	\hline 
	\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
	\cline{2-10} 
	 \textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
	 \hline 
	 Zero-filled & 41.494 & 36.736 & 38.546 & 37.279 & 34.379 & 36.369 & 24.887 & 24.987 & 29.337\tabularnewline
	 \hline 
	 CS-MRI & 44.374 & 40.042 & 40.744 & 41.655 & 37.247 & 39.119 & 35.595 & 33.111 & 36.648\tabularnewline
	 \hline 
	 CNN-L2 & 45.727 & 41.593 & 41.689 & 43.265 & 40.151 & 40.247 & 41.119 & 39.277 & 39.102\tabularnewline
	 \hline 
	 \textbf{Proposed} & 46.206 & 41.942 & 41.616 & 43.857 & 40.109 & 40.496 & 41.919 & 39.014 & 39.366\tabularnewline
	 \hline 
\end{tabular}
\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
\end{table}

%TODO:add after images
%Visual comparison is shown in Figure~\ref{fig:results}. MRIs reconstructed by using the suggested adversarial loss have stronger contrast and no significant aliasing or artifacts.

\subsection{Brain Extraction - Skull Stripping}
Brain extraction (Skull stripping) is a an algorithm that delineates the brain boundary (Figure~ \ref{fig:brain_extraction}). It is necessary for almost every brain analysis algorithm. In tissue segmentation for example, skull stripping is a pre-processing step which affects directly on the segments partition. We examine the different reconstruction methods by applying the Brain Extraction Tool (BET) \cite{smith2002fast} on each different MR reconstructed image. Then, we compared the skull stripping results to the fully-sampled result using the Modified Hausdorff Distance (MHD)~\cite{dubuisson1994modified}.

Let $C_1,C_2\in R^2$ denotes the brain contours extract from skull stripping algorithm on two different reconstruction methods respectively. MHD measures the distance between the contours such that:

\begin{equation}
\begin{array}{cc}
MHD(C_1,C_2) = \max \left\{\frac{1}{|C_1|} \sum_{\sigma_{1}\in C_1}^{}d(\sigma_1,C_2), ~ \frac{1}{|C_2|} \sum_{\sigma_{2}\in C_2}^{}d(\sigma_2,C_1)\right\} \\
d(\sigma_1,C_2) = \underset{\sigma_{2}\in C_{2}}{\min}||\sigma_1-\sigma_2|| \\
d(\sigma_2,C_1) = \underset{\sigma_{1}\in C_{1}}{\min}||\sigma_2-\sigma_1||
\end{array}
\end{equation}
where $\sigma_1,\sigma_2$ are points on the contours $C_1,C_2$ respectively (Figure~\ref{fig:brain_extraction}.c). MHD values for different sampling ratios are presented in~Table~\ref{tbl:MHD}.

\begin{table}[H]
	\centering{}
	\begin{tabular}{|c||c|c||c|c||c|c|}
		\hline 
		\textbf{MHD} & \multicolumn{2}{c||}{Factor 2.5} & \multicolumn{2}{c||}{Factor 4} & \multicolumn{2}{c|}{Factor 6}\tabularnewline \cline{2-7}

		\textbf{Method}     &Mean   &std    &Mean   &std     &Mean   &std \tabularnewline \hline 	
		Zero-filled         &1.111 &0.563  &2.617 &1.214   &3.121 &1.279\tabularnewline
		CS-MRI              &0.701 &0.511  &1.447 &1.027   &3.114 &1.617\tabularnewline
		CNN-L2              &0.420 &0.270  &0.715 &0.561   &1.083 &1.052\tabularnewline
		\textbf{Proposed}   &0.391 &0.250  &0.617 &0.306   &1.050 &1.033\tabularnewline
		\hline 
	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}MHD - brain extraction}{\footnotesize{}\label{tbl:MHD}}}
\end{table}

\begin{figure}[H]
	\centering
	\begin{tabular}{ccc}
	\subfloat[MR image]{\includegraphics[width=3cm, height=3.5cm]{include/grp2/skull_stripping}} 
	& 
	\subfloat[Brain extraction]{\includegraphics[width=3cm, height=3.5cm]{include/grp2/skull_stripping_brain}}
	&
	\subfloat[Hausdorff distance]{\includegraphics[width=3.5cm, height=3.5cm]{include/grp2/hausdorff}}
	\tabularnewline

	\end{tabular}\caption{Example of brain extraction}
	\label{fig:brain_extraction}
\end{figure}

\subsection{Brain Segmentation}
Talk about segmentation (FSL, FAST, etc..)

Why it is important

Noise and smoothing vs edges - important for segmentation algorithms

What is Dice score

Table

Images

%--------------------- CONCLUSIONS --------------------%
\section{Conclusions}

We proposed a software-only framework, using GANs for accelerating
MRI acquisition. Specifically, high-quality MRI reconstruction using
only 52\% of the original k-space data is demonstrated. The key idea
is based on utilizing an adversarial loss in addition to L2 loss.
It is worth mentioning that the proposed sampling mask is currently
implemented in commercial MRI machines with no need for additional
hardware or dedicated pulse programming. Future work will concentrate
on generation of MRI in the presence of pathologies.

%--------------------- Acknowledgment --------------------%
\subsection{Acknowledgment}
This research is partially supported by the Israel Science Foundation (T.R.R. 1638/16 ) and the IDF Medical Corps (T.R.R.)

\begin{figure}
	\begin{raggedright}

%		\hspace{-1.2cm}%
		\begin{tabular}{>{\centering}b{0.2cm}lcccc}
			& \multicolumn{1}{c}{{\footnotesize{}Original}} & {\footnotesize{}Zero-filled} & {\footnotesize{}CS-MRI} & {\footnotesize{}CNN-L2} & {\footnotesize{}Proposed}\tabularnewline
			\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
					{\footnotesize{}Reconstructed}
				\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res1_org} & \includegraphics[width=2.5cm]{include/grp1/res1_zero} & \includegraphics[width=2.5cm]{include/grp1/res1_cs_red} & \includegraphics[width=2.5cm]{include/grp1/res1_L2_red} & \includegraphics[width=2.5cm]{include/grp1/res1_our}\tabularnewline
				\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
						{\footnotesize{}Zoom in}
					\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res1_org_zoom} & \includegraphics[width=2.5cm]{include/grp1/res1_zero_zoom} & \includegraphics[width=2.5cm]{include/grp1/res1_cs_zoom} & \includegraphics[width=2.5cm]{include/grp1/res1_L2_zoom} & \includegraphics[width=2.5cm]{include/grp1/res1_our_zoom}\tabularnewline
					\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
							{\footnotesize{}Reconstructed}
						\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res7_org} & \includegraphics[width=2.5cm]{include/grp1/res7_zero} & \includegraphics[width=2.5cm]{include/grp1/res7_cs_red} & \includegraphics[width=2.5cm]{include/grp1/res7_L2_red} & \includegraphics[width=2.5cm]{include/grp1/res7_our}\tabularnewline
						\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
								{\footnotesize{}Zoom in}
							\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res7_org_zoom} & \includegraphics[width=2.5cm]{include/grp1/res7_zero_zoom} & \includegraphics[width=2.5cm]{include/grp1/res7_cs_zoom} & \includegraphics[width=2.5cm]{include/grp1/res7_L2_zoom} & \includegraphics[width=2.5cm]{include/grp1/res7_our_zoom}\tabularnewline
							\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
									{\footnotesize{}Reconstructed}
								\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res11_org} & \includegraphics[width=2.5cm]{include/grp1/res11_zero} & \includegraphics[width=2.5cm]{include/grp1/res11_cs_red} & \includegraphics[width=2.5cm]{include/grp1/res11_L2_red} & \includegraphics[width=2.5cm]{include/grp1/res11_our}\tabularnewline
								\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
										{\footnotesize{}Zoom in}
									\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res11_org_zoom} & \includegraphics[width=2.5cm]{include/grp1/res11_zero_zoom} & \includegraphics[width=2.5cm]{include/grp1/res11_cs_zoom} & \includegraphics[width=2.5cm]{include/grp1/res11_L2_zoom} & \includegraphics[width=2.5cm]{include/grp1/res11_our_zoom}\tabularnewline
								\end{tabular}
								\par\end{raggedright}
							\raggedright{}\caption{\textcolor{black}{\footnotesize{}Examples of reconstructed MR images
									from under-sampled k-space.}}
							\label{fig:results} 
						\end{figure}

\bibliography{paper}

\end{document}

### 2017-12-25 paper.tex
Update doc - sampling masls

@@
 is created by random offsets of the proposed mask and image flipping.
-This leads us to reconstruction of the MR image from 16.6\%-40\% of
+This leads us to reconstruction of the MR image from 16.6\%-40\% (Figure~\ref{fig:sampling_masks}) of
 the original k-space data.
@@
 In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, brain's shape measure and segmentation.
+
+\begin{figure}[H]
+	\centering
+	\begin{tabular}{ccc}
+		\subfloat[Factor 2.5 (40\%)]{\includegraphics[width=3cm, height=3cm]{include/grp2/mask2}}
+		& 
+		\subfloat[Factor 4 (25\%)]{\includegraphics[width=3cm, height=3cm]{include/grp2/mask4}}
+		&
+		\subfloat[Factor 6 (16.66\%)]{\includegraphics[width=3cm, height=3cm]{include/grp2/mask6}}
+		\tabularnewline
+
+	\end{tabular}\caption{$2D$ Gaussian sampling masks}
+	\label{fig:sampling_masks}
+\end{figure}
 

### 2017-12-27 paper.tex
images update

@@
 \subsection{Peak signal-to-noise ratio (PSNR)}
-The first measure and the most basic one.
 PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image.
-Therefore, this measure might no be a good metric for edges and general shape.
-For example, a model can provides a good reconstruction in the sense of PSNR but with blurry edges, results in a poor performance of algorithms that are based on them, for example segmentation.
+Therefore, this measure is not a sufficient metric for edges and general shape.
+For example, a model can provides a good reconstruction in the sense of PSNR but with blurry edges, which results in a poor performance of algorithms that use them, for example segmentation.
 However, PSNR is still a good indication for the image quality, especially if an expert should view it.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 
-An extended validation of our model done by calculating the PSNR measure for different brain tissues.
+An extended validation of our model done by calculating the PSNR measure on different brain tissues.
 We applied an image segmentation algorithm, FAST \cite{zhang2001segmentation}, on the original fully-sampled MR image and then use it for calculating the masked-PSNR on gray matters, white matters and the Cerebrospinal Fluid (CSF).
@@
 %Visual comparison is shown in Figure~\ref{fig:results}. MRIs reconstructed by using the suggested adversarial loss have stronger contrast and no significant aliasing or artifacts.
+
+\begin{figure}[H]
+	\begin{raggedright}
+		\begin{tabular}{>{\centering}b{0.2cm}lcccc}
+			& \multicolumn{1}{c}{\footnotesize Original} & {\footnotesize Zero-filled} & {\footnotesize CS-MRI} & {\footnotesize CNN-L2} & {\footnotesize Proposed}\tabularnewline
+			\multirow{1}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Reconstructed} \end{turn}} &
+
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__50} &
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_50}
+
+			 \tabularnewline
+
+			 \multirow{1}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Zoom in} \end{turn}} &
+
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zoom_50} &
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_zoom_50} & 
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CNNL2_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_zoom_50}
+
+			 \tabularnewline
+
+			\multirow{2}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Brain} \end{turn}} &
+
+ 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__50} &
+			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__predict_50}
+
+			\tabularnewline
+
+			\multirow{2}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Segmentation} \end{turn}} &
+
+ 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__50} &
+ 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__predict_50}
+
+		\end{tabular}
+	\par\end{raggedright}
+	\raggedright{}\caption{\textcolor{black}{\footnotesize{}Examples of reconstructed MR images from under-sampled k-space.}}
+	\label{fig:example} 
+\end{figure}
 

### 2017-12-28 paper.tex
Update 28.12

@@
 
+%\begin{table}[H]
+%	\centering{}
+%\begin{tabular}{|c||c|c||c|c||c|c|}
+%	\hline 
+%	\textbf{PSNR} & \multicolumn{2}{c||}{Factor 2.5} & \multicolumn{2}{c||}{Factor 4} & \multicolumn{2}{c|}{Factor 6}\tabularnewline \cline{2-7}
+%
+%	\textbf{Method}     &Mean   &std    &Mean   &std     &Mean   &std \tabularnewline \hline 	
+%	Zero-filled         &32.044 &2.616  &26.447 &1.997   &16.470 &2.181\tabularnewline
+%	CS-MRI              &39.053 &2.479  &33.273 &2.452   &26.951 &3.380\tabularnewline
+%	CNN-L2              &38.978 &2.454  &33.405 &2.232   &31.010 &2.299\tabularnewline
+%	\textbf{Proposed}   &39.802 &2.489  &34.595 &2.519   &31.555 &2.487\tabularnewline
+%		\hline 
+%	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, without masking}{\footnotesize{}\label{tbl:PSNR_NO_MASK}}}
+%\end{table}
+
 \begin{table}[H]
 	\centering{}
-\begin{tabular}{|c||c|c||c|c||c|c|}
+	\begin{tabular}{|c||c||c||c|}
 		\hline 
-	\textbf{PSNR} & \multicolumn{2}{c||}{Factor 2.5} & \multicolumn{2}{c||}{Factor 4} & \multicolumn{2}{c|}{Factor 6}\tabularnewline \cline{2-7}
+		\textbf{PSNR} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6}} \tabularnewline
+		\textbf{Method} & \multicolumn{1}{c||}{} & \multicolumn{1}{c||}{} & \multicolumn{1}{c|}{} \tabularnewline \cline{1-4}
 
-	\textbf{Method}     &Mean   &std    &Mean   &std     &Mean   &std \tabularnewline \hline 	
-	Zero-filled         &32.044 &2.616  &26.447 &1.997   &16.470 &2.181\tabularnewline
-	CS-MRI              &39.053 &2.479  &33.273 &2.452   &26.951 &3.380\tabularnewline
-	CNN-L2              &38.978 &2.454  &33.405 &2.232   &31.010 &2.299\tabularnewline
-	\textbf{Proposed}   &39.802 &2.489  &34.595 &2.519   &31.555 &2.487\tabularnewline
+		Zero-filled         &32.044~$\pm$~2.616  &26.447~$\pm$~1.997   &16.470~$\pm$~2.181\tabularnewline
+		CS-MRI              &39.053~$\pm$~2.479  &33.273~$\pm$~2.452   &26.951~$\pm$~3.380\tabularnewline
+		CNN-L2              &38.978~$\pm$~2.454  &33.405~$\pm$~2.232   &31.010~$\pm$~2.299\tabularnewline
+		\textbf{Proposed}   &\textbf{39.802~$\pm$~2.489}  &\textbf{34.595~$\pm$~2.519}   &\textbf{31.555~$\pm$~2.487}\tabularnewline
 		\hline 
@@
 	\centering{}
-	\begin{tabular}{|c||c|c||c|c||c|c|}
+	\begin{tabular}{|c||c||c||c|}
 		\hline 
-		\textbf{MHD} & \multicolumn{2}{c||}{Factor 2.5} & \multicolumn{2}{c||}{Factor 4} & \multicolumn{2}{c|}{Factor 6}\tabularnewline \cline{2-7}
+		\textbf{MHD} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6}} \tabularnewline
+		\textbf{Method} & \multicolumn{1}{c||}{} & \multicolumn{1}{c||}{} & \multicolumn{1}{c|}{} \tabularnewline \cline{1-4}
 
-		\textbf{Method}     &Mean   &std    &Mean   &std     &Mean   &std \tabularnewline \hline 	
-		Zero-filled         &1.111 &0.563  &2.617 &1.214   &3.121 &1.279\tabularnewline
-		CS-MRI              &0.701 &0.511  &1.447 &1.027   &3.114 &1.617\tabularnewline
-		CNN-L2              &0.420 &0.270  &0.715 &0.561   &1.083 &1.052\tabularnewline
-		\textbf{Proposed}   &0.391 &0.250  &0.617 &0.306   &1.050 &1.033\tabularnewline
+		Zero-filled         &1.111~$\pm$~0.563  &2.617~$\pm$~1.214   &3.121~$\pm$~1.279\tabularnewline
+		CS-MRI              &0.701~$\pm$~0.511  &1.447~$\pm$~1.027   &3.114~$\pm$~1.617\tabularnewline
+		CNN-L2              &0.420~$\pm$~0.270  &0.715~$\pm$~0.561   &1.083~$\pm$~1.052\tabularnewline
+		\textbf{Proposed}   &\textbf{0.391~$\pm$~0.250}  &\textbf{0.617~$\pm$~0.306}   &\textbf{1.050~$\pm$~1.033}\tabularnewline
 		\hline 
@@
 Images
+
+\begin{table}[H]
+	\centering
+	\resizebox{\textwidth}{!}{%
+	\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
+		\hline 
+		\textbf{DICE} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
+		\cline{2-10} 
+		\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
+		\hline 
+		Zero-filled & 0.882~$\pm$~0.08 & 0.826~$\pm$~0.05 & 0.796~$\pm$~0.05 & 0.718~$\pm$~0.10 & 0.644~$\pm$~0.05 & 0.627~$\pm$~0.05 & 0.599~$\pm$~0.12 & 0.466~$\pm$~0.07 & 0.050~$\pm$~0.06\tabularnewline
+		\hline 
+		CS-MRI & 0.942~$\pm$~0.05 & 0.910~$\pm$~0.03 & 0.868~$\pm$~0.03 & 0.871~$\pm$~0.10 & 0.805~$\pm$~0.08 & 0.770~$\pm$~0.05 & 0.708~$\pm$~0.14 & 0.639~$\pm$~0.08 & 0.621~$\pm$~0.07     \tabularnewline
+		\hline 
+		CNN-L2 & 0.948~$\pm$~0.02 & 0.919~$\pm$~0.02 & 0.891~$\pm$~0.02 & 0.888~$\pm$~0.06 & 0.836~$\pm$~0.04 & 0.813~$\pm$~0.03 & 0.836~$\pm$~0.09 & 0.770~$\pm$~0.06 & 0.747~$\pm$~0.06     \tabularnewline
+		\hline
+
+		\textbf{Proposed} & \textbf{0.954~$\pm$~0.01} & \textbf{0.928~$\pm$~0.02} & \textbf{0.900~$\pm$~0.002} & \textbf{0.903~$\pm$~0.06} & \textbf{0.858~$\pm$~0.04} & \textbf{0.833~$\pm$~0.03} & \textbf{0.851~$\pm$~0.09} & \textbf{0.789~$\pm$~0.06} & \textbf{0.767~$\pm$~0.06}     \tabularnewline
+		\hline 
+	\end{tabular}
+	}
+	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice score for different sampling ratios}{\footnotesize{}\label{tbl:DICE}}}
+\end{table}
+
+WHICH IS BETTER???
+\begin{table}[H]
+	\centering
+	\resizebox{\textwidth}{!}{%
+		\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
+			\hline 
+			\textbf{DICE} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
+			\cline{2-10} 
+			\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
+			\hline 
+			Zero-filled & 0.882$\pm$0.08 & 0.826$\pm$0.05 & 0.796$\pm$0.05 & 0.718$\pm$0.10 & 0.644$\pm$0.05 & 0.627$\pm$0.05 & 0.599$\pm$0.12 & 0.466$\pm$0.07 & 0.050$\pm$0.06\tabularnewline
+			\hline 
+			CS-MRI & 0.942$\pm$0.05 & 0.910$\pm$0.03 & 0.868$\pm$0.03 & 0.871$\pm$0.10 & 0.805$\pm$0.08 & 0.770$\pm$0.05 & 0.708$\pm$0.14 & 0.639$\pm$0.08 & 0.621$\pm$0.07     \tabularnewline
+			\hline 
+			CNN-L2 & 0.948$\pm$0.02 & 0.919$\pm$0.02 & 0.891$\pm$0.02 & 0.888$\pm$0.06 & 0.836$\pm$0.04 & 0.813$\pm$0.03 & 0.836$\pm$0.09 & 0.770$\pm$0.06 & 0.747$\pm$0.06     \tabularnewline
+			\hline
+
+			\textbf{Proposed} & \textbf{0.954$\pm$0.01} & \textbf{0.928$\pm$0.02} & \textbf{0.900$\pm$0.002} & \textbf{0.903$\pm$0.06} & \textbf{0.858$\pm$0.04} & \textbf{0.833$\pm$0.03} & \textbf{0.851$\pm$0.09} & \textbf{0.789$\pm$0.06} & \textbf{0.767$\pm$0.06}     \tabularnewline
+			\hline 
+		\end{tabular}
+	}
+	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice score for different sampling ratios}{\footnotesize{}\label{tbl:DICE2}}}
+\end{table}
 

### 2017-12-30 paper.tex
Update

@@
 \begin{document}
-
+%		\fontfamily{qtm}\selectfont
 \begin{frontmatter}
@@
 \begin{abstract}
-A main challenge in Magnetic Resonance Imaging (MRI) for clinical
-applications is speeding up scan time. Beyond the improvement of patient
-experience and the reduction of operational costs, faster scans are
-essential for time-sensitive imaging, where target movement is unavoidable,
-yet must be significantly lessened, e.g., fetal MRI, cardiac cine,
-and lungs imaging. Moreover, short scan time can enhance temporal
-resolution in dynamic scans, such as functional MRI or dynamic contrast
-enhanced MRI. Current imaging methods facilitate MRI acquisition at
-the price of lower spatial resolution and costly hardware solutions.
+A main challenge in Magnetic Resonance Imaging (MRI) for clinical applications is speeding up scan time.
+Beyond the improvement of patient experience and the reduction of operational costs, faster scans are essential for time-sensitive imaging, where target movement is unavoidable, yet must be significantly lessened, e.g., fetal MRI, cardiac cine, and lungs imaging.
+Moreover, short scan time can enhance temporal resolution in dynamic scans, such as functional MRI or dynamic contrast enhanced MRI.
+Current imaging methods facilitate MRI acquisition at the price of lower spatial resolution and costly hardware solutions.
 
-We introduce a practical, software-only framework, based on deep learning,
-for accelerating MRI scan time allows maintaining good quality imaging.
-This is accomplished by partial MRI sampling, while using an adversarial
-neural network to estimate the missing samples. The inter-play between
-the generator and the discriminator networks enables the introduction
-of an adversarial cost in addition to a fidelity loss used for optimizing
-the peak signal-to-noise ratio (PSNR). Promising image reconstruction
-results are obtained for 1.5T MRI where only 52\% of the original
-data are used. 
+We introduce a practical, software-only framework, based on deep learning, for accelerating MRI scan time allows maintaining good quality imaging.
+This is accomplished by partial MRI sampling, while using an adversarial neural network to estimate the missing samples.
+The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to a fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR).
+Promising image reconstruction results are obtained for 3T and 1.5T MRI where only 40\%, 25\% and 16.6\% of the original data are used.
+Extended performance assessment was conducted in order to emphasize the advantage of proposed method.
 \end{abstract}
@@
 \section{Introduction}
-Magnetic Resonance Imaging (MRI) is a non-ionizing imaging modality,
-and is therefore widely used in diagnostic medicine and biomedical
-research. The physical principles of MRI are based on a strong magnetic
-field and pulses of radio frequency (RF) electromagnetic radiation.
-Images are produced when hydrogen atoms, which are prevalent in living
-organisms, emit the absorbed RF energy that is then received by antennas
-in close proximity to the anatomy being examined. Spatial localization
-of the detected MRI signals is obtained by varying the magnetic field
-gradients. The discretized RF output is presented in a Fourier space
-(called K-space), where the x-axis is refers to the frequency and
-the y-axis to the phase. An inverse fast Fourier transform (IFFT)
-of the K-space is then used for generating anatomically meaningful
-MRI scans. Figure \ref{fig:pair_of_k_space_mri} presents K-space
-traversal patterns used in conventional imaging. Each row of the k-space
-is acquired after one RF excitation pulse. The number of rows multiplied
-by the number of slices (z-axis) determines the total scan time.
+Magnetic Resonance Imaging (MRI) is a non-ionizing imaging modality, and is therefore widely used in diagnostic medicine and biomedical research.
+The physical principles of MRI are based on a strong magnetic field and pulses of radio frequency (RF) electromagnetic radiation.
+Images are produced when hydrogen atoms, which are prevalent in living organisms, emit the absorbed RF energy that is then received by antennas in close proximity to the anatomy being examined.
+Spatial localization of the detected MRI signals is obtained by varying the magnetic field gradients.
+The discretized RF output is presented in a Fourier space
+(called K-space), where the x-axis is refers to the frequency and the y-axis to the phase.
+An inverse fast Fourier transform (IFFT) of the K-space is then used for generating anatomically meaningful MRI scans.
+Figure \ref{fig:pair_of_k_space_mri} presents K-space traversal patterns used in conventional imaging.
+Each row of the k-space is acquired after one RF excitation pulse.
+The number of rows multiplied by the number of slices (z-axis) determines the total scan time.
 
@@
 using $M_{p}$ as a sampling mask, the reconstructed MR image suffers
-from artifacts and aliasing. An example of the under-sampling (52\%)
-artifacts is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
+from artifacts and aliasing. An example artifacts caused by under-sampling in the phase axis using Gaussian mask (40\%)
+is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\begin{tabular}{cccc}
-		\subfloat[\textcolor{black}{\scriptsize{}raw k-space}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_kspace_with_arrows}
+		\subfloat[\textcolor{black}{\scriptsize{}raw k-space}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp1/example_mask_kspace_with_arrows}
 
-		} & \subfloat[\textcolor{black}{\scriptsize{}fully sampled MRI}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mri}
+		} & \subfloat[\textcolor{black}{\scriptsize{}fully sampled MRI}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_original.png}
 
-		} & \subfloat[\textcolor{black}{\scriptsize{}sampling mask}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mask}
+		} & \subfloat[\textcolor{black}{\scriptsize{}sampling mask}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_samplingMask4.png}
 
-		} & \subfloat[\textcolor{black}{\scriptsize{}Zero-filled}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mri_rec}
+		} & \subfloat[\textcolor{black}{\scriptsize{}Zero-filled}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_zeroPadding.png}
 }\tabularnewline
@@
 is created by random offsets of the proposed mask and image flipping.
-This leads us to reconstruction of the MR image from 16.6\%-40\% (Figure~\ref{fig:sampling_masks}) of
+This leads us to reconstruction of the MR image from 40\%, 25\% and 16.6\% (Figure~\ref{fig:sampling_masks}) of
 the original k-space data.
 
-The generator is composed of $5$ blocks of CONV-BatchNorm-ReLU, with
-output channels $16,32,64,32,8,$ respectively. The last layer is
-CONV with two outputs channels (for real and imaginary parts). The
-discriminator is composed of $4$ blocks of CONV-Pool-BatchNorm-LReLU
-with output channels $8,16,32,16$ and one fully-connected layer.
-All CONV layers kernel size is $3\times3$. All weights was initialized
-by Xavier \cite{glorot2010understanding}. We used RMSprop solver with
-fixed learning rate of $5\mathrm{e}{-6}$ and set $k_{d}$ to 1.
+The generator is composed of $5$ blocks of CONV-BatchNorm-ReLU, with output channels $16,32,64,32,8,$ respectively.
+The last layer is CONV with two outputs channels (for real and imaginary parts).
+The discriminator is composed of $4$ blocks of CONV-Pool-BatchNorm-LReLU with output channels $8,16,32,16$ and one fully-connected layer.
+All CONV layers kernel size is $3\times3$.
+All weights was initialized by Xavier \cite{glorot2010understanding}.
+We used RMSprop solver with fixed learning rate of $5\mathrm{e}{-6}$ and set $k_{d}$ to 1.
 
-We compare the proposed method to reconstruction results obtained
-by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse}
-and Zero-filling. In addition, we trained a generator (G) using only
-L2 loss (CNN-L2). The same sampling masks was used for all cases.
+We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
+In addition, we optimized two networks: 1.
+CNN-L2 - a k-space generator (with same architecture as the proposed method) using only L2 loss.
+2.
+IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding.
+We used the U-net \cite{ronneberger2015u} architecture inspired by \cite{lee2017deep}.
+The same sampling masks was used for all cases.
 
 A common metric used to quantify the reconstructed image quality is the PSNR.
-In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, brain's shape measure and segmentation.
+In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, brain's shape measure and tissue segmentation.
 
@@
 		CS-MRI              &39.053~$\pm$~2.479  &33.273~$\pm$~2.452   &26.951~$\pm$~3.380\tabularnewline
+		IM-CNN-L2           &35.281~$\pm$~2.210  &31.577~$\pm$~2.109   &23.417~$\pm$~2.676\tabularnewline
 		CNN-L2              &38.978~$\pm$~2.454  &33.405~$\pm$~2.232   &31.010~$\pm$~2.299\tabularnewline
@@
 
+%\begin{table}[H]
+%	\centering
+%\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
+%	\hline 
+%	\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
+%	\cline{2-10} 
+%	 \textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
+%	 \hline 
+%	 Zero-filled & 41.494 & 36.736 & 38.546 & 37.279 & 34.379 & 36.369 & 24.887 & 24.987 & 29.337\tabularnewline
+%	 \hline 
+%	 CS-MRI & 44.374 & 40.042 & 40.744 & 41.655 & 37.247 & 39.119 & 35.595 & 33.111 & 36.648\tabularnewline
+%	 \hline 
+%	 CNN-L2 & 45.727 & 41.593 & 41.689 & 43.265 & 40.151 & 40.247 & 41.119 & 39.277 & 39.102\tabularnewline
+%	 \hline 
+%	 \textbf{Proposed} & 46.206 & 41.942 & 41.616 & 43.857 & 40.109 & 40.496 & 41.919 & 39.014 & 39.366\tabularnewline
+%	 \hline 
+%\end{tabular}
+%\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
+%\end{table}
+
 \begin{table}[H]
 	\centering
+	\resizebox{\textwidth}{!}{%
+		\scriptsize
+		\setlength\tabcolsep{2pt}
 	\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
@@
 		\hline 
-	 Zero-filled & 41.494 & 36.736 & 38.546 & 37.279 & 34.379 & 36.369 & 24.887 & 24.987 & 29.337\tabularnewline
+		Zero-filled & 41.494{\tiny $\pm$}3.48 & 36.736{\tiny $\pm$}3.32 & 38.546{\tiny $\pm$}2.45 & 37.279{\tiny $\pm$}2.18 & 34.379{\tiny $\pm$}2.52 & 36.369{\tiny $\pm$}1.87 & 24.887{\tiny $\pm$}1.62 & 24.987{\tiny $\pm$}1.91 & 29.337{\tiny $\pm$}2.08\tabularnewline
 		\hline 
-	 CS-MRI & 44.374 & 40.042 & 40.744 & 41.655 & 37.247 & 39.119 & 35.595 & 33.111 & 36.648\tabularnewline
+		CS-MRI & 44.374{\tiny $\pm$}4.20 & 40.042{\tiny $\pm$}3.84 & 40.744{\tiny $\pm$}3.16 & 41.655{\tiny $\pm$}3.12 & 37.247{\tiny $\pm$}2.99 & 39.119{\tiny $\pm$}2.43 & 35.595{\tiny $\pm$}3.15 & 33.111{\tiny $\pm$}2.91 & 36.648{\tiny $\pm$}2.26\tabularnewline
 		\hline 
-	 CNN-L2 & 45.727 & 41.593 & 41.689 & 43.265 & 40.151 & 40.247 & 41.119 & 39.277 & 39.102\tabularnewline
+		CNN-L2 & 45.727{\tiny $\pm$}4.70 & 41.593{\tiny $\pm$}4.16 & 41.689{\tiny $\pm$}3.69 & 43.265{\tiny $\pm$}2.95 & 40.151{\tiny $\pm$}3.15 & 40.247{\tiny $\pm$}2.47 & 41.119{\tiny $\pm$}2.48 & 39.277{\tiny $\pm$}2.65 & 39.102{\tiny $\pm$}1.93\tabularnewline
 		\hline 
-	 \textbf{Proposed} & 46.206 & 41.942 & 41.616 & 43.857 & 40.109 & 40.496 & 41.919 & 39.014 & 39.366\tabularnewline
+		\textbf{Proposed} & \textbf{46.206{\tiny $\pm$}4.77} & \textbf{41.942{\tiny $\pm$}4.34} & \textbf{41.616{\tiny $\pm$}2.45} & \textbf{43.857{\tiny $\pm$}3.16} & \textbf{40.109{\tiny $\pm$}3.25} & \textbf{40.496{\tiny $\pm$}2.57} & \textbf{41.919{\tiny $\pm$}2.77} & \textbf{39.014{\tiny $\pm$}2.88} & \textbf{39.366{\tiny $\pm$}2.17}\tabularnewline
 		\hline 
 	\end{tabular}
+	}
 	\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
+\end{table}
+
+ONLY 2 DIGITS
+\begin{table}[H]
+	\centering
+	\resizebox{\textwidth}{!}{%
+		\scriptsize
+		\setlength\tabcolsep{2pt}
+		\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
+			\hline 
+			\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
+			\cline{2-10} 
+			\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
+			\hline 
+			Zero-filled & 41.49{\tiny $\pm$}3.48 & 36.73{\tiny $\pm$}3.32 & 38.54{\tiny $\pm$}2.45 & 37.27{\tiny $\pm$}2.18 & 34.37{\tiny $\pm$}2.52 & 36.36{\tiny $\pm$}1.87 & 24.88{\tiny $\pm$}1.62 & 24.98{\tiny $\pm$}1.91 & 29.33{\tiny $\pm$}2.08\tabularnewline
+			\hline 
+			CS-MRI & 44.37{\tiny $\pm$}4.20 & 40.04{\tiny $\pm$}3.84 & 40.74{\tiny $\pm$}3.16 & 41.65{\tiny $\pm$}3.12 & 37.24{\tiny $\pm$}2.99 & 39.11{\tiny $\pm$}2.43 & 35.59{\tiny $\pm$}3.15 & 33.11{\tiny $\pm$}2.91 & 36.64{\tiny $\pm$}2.26\tabularnewline
+			\hline 
+			CNN-L2 & 45.72{\tiny $\pm$}4.70 & 41.59{\tiny $\pm$}4.16 & 41.68{\tiny $\pm$}3.69 & 43.26{\tiny $\pm$}2.95 & 40.15{\tiny $\pm$}3.15 & 40.24{\tiny $\pm$}2.47 & 41.11{\tiny $\pm$}2.48 & 39.27{\tiny $\pm$}2.65 & 39.10{\tiny $\pm$}1.93\tabularnewline
+			\hline 
+			\textbf{Proposed} & \textbf{46.20{\tiny $\pm$}4.77} & \textbf{41.94{\tiny $\pm$}4.34} & \textbf{41.61{\tiny $\pm$}2.45} & \textbf{43.85{\tiny $\pm$}3.16} & \textbf{40.11{\tiny $\pm$}3.25} & \textbf{40.49{\tiny $\pm$}2.57} & \textbf{41.91{\tiny $\pm$}2.77} & \textbf{39.01{\tiny $\pm$}2.88} & \textbf{39.36{\tiny $\pm$}2.17}\tabularnewline
+			\hline 
+		\end{tabular}
+	}
+	\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK2}}}
 \end{table}
@@
 \subsection{Brain Segmentation}
-Talk about segmentation (FSL, FAST, etc..)
+Brain segmentation is the task of partitioning the brain image (MRI in our case), into the following segments: background, white matter, gray matter and CSF.
+This process is of a great importance for brain MR image analysis, especially for therapy planning and also for clinical research.
+Sampling artifacts, results in poor signal to noise and blurry edges, may hurts the algorithm performance.
+We suggest a way to evaluate and compare different MRI reconstruction methods based on segmentation results.
+We create a reference by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and run a brain segmentation algorithm (FAST \cite{zhang2001segmentation}).
+Then, we did the same process for all the reconstruction methods and compared the segmentation results to the reference.
 
-Why it is important
-
-Noise and smoothing vs edges - important for segmentation algorithms
-
-What is Dice score
-
-Table
-
-Images
+The measure used for segmentations comparison is the Dice score \cite{dice1945measures} between the original and the reconstructed image segments.
+Dice score is a measure of sets similarity which gets the values between 0 (no similarity) to 1.0 (max similarity).
+Denotes by $S_{i,j}$ the set of pixels in segment $j$ for method $i$, the Dice between two methods for this segment is:
+\begin{equation}
+\begin{array}{c}
+DICE(S_{1,j},S_{2,j}) = \frac{2\cdot|S_{1,j} \cap S_{2,j}|} {|S_{1,j}| + |S_{2,j}|}
+\end{array}
+\end{equation}
+Dice values for different sampling ratios are presented in~Table~\ref{tbl:DICE}. Our methods archive the best Dice score for all the brain tissues.
 
@@
 	\resizebox{\textwidth}{!}{%
+		\scriptsize
+		\setlength\tabcolsep{2pt}
 		\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
@@
 			\hline 
-		Zero-filled & 0.882~$\pm$~0.08 & 0.826~$\pm$~0.05 & 0.796~$\pm$~0.05 & 0.718~$\pm$~0.10 & 0.644~$\pm$~0.05 & 0.627~$\pm$~0.05 & 0.599~$\pm$~0.12 & 0.466~$\pm$~0.07 & 0.050~$\pm$~0.06\tabularnewline
+			Zero-filled & 0.882{\tiny $\pm$}0.08 & 0.826{\tiny $\pm$}0.05 & 0.796{\tiny $\pm$}0.05 & 0.718{\tiny $\pm$}0.10 & 0.644{\tiny $\pm$}0.05 & 0.627{\tiny $\pm$}0.05 & 0.599{\tiny $\pm$}0.12 & 0.466{\tiny $\pm$}0.07 & 0.050{\tiny $\pm$}0.06\tabularnewline
 			\hline 
-		CS-MRI & 0.942~$\pm$~0.05 & 0.910~$\pm$~0.03 & 0.868~$\pm$~0.03 & 0.871~$\pm$~0.10 & 0.805~$\pm$~0.08 & 0.770~$\pm$~0.05 & 0.708~$\pm$~0.14 & 0.639~$\pm$~0.08 & 0.621~$\pm$~0.07     \tabularnewline
+			CS-MRI & 0.942{\tiny $\pm$}0.05 & 0.910{\tiny $\pm$}0.03 & 0.868{\tiny $\pm$}0.03 & 0.871{\tiny $\pm$}0.10 & 0.805{\tiny $\pm$}0.08 & 0.770{\tiny $\pm$}0.05 & 0.708{\tiny $\pm$}0.14 & 0.639{\tiny $\pm$}0.08 & 0.621{\tiny $\pm$}0.07     \tabularnewline
 			\hline 
-		CNN-L2 & 0.948~$\pm$~0.02 & 0.919~$\pm$~0.02 & 0.891~$\pm$~0.02 & 0.888~$\pm$~0.06 & 0.836~$\pm$~0.04 & 0.813~$\pm$~0.03 & 0.836~$\pm$~0.09 & 0.770~$\pm$~0.06 & 0.747~$\pm$~0.06     \tabularnewline
+			CNN-L2 & 0.948{\tiny $\pm$}0.02 & 0.919{\tiny $\pm$}0.02 & 0.891{\tiny $\pm$}0.02 & 0.888{\tiny $\pm$}0.06 & 0.836{\tiny $\pm$}0.04 & 0.813{\tiny $\pm$}0.03 & 0.836{\tiny $\pm$}0.09 & 0.770{\tiny $\pm$}0.06 & 0.747{\tiny $\pm$}0.06     \tabularnewline
 			\hline
 
-		\textbf{Proposed} & \textbf{0.954~$\pm$~0.01} & \textbf{0.928~$\pm$~0.02} & \textbf{0.900~$\pm$~0.002} & \textbf{0.903~$\pm$~0.06} & \textbf{0.858~$\pm$~0.04} & \textbf{0.833~$\pm$~0.03} & \textbf{0.851~$\pm$~0.09} & \textbf{0.789~$\pm$~0.06} & \textbf{0.767~$\pm$~0.06}     \tabularnewline
+			\textbf{Proposed} & \textbf{0.954{\tiny $\pm$}0.01} & \textbf{0.928{\tiny $\pm$}0.02} & \textbf{0.900{\tiny $\pm$}0.002} & \textbf{0.903{\tiny $\pm$}0.06} & \textbf{0.858{\tiny $\pm$}0.04} & \textbf{0.833{\tiny $\pm$}0.03} & \textbf{0.851{\tiny $\pm$}0.09} & \textbf{0.789{\tiny $\pm$}0.06} & \textbf{0.767{\tiny $\pm$}0.06}     \tabularnewline
 			\hline 
@@
 	}
+
 	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice score for different sampling ratios}{\footnotesize{}\label{tbl:DICE}}}
-\end{table}
 
-WHICH IS BETTER???
-\begin{table}[H]
-	\centering
-	\resizebox{\textwidth}{!}{%
-		\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
-			\hline 
-			\textbf{DICE} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
-			\cline{2-10} 
-			\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
-			\hline 
-			Zero-filled & 0.882$\pm$0.08 & 0.826$\pm$0.05 & 0.796$\pm$0.05 & 0.718$\pm$0.10 & 0.644$\pm$0.05 & 0.627$\pm$0.05 & 0.599$\pm$0.12 & 0.466$\pm$0.07 & 0.050$\pm$0.06\tabularnewline
-			\hline 
-			CS-MRI & 0.942$\pm$0.05 & 0.910$\pm$0.03 & 0.868$\pm$0.03 & 0.871$\pm$0.10 & 0.805$\pm$0.08 & 0.770$\pm$0.05 & 0.708$\pm$0.14 & 0.639$\pm$0.08 & 0.621$\pm$0.07     \tabularnewline
-			\hline 
-			CNN-L2 & 0.948$\pm$0.02 & 0.919$\pm$0.02 & 0.891$\pm$0.02 & 0.888$\pm$0.06 & 0.836$\pm$0.04 & 0.813$\pm$0.03 & 0.836$\pm$0.09 & 0.770$\pm$0.06 & 0.747$\pm$0.06     \tabularnewline
-			\hline
-
-			\textbf{Proposed} & \textbf{0.954$\pm$0.01} & \textbf{0.928$\pm$0.02} & \textbf{0.900$\pm$0.002} & \textbf{0.903$\pm$0.06} & \textbf{0.858$\pm$0.04} & \textbf{0.833$\pm$0.03} & \textbf{0.851$\pm$0.09} & \textbf{0.789$\pm$0.06} & \textbf{0.767$\pm$0.06}     \tabularnewline
-			\hline 
-		\end{tabular}
-	}
-	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice score for different sampling ratios}{\footnotesize{}\label{tbl:DICE2}}}
 \end{table}
@@
 %--------------------- CONCLUSIONS --------------------%
-\section{Conclusions}
+\section{Discussion}
 
-We proposed a software-only framework, using GANs for accelerating
-MRI acquisition. Specifically, high-quality MRI reconstruction using
-only 52\% of the original k-space data is demonstrated. The key idea
-is based on utilizing an adversarial loss in addition to L2 loss.
-It is worth mentioning that the proposed sampling mask is currently
-implemented in commercial MRI machines with no need for additional
-hardware or dedicated pulse programming. Future work will concentrate
-on generation of MRI in the presence of pathologies.
+We proposed a software-only framework, using GANs for accelerating MRI acquisition.
+Specifically, high-quality MRI reconstruction using only 40\%, 25\% and 16.6\% of the original k-space data is demonstrated.
+The key idea is based on utilizing an adversarial loss in addition to L2 loss.
+Extensive evaluation of the reconstruction quality was conducted in order to emphasize the advantage of proposed method.
+Future work will concentrate on generation of MRI in the presence of pathologies.
 

### 2018-01-01 paper.tex
update

@@
 We applied an image segmentation algorithm, FAST \cite{zhang2001segmentation}, on the original fully-sampled MR image and then use it for calculating the masked-PSNR on gray matters, white matters and the Cerebrospinal Fluid (CSF).
-results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}.
+Results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}.
 
@@
 		\hline 
+		IM-CNN-L2 & 42.992{\tiny $\pm$}3.81 & 38.827{\tiny $\pm$}3.69 & 39.922{\tiny $\pm$}3.11 & 40.574{\tiny $\pm$}2.66 & 37.102{\tiny $\pm$}2.90 & 38.473{\tiny $\pm$}2.31 & 34.742{\tiny $\pm$}2.89 & 31.496{\tiny $\pm$}2.43 & 33.710{\tiny $\pm$}1.80\tabularnewline
+		\hline 
 		CNN-L2 & 45.727{\tiny $\pm$}4.70 & 41.593{\tiny $\pm$}4.16 & 41.689{\tiny $\pm$}3.69 & 43.265{\tiny $\pm$}2.95 & 40.151{\tiny $\pm$}3.15 & 40.247{\tiny $\pm$}2.47 & 41.119{\tiny $\pm$}2.48 & 39.277{\tiny $\pm$}2.65 & 39.102{\tiny $\pm$}1.93\tabularnewline
@@
 
-ONLY 2 DIGITS
+ONLY 2 DIGITS - WHICH IS BETTER??
 \begin{table}[H]
@@
 			CS-MRI & 44.37{\tiny $\pm$}4.20 & 40.04{\tiny $\pm$}3.84 & 40.74{\tiny $\pm$}3.16 & 41.65{\tiny $\pm$}3.12 & 37.24{\tiny $\pm$}2.99 & 39.11{\tiny $\pm$}2.43 & 35.59{\tiny $\pm$}3.15 & 33.11{\tiny $\pm$}2.91 & 36.64{\tiny $\pm$}2.26\tabularnewline
+			\hline
+			IM-CNN-L2 & 42.99{\tiny $\pm$}3.81 & 38.82{\tiny $\pm$}3.69 & 39.92{\tiny $\pm$}3.11 & 40.57{\tiny $\pm$}2.66 & 37.10{\tiny $\pm$}2.90 & 38.47{\tiny $\pm$}2.31 & 34.74{\tiny $\pm$}2.89 & 31.49{\tiny $\pm$}2.43 & 33.71{\tiny $\pm$}1.80\tabularnewline
 			\hline  
@@
 		\begin{tabular}{>{\centering}b{0.2cm}lcccc}
-			& \multicolumn{1}{c}{\footnotesize Original} & {\footnotesize Zero-filled} & {\footnotesize CS-MRI} & {\footnotesize CNN-L2} & {\footnotesize Proposed}\tabularnewline
+			& \multicolumn{1}{c}{\footnotesize Original} & {\footnotesize Zero-filled} & {\footnotesize CS-MRI} & {\footnotesize IM-CNN-L2} & {\footnotesize Proposed}\tabularnewline
 			\multirow{1}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Reconstructed} \end{turn}} &
@@
 			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__50} &
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_50}
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_50}
 
@@
 			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_zoom_50} & 
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CNNL2_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_zoom_50}
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_zoom_50}
 
@@
  			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__50} &
-			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__predict_50}
+			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__IMCNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__predict_50}
 
@@
  			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__50} &
- 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__predict_50}
+ 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__IMCNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__predict_50}
 
@@
 		CS-MRI              &0.701~$\pm$~0.511  &1.447~$\pm$~1.027   &3.114~$\pm$~1.617\tabularnewline
+		IM-CNN-L2           &0.654~$\pm$~0.414  &0.878~$\pm$~0.548   &2.760~$\pm$~1.748\tabularnewline
 		CNN-L2              &0.420~$\pm$~0.270  &0.715~$\pm$~0.561   &1.083~$\pm$~1.052\tabularnewline
@@
 Dice score is a measure of sets similarity which gets the values between 0 (no similarity) to 1.0 (max similarity).
-Denotes by $S_{i,j}$ the set of pixels in segment $j$ for method $i$, the Dice between two methods for this segment is:
+Denotes by $S_{i,j}$ the set of pixels in segment $j$ for reconstruction method $i$, the Dice score between this method to the reference is:
 \begin{equation}
 \begin{array}{c}
-DICE(S_{1,j},S_{2,j}) = \frac{2\cdot|S_{1,j} \cap S_{2,j}|} {|S_{1,j}| + |S_{2,j}|}
+DICE(S_{ref,j},S_{i,j}) = \frac{2\cdot|S_{ref,j} \cap S_{i,j}|} {|S_{ref,j}| + |S_{i,j}|}
 \end{array}
 \end{equation}
-Dice values for different sampling ratios are presented in~Table~\ref{tbl:DICE}. Our methods archive the best Dice score for all the brain tissues.
+Dice values for different sampling ratios are presented in~Table~\ref{tbl:DICE}. Our methods achieved the best Dice score in all brain tissues.
 
@@
 			\hline
+
+			IM-CNN-L2 & 0.908{\tiny $\pm$}0.04 & 0.863{\tiny $\pm$}0.03 & 0.839{\tiny $\pm$}0.03 & 0.832{\tiny $\pm$}0.05 & 0.754{\tiny $\pm$}0.03 & 0.754{\tiny $\pm$}0.03 & 0.695{\tiny $\pm$}0.11 & 0.590{\tiny $\pm$}0.06 & 0.560{\tiny $\pm$}0.06     \tabularnewline
+			\hline
+
 			CNN-L2 & 0.948{\tiny $\pm$}0.02 & 0.919{\tiny $\pm$}0.02 & 0.891{\tiny $\pm$}0.02 & 0.888{\tiny $\pm$}0.06 & 0.836{\tiny $\pm$}0.04 & 0.813{\tiny $\pm$}0.03 & 0.836{\tiny $\pm$}0.09 & 0.770{\tiny $\pm$}0.06 & 0.747{\tiny $\pm$}0.06     \tabularnewline

### 2018-01-04 paper.tex
Update all paper, see red comments

@@
 \begin{keyword}
-\texttt MRI \sep GAN \sep Imaging
+\texttt MRI \sep GAN \sep Accelerated \sep K-space
 %\MSC[2010] 00-01\sep  99-00
@@
 
-The duration of standard single structural MRI acquisition is approximately
-5 minutes. Usually, several scans of different modalities or a sequence
-of scans are acquired such that the overall scan time is much longer.
-Lengthy imaging process reduces patient comfort and is more vulnerable
-to motion artifacts. In cases where motion is inevitable, e.g., fetal
-MRI, cardiac cine, and lungs imaging, scan time must be significantly
-shortened, otherwise the produced images might be useless. Moreover,
-in dynamic MRI sequences, acquisition must be brief such that the
-temporal resolution of the sequence would allow capturing significant
-temporal changes, e.g., instantaneous increment of the contrast-enhanced
-material concentration in DCE-MRI or differences in hemodynamic response
-expressed in fMRI \cite{moeller2010multiband}.
+The duration of standard single structural MRI acquisition is approximately 5 minutes.
+Usually, several scans of different modalities or a sequence of scans are acquired such that the overall scan time is much longer.
+Lengthy imaging process reduces patient comfort and is more vulnerable to motion artifacts.
+In cases where motion is inevitable, e.g., fetal MRI, cardiac cine, and lungs imaging, scan time must be significantly shortened, otherwise the produced images might be useless.
+Moreover, in dynamic MRI sequences, acquisition must be brief such that the temporal resolution of the sequence would allow capturing significant temporal changes, e.g., instantaneous increment of the contrast-enhanced material concentration in DCE-MRI or differences in hemodynamic response expressed in fMRI \cite{moeller2010multiband}.
 
-A straight forward reduction of the scan time can be obtained by sampling
-fewer slices, thus reducing the spatial resolution in the z-axis.
-Spatial distances between adjacent slices of fetal MRI or fMRI, for
-example, are often as high as 0.5 centimeters. Therefore, a significant
-portion of the potential input is not conveyed through imaging. On
-the other hand, under-sampling in the x-y domain leads to aliasing,
-as predicted by the Nyquist sampling theorem.
+A straight forward reduction of the scan time can be obtained by sampling fewer slices, thus reducing the spatial resolution in the z-axis.
+Spatial distances between adjacent slices of fetal MRI or fMRI, for example, are often as high as 0.5 centimeters.
+Therefore, a significant portion of the potential input is not conveyed through imaging.
+On the other hand, under-sampling in the x-y domain leads to aliasing, as predicted by the Nyquist sampling theorem.
 
-Numerous research groups as well as leading MRI scanner manufacturers
-make significant efforts to accelerate the MRI acquisition process.
-Hardware solutions allow parallel imaging by using multiple coils
-\cite{roemer1990nmr} to sample k-space data. There exist two major
-approaches~\cite{Deshmane2012} that are currently implemented in
-commercial MRI machines. Both reconstruct an image from the under-sampled
-k-space data provided by each of the coils. The sensitivity encoder
-(SENSE) transforms the partial k-spaces into images, then merges the
-resulting aliased images into one coherent image~\cite{pruessmann1999sense}.
-The GeneRalized Autocalibrating Partial Parallel Acquisition (GRAPPA)
-techniques~\cite{griswold2002generalized} operate on signal data
-within the complex frequency domain before the IFFT.
+Numerous research groups as well as leading MRI scanner manufacturers make significant efforts to accelerate the MRI acquisition process.
+Hardware solutions allow parallel imaging by using multiple coils \cite{roemer1990nmr} to sample k-space data.
+There exist two major approaches~\cite{Deshmane2012} that are currently implemented in commercial MRI machines.
+Both reconstruct an image from the under-sampled k-space data provided by each of the coils.
+The sensitivity encoder (SENSE) transforms the partial k-spaces into images, then merges the resulting aliased images into one coherent image~\cite{pruessmann1999sense}.
+The GeneRalized Autocalibrating Partial Parallel Acquisition (GRAPPA) techniques~\cite{griswold2002generalized} operate on signal data within the complex frequency domain before the IFFT.
 
-The compressed sensing (CS) technique~\cite{donoho2006compressed}
-allows efficient acquisition and reconstruction of a signal with fewer
-samples than the Nyquist-Shannon sampling theorem requires, if the
-signal has sparse representation in a known transform domain. Using
-CS for MRI reconstruction by sampling a small subset of the k-space
-grid had been proposed in~\cite{lustig2007sparse}. The underlying
-assumption is that the undersampling is random, such that the zero-filled
-Fourier reconstruction exhibits incoherent artifacts that behave similarly
-to additive random noise. This, however, would require specified pulse
-programming.
+The compressed sensing (CS) technique~\cite{donoho2006compressed} allows efficient acquisition and reconstruction of a signal with fewer samples than the Nyquist-Shannon sampling theorem requires, if the signal has sparse representation in a known transform domain.
+Using CS for MRI reconstruction by sampling a small subset of the k-space grid had been proposed in~\cite{lustig2007sparse}.
+The underlying assumption is that the undersampling is random, such that the zero-filled Fourier reconstruction exhibits incoherent artifacts that behave similarly to additive random noise.
+{\color{red}This, however, makes the algorithm less sensitive to fine details and noise like texture, results in smooth reconstruction with loss of diagnostically information, as we will see in section \ref{experiments_section}.}
+%This, however, would require specified pulse programming.
 
-Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast}
-and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary}
-were suggested for MRI reconstruction. MRI reconstruction using convolutional
-neural networks (CNN) was introduced in \cite{wang2016accelerating}.
-The network learns the mapping between zero-filled and fully-sampled
-MR images. In \cite{Oktay2016}, residual network was proposed for
-MRI super-resolution. Their model is able to receive multiple inputs
-acquired from different viewing planes for better image reconstruction.
-Both works address the reconstruction problems in the image domain
-rather than the k-space domain. The proposed framework utilizes recent
-advances in deep learning, while similarly to the CS methods addresses
-MRI reconstruction directly from the k-space. Specifically, we use
-generative adversarial networks (GAN) \cite{goodfellow2014generative,radford2015unsupervised,pathak2016context}.
-GANs are based on the inter-play between two networks: a generator
-and a discriminator. The generator is capable of learning the distribution
-over a data-base, and sample realizations of this distribution. The
-discriminator is trained to distinguish between `generated' samples
-and real ones. This powerful combination has been used for generating
-Computed Tomography (CT)-like images from MRIs~\cite{nie2016medical}.
-Here, the generator is used for reconstruction of the entire k-space
-grid from under-sampled data. Its loss is a combination of an adversarial
-loss, based on the discriminator output and a fidelity loss with respect
-to the fully sampled MRI. Promising results are obtained for brain
-MRI reconstruction using only 52\% of the data.
+Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction.
+MRI reconstruction using convolutional neural networks (CNN) was introduced in \cite{wang2016accelerating}.
+The network learns the mapping between zero-filled and fully-sampled MR images.
+In \cite{Oktay2016}, residual network was proposed for MRI super-resolution.
+Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction.
+In \cite{lee2017deep,hyun2017deep} a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} is used and provides good reconstruction MR images.
+Deep convolutional networks have been successfully applied to acceleration of dynamic MRI in \cite{sandinodeep}.
+All these works address the reconstruction problem in the image domain rather than the k-space domain.
 
-The paper is organized as follows. Section 2 presents some theoretical
-foundation and our method. Section 3 describes the experimental results.
-Conclusions and future directions are describes in section 4.
+The proposed framework utilizes recent advances in deep learning, while similarly to the CS methods addresses MRI reconstruction directly from the k-space.
+Specifically, we use generative adversarial networks (GAN) \cite{goodfellow2014generative,radford2015unsupervised,pathak2016context}.
+GANs are based on the inter-play between two networks: a generator and a discriminator.
+The generator is capable of learning the distribution over a data-base, and sample realizations of this distribution.
+The discriminator is trained to distinguish between `generated' samples and real ones.
+This powerful combination has been used for MRI acceleration in~\cite{yu2017deep,mardani2017deep}, and also for generating Computed Tomography (CT)-like images from MRIs~\cite{nie2016medical}.
+Here, the generator is used for reconstruction of the entire k-space grid from under-sampled data.
+Its loss is a combination of an adversarial loss, based on the discriminator output and a fidelity loss with respect to the fully sampled MRI.
+Promising results are obtained for brain MRI reconstruction using only 40\%, 25\% and 16.6\% of the data.
+
+The paper is organized as follows.
+Section \ref{method_section} presents some theoretical foundation and our method.
+Section \ref{experiments_section} describes the experimental results.
+Conclusions and future directions are describes in section \ref{conclusions_section}.
 
 %--------------------- METHOD --------------------%
-\section{Method}
+\section{Method}\label{method_section}
 
 \subsection{K-space}
-Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained
-by the IFFT of the complex k-space signal $s_{0}$. Let $M_{F}$ denote
-a full sampling mask such that the reconstructed MR image is: 
+Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained by the IFFT of the complex k-space signal $s_{0}$. Let $M_{F}$ denote a full sampling mask such that the reconstructed MR image is: 
 \begin{equation}
@@
 \end{equation} 
-where $H$ is the Hermitian transpose operation, $\odot$ denotes
-element-wise multiplication, and $F^{H}$ is an orthonormal 2D IFFT
-operator, such that $F^{H}F=I$. While sampling part of the k-space,
-using $M_{p}$ as a sampling mask, the reconstructed MR image suffers
-from artifacts and aliasing. An example artifacts caused by under-sampling in the phase axis using Gaussian mask (40\%)
-is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
+where $H$ is the Hermitian transpose operation, $\odot$ denotes element-wise multiplication, and $F^{H}$ is an orthonormal 2D IFFT operator, such that $F^{H}F=I$. 
+While sampling part of the k-space, using $M_{p}$ as a sampling mask, the reconstructed MR image suffers from artifacts and aliasing.
+An example artifacts caused by under-sampling in the phase axis using Gaussian mask (40\%) is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
 
@@
 
-Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space. Given
-a sampling mask and a model $f$, defined by the set of parameters
-$\Theta$, our goal is to estimate the missing k-space samples such
-that: 
+Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space.
+Given a sampling mask and a model $f$, defined by the set of parameters $\Theta$, our goal is to estimate the missing k-space samples such that:
 \begin{equation}
@@
 \end{equation}
-where $L\left(\cdot\right)$ is the loss function. While choosing
-the loss to be L2 norm is reasonable for natural images, for the k-space,
-which has different spatial features, this may not be enough. As mentioned
-in \cite{pathak2016context}, L2 minimization provides a blurry solution.
-Averaging the high frequency details in the k-space domain results
-in very poor reconstruction. In order to address this problem, we
-used the adversarial loss, based on GAN.
+where $L\left(\cdot\right)$ is the loss function.
+While choosing the loss to be L2 norm is reasonable for natural images, for the k-space, which has different spatial features, this may not be enough.
+As mentioned in \cite{pathak2016context}, L2 minimization provides a blurry solution, results in a loss of fine details.
+Averaging the high frequency details in the k-space domain results in very poor reconstruction. In order to address this problem, we used the adversarial loss, based on GAN.
 
-We trained our model using the adversarial strategy, as described
-in \cite{goodfellow2014generative,radford2015unsupervised}. This
-method is based on a generator $G$, which takes noise \textbf{$z$
-}with uniform distribution \textbf{$p_{u}\left(z\right)$} as input
-and generates samples from the data distribution. A discriminator
-$D$ is trained to distinguish between ``real'' examples from the
-data and generated (``fake'') examples from $G.$ During the training
-process, we optimize $G$ to maximize the discriminator's probability
-of error. Simultaneously, $D$ is getting better and provides more
+We trained our model using the adversarial strategy, as described in \cite{goodfellow2014generative,radford2015unsupervised}. 
+This method is based on a generator $G$, which takes noise \textbf{$z$ }with uniform distribution \textbf{$p_{u}\left(z\right)$} as input and generates samples from the data distribution.
+A discriminator $D$ is trained to distinguish between ``real'' examples from the data and generated (``fake'') examples from $G.$ During the training process, we optimize $G$ to maximize the discriminator's probability of error.
+Simultaneously, $D$ is getting better and provides more
 accurate predictions.
 
-Let $s_{0}$ denote a ``real'' k-space sample from the distribution
-$p_{r}\left(s_{0}\right)$. The following optimization process can
-be described by two-players min-max game:
+Let $s_{0}$ denote a ``real'' k-space sample from the distribution $p_{r}\left(s_{0}\right)$. The following optimization process can be described by two-players min-max game:
 
@@
 
-In equilibrium, the generator $G$ is able to generate samples that
-look like the real data. In our case, $G$ estimates the missing k-space
-samples from a linear combination of the sampled data and a uniform
-noise with distribution $p_{u}\left(z\right)$. An L2 fidelity constraint
-is added to the adverbial loss of the generator, as follows:
+In equilibrium, the generator $G$ is able to generate samples that look like the real data.
+In our case, $G$ estimates the missing k-space samples from a linear combination of the sampled data and a uniform noise with distribution $p_{u}\left(z\right)$.
+An L2 fidelity constraint is added to the adverbial loss of the generator, as follows:
 
@@
 \end{equation}
-where $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=0.8$
-are hyperparameters tuned by a cross-validation process. The discriminator's
-input is the reconstructed MR image,\textbf{ }i.e.,\textbf{ }after
-IFFT. By that, we are integrating the reconstruction phase in our
-optimization.
+where $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=1$ are hyperparameters tuned by a cross-validation process.
+The discriminator's input is the reconstructed MR image,\textbf{ }i.e.,\textbf{ }after IFFT.
+By that, we are integrating the reconstruction phase in our optimization.
+In this work, we use the Wasserstein distance as the GAN loss function~\cite{arjovsky2017wasserstein} which helps us to improve the training stability and provides better reconstruction than the classic GAN.
 
@@
 
-The generator input is a two-channel image representing the real and
-the imaginary parts of the partially sampled k-space image, $s_{p}$.
-Each missing sample is initialized by uniform i.i.d. noise. The pixel
-$\left(i,j\right)$ in the generator input image is: 
+The generator input is a two-channel image representing the real and the imaginary parts of the partially sampled k-space image, $s_{p}$.
+Each missing sample is initialized by uniform i.i.d.
+noise.
+The pixel $\left(i,j\right)$ in the generator input image is:
 \begin{equation}
@@
 
-Due to the combination of the adversarial and the fidelity loss, $G$
-produces reasonable k-space samples from a given samples and noise
-distribution $p_{u}\left(z\right)$. In order to use the sampled data,
-$s_{p}$, and estimate only the missing samples we used a residual
-network \cite{he2016deep} as used in \cite{Oktay2016}, such that:
+Due to the combination of the adversarial and the fidelity loss, $G$ produces reasonable k-space samples from a given samples and noise distribution $p_{u}\left(z\right)$.
+In order to use the sampled data, $s_{p}$, and estimate only the missing samples we used a residual network \cite{he2016deep} as used in \cite{Oktay2016}, such that:
 \begin{equation}
@@
 \end{equation}
-where $G_{out}$ is the generator output. Figure \ref{fig:system}
-describes our framework:
+where $G_{out}$ is the generator output. Figure \ref{fig:system} describes our framework:
 
@@
 
-A common architecture is used for the discriminator, composed of convolutional
-layers, batch normalization, and leaky-ReLU as suggested in \cite{radford2015unsupervised}.
-For the generator, we compose a dedicated architecture based on multi-channel
-input for representing the real and imaginary components. Both architectures
-are shown in Figure \ref{fig:test}.\textbf{ }The training methodology
-is doing $k_{g}$ generator update steps for each discriminator single
-step.
+A common architecture is used for the discriminator, composed of convolutional layers, batch normalization, and leaky-ReLU as suggested in \cite{radford2015unsupervised}.
+For the generator, we compose a dedicated architecture based on multi-channel input for representing the real and imaginary components.
+Both architectures are shown in Figure \ref{fig:test}.\textbf{ }The training methodology is doing $k_{d}$ discriminator update steps for each generator single step.
 
@@
 %--------------------- Experiments --------------------%
-\section{Experiments}
+\section{Experiments}\label{experiments_section}
 
@@
 IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding.
-We used the U-net \cite{ronneberger2015u} architecture inspired by \cite{lee2017deep}.
+%We used the U-net \cite{ronneberger2015u} architecture inspired by \cite{lee2017deep}. 
+We used the U-net \cite{ronneberger2015u} architecture and the same reconstruction method as presented in~\cite{hyun2017deep}.
+Specifically, we apply an FFT on the U-net image to get an estimated k-space.
+The fully k-space is then recovered by integrating the sampled k-space according to the sampling mask.
 The same sampling masks was used for all cases.
@@
 %--------------------- CONCLUSIONS --------------------%
-\section{Discussion}
+\section{Discussion}\label{conclusions_section}
 

### 2018-01-06 paper.tex
update

@@
 For the generator, we compose a dedicated architecture based on multi-channel input for representing the real and imaginary components.
-Both architectures are shown in Figure \ref{fig:test}.\textbf{ }The training methodology is doing $k_{d}$ discriminator update steps for each generator single step.
+Both architectures are shown in Figure \ref{fig:architectures}.\textbf{ }The training methodology is doing $k_{d}$ discriminator update steps for each generator single step.
 
-\begin{figure*}
+\begin{figure}[H]
 	\centering{}%
@@
 		\hline 
-		\subfloat[\textcolor{black}{\footnotesize{}Generator}]{\centering{}\includegraphics[width=12cm,height=2cm]{include/grp1/arch_generator}
+		\subfloat[\textcolor{black}{\footnotesize{}Generator}]{\centering{}\includegraphics[width=11cm,height=2cm]{include/grp2/generator_arch}
 
@@
 		\hline
-		\subfloat[\textcolor{black}{\footnotesize{}Discriminator}]{\centering{}\includegraphics[width=9cm,height=2cm]{include/grp1/arch_discriminator}
+
+		\subfloat[\textcolor{black}{\footnotesize{}Discriminator}]{\centering{}\includegraphics[width=11cm,height=2cm]{include/grp2/discrimonator_arch} 
+%		\subfloat[\textcolor{black}{\footnotesize{}Discriminator}]{\centering{}\includegraphics[width=9cm,height=2cm]{include/grp1/arch_discriminator}
 
@@
 		\hline 
-	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Networks architecture. The generator
-		input is a two-channel signal, real and imaginary. For each layer,
-		$k$ is the kernel size and $C$ is the number of output channels.}}
-\label{fig:test} 
-\end{figure*}
+	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Networks architecture.
+Both generator and discriminator input is a two-channel signal, real and imaginary.
+The number above each layer represents the output channels and all convolutional kernels are $3\times3$.}}
+\label{fig:architectures} 
+\end{figure}
 
@@
 In addition, we optimized two networks: 1.
-CNN-L2 - a k-space generator (with same architecture as the proposed method) using only L2 loss.
+CNN-L2 - a k-space generator (with same architecture as the proposed method) trained with only L2 loss.
 2.
@@
 
-A common metric used to quantify the reconstructed image quality is the PSNR.
-In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, brain's shape measure and tissue segmentation.
+A common metric used to quantify the reconstructed image quality is the PSNR and Struture Similarity Index (SSIM)~\cite{wang2004image}.
+In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, SSIM, brain's shape measure and tissue segmentation.
 
@@
 
-\subsection{Peak signal-to-noise ratio (PSNR)}
+\subsection{PSNR and SSIM}
+PSNR and SSIM are the most commonly used measures for evaluate image quality.
 PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image.
@@
 
-%\begin{table}[H]
-%	\centering{}
-%\begin{tabular}{|c||c|c||c|c||c|c|}
-%	\hline 
-%	\textbf{PSNR} & \multicolumn{2}{c||}{Factor 2.5} & \multicolumn{2}{c||}{Factor 4} & \multicolumn{2}{c|}{Factor 6}\tabularnewline \cline{2-7}
-%
-%	\textbf{Method}     &Mean   &std    &Mean   &std     &Mean   &std \tabularnewline \hline 	
-%	Zero-filled         &32.044 &2.616  &26.447 &1.997   &16.470 &2.181\tabularnewline
-%	CS-MRI              &39.053 &2.479  &33.273 &2.452   &26.951 &3.380\tabularnewline
-%	CNN-L2              &38.978 &2.454  &33.405 &2.232   &31.010 &2.299\tabularnewline
-%	\textbf{Proposed}   &39.802 &2.489  &34.595 &2.519   &31.555 &2.487\tabularnewline
-%		\hline 
-%	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, without masking}{\footnotesize{}\label{tbl:PSNR_NO_MASK}}}
-%\end{table}
-
 \begin{table}[H]
@@
 
-		Zero-filled         &32.044~$\pm$~2.616  &26.447~$\pm$~1.997   &16.470~$\pm$~2.181\tabularnewline
-		CS-MRI              &39.053~$\pm$~2.479  &33.273~$\pm$~2.452   &26.951~$\pm$~3.380\tabularnewline
-		IM-CNN-L2           &35.281~$\pm$~2.210  &31.577~$\pm$~2.109   &23.417~$\pm$~2.676\tabularnewline
-		CNN-L2              &38.978~$\pm$~2.454  &33.405~$\pm$~2.232   &31.010~$\pm$~2.299\tabularnewline
-		\textbf{Proposed}   &\textbf{39.802~$\pm$~2.489}  &\textbf{34.595~$\pm$~2.519}   &\textbf{31.555~$\pm$~2.487}\tabularnewline
+		Zero-filled         &32.555~$\pm$~2.294  &26.791~$\pm$~1.856 &16.781~$\pm$~1.737\tabularnewline
+		CS-MRI              &39.053~$\pm$~1.750  &33.088~$\pm$~1.929 &26.491~$\pm$~2.587\tabularnewline
+		IM-CNN-L2           &39.663~$\pm$~1.934  &35.042~$\pm$~2.042 &28.134~$\pm$~2.181\tabularnewline
+		CNN-L2              &39.394~$\pm$~1.985  &33.829~$\pm$~2.034 &31.403~$\pm$~2.040\tabularnewline
+		\textbf{Proposed}   &\textbf{40.211~$\pm$~1.902}  &\textbf{35.133~$\pm$~1.870}   &\textbf{32.040~$\pm$~2.110}\tabularnewline
 		\hline 
@@
 
-%\begin{table}[H]
-%	\centering
-%\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
-%	\hline 
-%	\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
-%	\cline{2-10} 
-%	 \textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
-%	 \hline 
-%	 Zero-filled & 41.494 & 36.736 & 38.546 & 37.279 & 34.379 & 36.369 & 24.887 & 24.987 & 29.337\tabularnewline
-%	 \hline 
-%	 CS-MRI & 44.374 & 40.042 & 40.744 & 41.655 & 37.247 & 39.119 & 35.595 & 33.111 & 36.648\tabularnewline
-%	 \hline 
-%	 CNN-L2 & 45.727 & 41.593 & 41.689 & 43.265 & 40.151 & 40.247 & 41.119 & 39.277 & 39.102\tabularnewline
-%	 \hline 
-%	 \textbf{Proposed} & 46.206 & 41.942 & 41.616 & 43.857 & 40.109 & 40.496 & 41.919 & 39.014 & 39.366\tabularnewline
-%	 \hline 
-%\end{tabular}
-%\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
-%\end{table}
-
-\begin{table}[H]
-	\centering
-	\resizebox{\textwidth}{!}{%
-		\scriptsize
-		\setlength\tabcolsep{2pt}
-	\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
-		\hline 
-		\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
-		\cline{2-10} 
-		\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
-		\hline 
-		Zero-filled & 41.494{\tiny $\pm$}3.48 & 36.736{\tiny $\pm$}3.32 & 38.546{\tiny $\pm$}2.45 & 37.279{\tiny $\pm$}2.18 & 34.379{\tiny $\pm$}2.52 & 36.369{\tiny $\pm$}1.87 & 24.887{\tiny $\pm$}1.62 & 24.987{\tiny $\pm$}1.91 & 29.337{\tiny $\pm$}2.08\tabularnewline
-		\hline 
-		CS-MRI & 44.374{\tiny $\pm$}4.20 & 40.042{\tiny $\pm$}3.84 & 40.744{\tiny $\pm$}3.16 & 41.655{\tiny $\pm$}3.12 & 37.247{\tiny $\pm$}2.99 & 39.119{\tiny $\pm$}2.43 & 35.595{\tiny $\pm$}3.15 & 33.111{\tiny $\pm$}2.91 & 36.648{\tiny $\pm$}2.26\tabularnewline
-		\hline 
-		IM-CNN-L2 & 42.992{\tiny $\pm$}3.81 & 38.827{\tiny $\pm$}3.69 & 39.922{\tiny $\pm$}3.11 & 40.574{\tiny $\pm$}2.66 & 37.102{\tiny $\pm$}2.90 & 38.473{\tiny $\pm$}2.31 & 34.742{\tiny $\pm$}2.89 & 31.496{\tiny $\pm$}2.43 & 33.710{\tiny $\pm$}1.80\tabularnewline
-		\hline 
-		CNN-L2 & 45.727{\tiny $\pm$}4.70 & 41.593{\tiny $\pm$}4.16 & 41.689{\tiny $\pm$}3.69 & 43.265{\tiny $\pm$}2.95 & 40.151{\tiny $\pm$}3.15 & 40.247{\tiny $\pm$}2.47 & 41.119{\tiny $\pm$}2.48 & 39.277{\tiny $\pm$}2.65 & 39.102{\tiny $\pm$}1.93\tabularnewline
-		\hline 
-		\textbf{Proposed} & \textbf{46.206{\tiny $\pm$}4.77} & \textbf{41.942{\tiny $\pm$}4.34} & \textbf{41.616{\tiny $\pm$}2.45} & \textbf{43.857{\tiny $\pm$}3.16} & \textbf{40.109{\tiny $\pm$}3.25} & \textbf{40.496{\tiny $\pm$}2.57} & \textbf{41.919{\tiny $\pm$}2.77} & \textbf{39.014{\tiny $\pm$}2.88} & \textbf{39.366{\tiny $\pm$}2.17}\tabularnewline
-		\hline 
-	\end{tabular}
-	}
-	\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
-\end{table}
-
-ONLY 2 DIGITS - WHICH IS BETTER??
 \begin{table}[H]
@@
 			\hline
-			IM-CNN-L2 & 42.99{\tiny $\pm$}3.81 & 38.82{\tiny $\pm$}3.69 & 39.92{\tiny $\pm$}3.11 & 40.57{\tiny $\pm$}2.66 & 37.10{\tiny $\pm$}2.90 & 38.47{\tiny $\pm$}2.31 & 34.74{\tiny $\pm$}2.89 & 31.49{\tiny $\pm$}2.43 & 33.71{\tiny $\pm$}1.80\tabularnewline
+%			IM-CNN-L2 & 42.99{\tiny $\pm$}3.81 & 38.82{\tiny $\pm$}3.69 & 39.92{\tiny $\pm$}3.11 & 40.57{\tiny $\pm$}2.66 & 37.10{\tiny $\pm$}2.90 & 38.47{\tiny $\pm$}2.31 & 34.74{\tiny $\pm$}2.89 & 31.49{\tiny $\pm$}2.43 & 33.71{\tiny $\pm$}1.80\tabularnewline
+			IM-CNN-L2  & 45.66{\tiny $\pm$}4.60 & 41.06{\tiny $\pm$}4.27 & 41.51{\tiny $\pm$}3.58 & 43.47{\tiny $\pm$}3.22 & 39.36{\tiny $\pm$}3.19 & 40.16{\tiny $\pm$}2.51 & 37.34{\tiny $\pm$}3.19 & 34.18{\tiny $\pm$}2.85 & 36.61{\tiny $\pm$}2.10\tabularnewline
 			\hline  
@@
 	\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK2}}}
+\end{table}
+
+SSIM is used for measuring the similarity between the original and the reconstructed images.
+It quantifies the degradation caused by sampling artifacts based on visible structures in the image. SSIM values for different sampling factors are presented in~Table~\ref{tbl:SSIM_NO_MASK}.
+
+\begin{table}[H]
+	\centering{}
+	\begin{tabular}{|c||c||c||c|}
+		\hline 
+		\textbf{SSIM} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6}} \tabularnewline
+		\textbf{Method} & \multicolumn{1}{c||}{} & \multicolumn{1}{c||}{} & \multicolumn{1}{c|}{} \tabularnewline \cline{1-4}
+
+		Zero-filled         &0.698~$\pm$~0.0452  &0.590~$\pm$~0.040   &0.255~$\pm$~0.021\tabularnewline
+		CS-MRI              &0.865~$\pm$~0.029  &0.757~$\pm$~0.037   &0.617~$\pm$~0.030\tabularnewline
+		IM-CNN-L2           &0.884~$\pm$~0.030  &0.796~$\pm$~0.036   &0.606~$\pm$~0.023\tabularnewline
+		CNN-L2              &0.885~$\pm$~0.030  &0.749~$\pm$~0.043   &0.682~$\pm$~0.042\tabularnewline
+		\textbf{Proposed}   &\textbf{0.917~$\pm$~0.019}  &\textbf{0.818~$\pm$~0.034}   &\textbf{0.726~$\pm$~0.038}\tabularnewline
+		\hline 
+	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}SSIM for different sampling factors}{\footnotesize{}\label{tbl:SSIM_NO_MASK}}}
 \end{table}
@@
 			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__50} &
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_50}
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_50}
 
@@
 			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_zoom_50} & 
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_zoom_50}
+			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2TUNE_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_zoom_50}
 
@@
  			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__50} &
-			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__IMCNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__predict_50}
+			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__predict_50}
 
@@
  			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__50} &
- 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__IMCNNL2_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__predict_50}
+ 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__predict_50}
 
@@
 		CS-MRI              &0.701~$\pm$~0.511  &1.447~$\pm$~1.027   &3.114~$\pm$~1.617\tabularnewline
-		IM-CNN-L2           &0.654~$\pm$~0.414  &0.878~$\pm$~0.548   &2.760~$\pm$~1.748\tabularnewline
+%		IM-CNN-L2           &0.654~$\pm$~0.414  &0.878~$\pm$~0.548   &2.760~$\pm$~1.748\tabularnewline
+		IM-CNN-L2           &0.541~$\pm$~0.388  &0.724~$\pm$~0.394   &1.902~$\pm$~1.437\tabularnewline
 		CNN-L2              &0.420~$\pm$~0.270  &0.715~$\pm$~0.561   &1.083~$\pm$~1.052\tabularnewline
@@
 
-			IM-CNN-L2 & 0.908{\tiny $\pm$}0.04 & 0.863{\tiny $\pm$}0.03 & 0.839{\tiny $\pm$}0.03 & 0.832{\tiny $\pm$}0.05 & 0.754{\tiny $\pm$}0.03 & 0.754{\tiny $\pm$}0.03 & 0.695{\tiny $\pm$}0.11 & 0.590{\tiny $\pm$}0.06 & 0.560{\tiny $\pm$}0.06     \tabularnewline
+%			IM-CNN-L2 & 0.908{\tiny $\pm$}0.04 & 0.863{\tiny $\pm$}0.03 & 0.839{\tiny $\pm$}0.03 & 0.832{\tiny $\pm$}0.05 & 0.754{\tiny $\pm$}0.03 & 0.754{\tiny $\pm$}0.03 & 0.695{\tiny $\pm$}0.11 & 0.590{\tiny $\pm$}0.06 & 0.560{\tiny $\pm$}0.06     \tabularnewline
+%			\hline
+
+			IM-CNN-L2  & 0.947{\tiny $\pm$}0.02 & 0.917{\tiny $\pm$}0.02 & 0.887{\tiny $\pm$}0.02 & 0.903{\tiny $\pm$}0.03 & 0.853{\tiny $\pm$}0.02 & 0.828{\tiny $\pm$}0.02 & 0.741{\tiny $\pm$}0.14 & 0.681{\tiny $\pm$}0.08 & 0.674{\tiny $\pm$}0.07     \tabularnewline
 			\hline
@@
 \section{Discussion}\label{conclusions_section}
+{\color{red}HERE WE NEED TO WRITE THE CONCLUSIONS,
+
+BETTER PSNR AND SSIM
+
+MORE REALISTIC AND FROM REAL DISTRIBUTION
+
+K-SPACE VS IMAGE SPACE
+
+EDGE VS BLURRY SOLUTION
+
+SO, WE NEED TO CHECK SEGMENTATIONS, BRAIN -> PRODUCE MEDICALLY ACCEPTABLE IMAGES
+
+ETC...
+}
 
@@
 
-\begin{figure}
-	\begin{raggedright}
-
-%		\hspace{-1.2cm}%
-		\begin{tabular}{>{\centering}b{0.2cm}lcccc}
-			& \multicolumn{1}{c}{{\footnotesize{}Original}} & {\footnotesize{}Zero-filled} & {\footnotesize{}CS-MRI} & {\footnotesize{}CNN-L2} & {\footnotesize{}Proposed}\tabularnewline
-			\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
-					{\footnotesize{}Reconstructed}
-				\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res1_org} & \includegraphics[width=2.5cm]{include/grp1/res1_zero} & \includegraphics[width=2.5cm]{include/grp1/res1_cs_red} & \includegraphics[width=2.5cm]{include/grp1/res1_L2_red} & \includegraphics[width=2.5cm]{include/grp1/res1_our}\tabularnewline
-				\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
-						{\footnotesize{}Zoom in}
-					\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res1_org_zoom} & \includegraphics[width=2.5cm]{include/grp1/res1_zero_zoom} & \includegraphics[width=2.5cm]{include/grp1/res1_cs_zoom} & \includegraphics[width=2.5cm]{include/grp1/res1_L2_zoom} & \includegraphics[width=2.5cm]{include/grp1/res1_our_zoom}\tabularnewline
-					\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
-							{\footnotesize{}Reconstructed}
-						\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res7_org} & \includegraphics[width=2.5cm]{include/grp1/res7_zero} & \includegraphics[width=2.5cm]{include/grp1/res7_cs_red} & \includegraphics[width=2.5cm]{include/grp1/res7_L2_red} & \includegraphics[width=2.5cm]{include/grp1/res7_our}\tabularnewline
-						\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
-								{\footnotesize{}Zoom in}
-							\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res7_org_zoom} & \includegraphics[width=2.5cm]{include/grp1/res7_zero_zoom} & \includegraphics[width=2.5cm]{include/grp1/res7_cs_zoom} & \includegraphics[width=2.5cm]{include/grp1/res7_L2_zoom} & \includegraphics[width=2.5cm]{include/grp1/res7_our_zoom}\tabularnewline
-							\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
-									{\footnotesize{}Reconstructed}
-								\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res11_org} & \includegraphics[width=2.5cm]{include/grp1/res11_zero} & \includegraphics[width=2.5cm]{include/grp1/res11_cs_red} & \includegraphics[width=2.5cm]{include/grp1/res11_L2_red} & \includegraphics[width=2.5cm]{include/grp1/res11_our}\tabularnewline
-								\multirow{1}{0.2cm}[2cm]{\begin{turn}{90}
-										{\footnotesize{}Zoom in}
-									\end{turn}} & \includegraphics[width=2.5cm]{include/grp1/res11_org_zoom} & \includegraphics[width=2.5cm]{include/grp1/res11_zero_zoom} & \includegraphics[width=2.5cm]{include/grp1/res11_cs_zoom} & \includegraphics[width=2.5cm]{include/grp1/res11_L2_zoom} & \includegraphics[width=2.5cm]{include/grp1/res11_our_zoom}\tabularnewline
-								\end{tabular}
-								\par\end{raggedright}
-							\raggedright{}\caption{\textcolor{black}{\footnotesize{}Examples of reconstructed MR images
-									from under-sampled k-space.}}
-							\label{fig:results} 
-						\end{figure}
-
+%-----------------------------BIBLIOGRAPHY--------------------%
 \bibliography{paper}

### 2018-01-08 paper.tex
Update factors 2.5, 4

@@
 
+%\begin{figure}[H]
+%	\centering{}\includegraphics[width=7.8cm,height=4cm]{include/grp1/chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
+%			architecture: $G$ and $D$ are the generator and discriminator networks,
+%			respectively. $F$ is a $2D$ IFFT operator.}}
+%\end{figure}
+
 \begin{figure}[H]
-	\centering{}\includegraphics[width=7.8cm,height=4cm]{include/grp1/chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
+	\centering{}\includegraphics[width=12.0cm,height=4cm]{include/grp2/system_chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
 			architecture: $G$ and $D$ are the generator and discriminator networks,
-			respectively. $F$ is a $2D$ IFFT operator.}}
+			respectively.}}
 \end{figure}
@@
 
-%TODO:add after images
-%Visual comparison is shown in Figure~\ref{fig:results}. MRIs reconstructed by using the suggested adversarial loss have stronger contrast and no significant aliasing or artifacts.
-
-\begin{figure}[H]
-	\begin{raggedright}
-		\begin{tabular}{>{\centering}b{0.2cm}lcccc}
-			& \multicolumn{1}{c}{\footnotesize Original} & {\footnotesize Zero-filled} & {\footnotesize CS-MRI} & {\footnotesize IM-CNN-L2} & {\footnotesize Proposed}\tabularnewline
-			\multirow{1}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Reconstructed} \end{turn}} &
-
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__50} &
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_50}
-
-			 \tabularnewline
-
-			 \multirow{1}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Zoom in} \end{turn}} &
-
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zoom_50} &
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_zoom_50} & 
-			 \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2TUNE_zoom_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_zoom_50}
-
-			 \tabularnewline
-
-			\multirow{2}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Brain} \end{turn}} &
-
- 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__50} &
-			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__predict_50}
-
-			\tabularnewline
-
-			\multirow{2}{0.2cm}[2cm]{\begin{turn}{90} {\footnotesize Segmentation} \end{turn}} &
-
- 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__50} &
- 			\includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__zeroPadding_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__predict_50}
-
-		\end{tabular}
-	\par\end{raggedright}
-	\raggedright{}\caption{\textcolor{black}{\footnotesize{}Examples of reconstructed MR images from under-sampled k-space.}}
-	\label{fig:example} 
-\end{figure}
-
 \subsection{Brain Extraction - Skull Stripping}
@@
 
+Visual comparison for sampling factor 6 is shown in Figure~\ref{fig:example_factor_6}.
+The first and the second rows are the reconstructed images with zoom in of red ROI.
+The third row is the extracted brain and the last row is the calculated segmentation.
+Each column represents different reconstruction method.
+MRIs reconstructed by using the suggested adversarial method have stronger contrast and no significant aliasing or artifacts.
+In addition the brain extraction and the segmentation are more accurate.
+Additional examples for factor 4 and 2.5 can be found in Figures~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}.
+
+% Examples factor 6
+\begin{figure}[H]
+	%	\begin{raggedright}
+	\begin{raggedleft}
+		%		\begin{tabular}{>{\centering}b{0.2cm}lcccc}
+		\hspace*{-2cm} \begin{tabular}{cccccc}
+			& \multicolumn{1}{c}{\footnotesize Original} & {\footnotesize Zero-filled} & {\footnotesize CS-MRI} & {\footnotesize IM-CNN-L2} & {\footnotesize Proposed}\tabularnewline
+			\multirow{1}{0.05cm}[1.8cm]{\begin{turn}{90} {\footnotesize Reconstructed} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__50} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_50}
+
+			\tabularnewline
+
+			\multirow{1}{0.05cm}[1.3cm]{\begin{turn}{90} {\footnotesize Zoom in} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zoom_50} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__zeroPadding_zoom_50} & 
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__CS_zoom_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__IMCNNL2TUNE_zoom_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_images__predict_zoom_50}
+
+			\tabularnewline
+
+			\multirow{2}{0.05cm}[1.4cm]{\begin{turn}{90} {\footnotesize Brain} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__50} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__zeroPadding_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__CS_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_brains__predict_50}
+
+			\tabularnewline
+
+			\multirow{2}{0.05cm}[1.7cm]{\begin{turn}{90} {\footnotesize Segmentation} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__50} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__zeroPadding_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__CS_50} & \includegraphics[width=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__IMCNNL2TUNE_50} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor6/022-Guys-0701-T1/022-Guys-0701-T1_segs__predict_50}
+
+		\end{tabular}
+		\par\end{raggedleft}
+	\raggedright{}\caption{\textcolor{black}{\footnotesize{}Examples of reconstructed MR images from under-sampled k-space - Factor 6.}}
+	\label{fig:example_factor_6} 
+\end{figure}
+
 %--------------------- CONCLUSIONS --------------------%
@@
 
+% Examples factor 4
+\begin{figure}[H]
+	%	\begin{raggedright}
+	\begin{raggedleft}
+		%		\begin{tabular}{>{\centering}b{0.2cm}lcccc}
+		\hspace*{-2cm} \begin{tabular}{cccccc}
+			& \multicolumn{1}{c}{\footnotesize Original} & {\footnotesize Zero-filled} & {\footnotesize CS-MRI} & {\footnotesize IM-CNN-L2} & {\footnotesize Proposed}\tabularnewline
+			\multirow{1}{0.05cm}[1.8cm]{\begin{turn}{90} {\footnotesize Reconstructed} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__35} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__zeroPadding_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__CS_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__IMCNNL2TUNE_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__predict_35}
+
+			\tabularnewline
+
+			\multirow{1}{0.05cm}[1.3cm]{\begin{turn}{90} {\footnotesize Zoom in} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__zoom_35} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__zeroPadding_zoom_35} & 
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__CS_zoom_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__IMCNNL2TUNE_zoom_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_images__predict_zoom_35}
+
+			\tabularnewline
+
+			\multirow{2}{0.05cm}[1.4cm]{\begin{turn}{90} {\footnotesize Brain} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_brains__35} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_brains__zeroPadding_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_brains__CS_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_brains__IMCNNL2TUNE_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_brains__predict_35}
+
+			\tabularnewline
+
+			\multirow{2}{0.05cm}[1.7cm]{\begin{turn}{90} {\footnotesize Segmentation} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_segs__35} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_segs__zeroPadding_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_segs__CS_35} & \includegraphics[width=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_segs__IMCNNL2TUNE_35} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor4/012-HH-1211-T1/012-HH-1211-T1_segs__predict_35}
+
+		\end{tabular}
+		\par\end{raggedleft}
+	\raggedright{}\caption{\textcolor{black}{\footnotesize{}Examples of reconstructed MR images from under-sampled k-space - Factor 4.}}
+	\label{fig:example_factor_4} 
+\end{figure}
+
+% Examples factor 2.5
+\begin{figure}[H]
+	%	\begin{raggedright}
+	\begin{raggedleft}
+		%		\begin{tabular}{>{\centering}b{0.2cm}lcccc}
+		\hspace*{-2cm} \begin{tabular}{cccccc}
+			& \multicolumn{1}{c}{\footnotesize Original} & {\footnotesize Zero-filled} & {\footnotesize CS-MRI} & {\footnotesize IM-CNN-L2} & {\footnotesize Proposed}\tabularnewline
+			\multirow{1}{0.05cm}[1.8cm]{\begin{turn}{90} {\footnotesize Reconstructed} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__78} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__zeroPadding_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__CS_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__IMCNNL2TUNE_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__predict_78}
+
+			\tabularnewline
+
+			\multirow{1}{0.05cm}[1.3cm]{\begin{turn}{90} {\footnotesize Zoom in} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__zoom_78} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__zeroPadding_zoom_78} & 
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__CS_zoom_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__IMCNNL2TUNE_zoom_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_images__predict_zoom_78}
+
+			\tabularnewline
+
+			\multirow{2}{0.05cm}[1.4cm]{\begin{turn}{90} {\footnotesize Brain} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_brains__78} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_brains__zeroPadding_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_brains__CS_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_brains__IMCNNL2TUNE_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_brains__predict_78}
+
+			\tabularnewline
+
+			\multirow{2}{0.05cm}[1.7cm]{\begin{turn}{90} {\footnotesize Segmentation} \end{turn}} &
+
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_segs__78} &
+			\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_segs__zeroPadding_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_segs__CS_78} & \includegraphics[width=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_segs__IMCNNL2TUNE_78} & \includegraphics[width=2.5cm,height=2.5cm]{include/grp2/factor2/019-Guys-0702-T1/019-Guys-0702-T1_segs__predict_78}
+
+		\end{tabular}
+		\par\end{raggedleft}
+	\raggedright{}\caption{\textcolor{black}{\footnotesize{}Examples of reconstructed MR images from under-sampled k-space - Factor 2.5.}}
+	\label{fig:example_factor_2.5} 
+\end{figure}
+
 %-----------------------------BIBLIOGRAPHY--------------------%

### 2018-01-16 paper.tex
Update with tammy

@@
 
-We introduce a practical, software-only framework, based on deep learning, for accelerating MRI scan time allows maintaining good quality imaging.
-This is accomplished by partial MRI sampling, while using an adversarial neural network to estimate the missing samples.
+We introduce a practical, software-only framework, based on deep learning, for accelerating MRI acquisition, while maintaining anatomically meaningful imaging.
+This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples.
 The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to a fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR).
-Promising image reconstruction results are obtained for 3T and 1.5T MRI where only 40\%, 25\% and 16.6\% of the original data are used.
-Extended performance assessment was conducted in order to emphasize the advantage of proposed method.
+Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from large publicly available dataset, where only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
+To assess the clinical usability of the reconstructed images we also performed tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
+Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.
+
 \end{abstract}
@@
 \begin{keyword}
-\texttt MRI \sep GAN \sep Accelerated \sep K-space
+\text Accelerated MRI \sep Adversarial Loss \sep Deep Neural Network \sep K-space
 %\MSC[2010] 00-01\sep  99-00
@@
 The underlying assumption is that the undersampling is random, such that the zero-filled Fourier reconstruction exhibits incoherent artifacts that behave similarly to additive random noise.
-{\color{red}This, however, makes the algorithm less sensitive to fine details and noise like texture, results in smooth reconstruction with loss of diagnostically information, as we will see in section \ref{experiments_section}.}
+The smooth reconstruction obtained by the CS, may result in a loss of noise-like texture that can be anatomically meaningful.
+
+%{\color{red}This, however, makes the algorithm less sensitive to fine details and noise like texture, results in smooth reconstruction with loss of diagnostically information, as we will see in section \ref{experiments_section}.}
 %This, however, would require specified pulse programming.
@@
 Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction.
-MRI reconstruction using convolutional neural networks (CNN) was introduced in \cite{wang2016accelerating}.
-The network learns the mapping between zero-filled and fully-sampled MR images.
+MRI reconstruction using convolutional neural networks (CNN) which learns the mapping between zero-filled and fully-sampled MR images was introduced in \cite{wang2016accelerating}.
 In \cite{Oktay2016}, residual network was proposed for MRI super-resolution.

### 2018-01-19 paper.tex
Updates

@@
 
-Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction.
+{\color{blue}
+
+Recently different data driven, machine learning techniques were used for MRI acceleration. 
+%Manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction.
+
+In~\cite{usman2014compressive} a manifold structure is reconstructed directly from the k-space data, where kernel regression is used for full image reconstruction.
+
+Dynamic MRI reconstruction using manifold learning was suggested in~\cite{bhatia2014hierarchical} using image patches and in~\cite{usman2014compressive, bhatia2015fast} using direct k-space sampling.
+
+Manifold learning of the image space~\cite{bhatia2014hierarchical} and k-space data~\cite{usman2014compressive, bhatia2015fast} was suggested for dynamic MRI reconstruction.
+In~\cite{bhatia2015fast} a kernel regression along the manifold structure of the sequence derived directly from the k-space data is used for full image reconstruction.
+}
+%The method is based on kernel regression along the manifold structure of the sequence derived directly from k-space data.
+
 MRI reconstruction using convolutional neural networks (CNN) which learns the mapping between zero-filled and fully-sampled MR images was introduced in \cite{wang2016accelerating}.
-In \cite{Oktay2016}, residual network was proposed for MRI super-resolution.
+In \cite{Oktay2016}, residual CNN was proposed for MRI super-resolution.
 Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction.

### 2018-01-19 paper.tex
Extand intro

--- 2018-01-16 paper.tex
@@
 
-Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction.
+{\color{blue}
+
+Recently different data driven, machine learning techniques were used for MRI acceleration. 
+Ravishankar and Bresler~\cite{ravishankar2011mr} proposed a patch dictionary learning based method, for exploit the correlation between image patches in a static image in order to reconstruct MRI from highly under-sampled k-space data.
+In~\cite{caballero2014dictionary}, an iterative algorithm for dictionary learning used for reconstruction of cardiac cine data with Cartesian k-space under sampling.
+
+Manifold learning has been applied to reconstruction of dynamic MRI in many works.
+In~\cite{bhatia2014hierarchical}, an hierarchical manifold learned from MR image patches, while each path manifold was consistent with the manifold trained on the entire image.
+In~\cite{usman2014compressive, bhatia2015fast}, a compressive manifold structure, based on Laplacian eigenmaps, is reconstructed directly from the k-space.
+The first aims to estimate respiratory motion while the second make use of kernel regression for estimate cardiac motion.
+}
+
+A deep learning based methods open the gate to learn the reconstruction from a fully-sampled MR images.
 MRI reconstruction using convolutional neural networks (CNN) which learns the mapping between zero-filled and fully-sampled MR images was introduced in \cite{wang2016accelerating}.
-In \cite{Oktay2016}, residual network was proposed for MRI super-resolution.
+In \cite{Oktay2016}, residual CNN was proposed for MRI super-resolution.
 Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction.
-In \cite{lee2017deep,hyun2017deep} a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} is used and provides good reconstruction MR images.
-Deep convolutional networks have been successfully applied to acceleration of dynamic MRI in \cite{sandinodeep}.
+
+Both~\cite{lee2017deep,hyun2017deep} suggests a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} for reconstruction of MR images.
+In~\cite{lee2017deep}, the CS problem was formulate as a residual regression problem and solved by a deep convolutional neural network that learned the aliasing artifacts.
+In~\cite{hyun2017deep}, the U-net corrected MR output image, is used for estimate the missing k-space samples.
+The fully k-space is then recovered by integrating the sampled k-space according to the sampling mask.
+Also for dynamic MRI reconstruction, a deep CNN has been successfully applied in~\cite{sandinodeep} and provides better results over the time-consuming CS method.
 All these works address the reconstruction problem in the image domain rather than the k-space domain.
@@
 Its loss is a combination of an adversarial loss, based on the discriminator output and a fidelity loss with respect to the fully sampled MRI.
+
+{\color{red}
+We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
+In addition, we optimized two networks: 1.
+CNN-L2 - a k-space generator (with same architecture as the proposed method) trained with only L2 loss.
+2.
+IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding
 Promising results are obtained for brain MRI reconstruction using only 40\%, 25\% and 16.6\% of the data.
+
+To assess the clinical usability of the reconstructed images we performed extended validation, anatomy and quantitative measurements.
+
+tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
+Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.
 
@@
 Conclusions and future directions are describes in section \ref{conclusions_section}.
-
+}
 %--------------------- METHOD --------------------%

### 2018-01-20 paper.tex
Update intro and discussion

@@
 To assess the clinical usability of the reconstructed images we also performed tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
-Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.
+Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate the quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.
 
@@
 
-{\color{blue}
-
 Recently different data driven, machine learning techniques were used for MRI acceleration. 
@@
 The first aims to estimate respiratory motion while the second make use of kernel regression for estimate cardiac motion.
-}
 
@@
 In~\cite{lee2017deep}, the CS problem was formulate as a residual regression problem and solved by a deep convolutional neural network that learned the aliasing artifacts.
-In~\cite{hyun2017deep}, the U-net corrected MR output image, is used for estimate the missing k-space samples.
+In~\cite{hyun2017deep}, the U-net MR output image, is used for estimate the missing k-space samples.
 The fully k-space is then recovered by integrating the sampled k-space according to the sampling mask.
@@
 
-{\color{red}
 We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
-In addition, we optimized two networks: 1.
+In addition, we optimize two networks: 1.
 CNN-L2 - a k-space generator (with same architecture as the proposed method) trained with only L2 loss.
 2.
-IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding
-Promising results are obtained for brain MRI reconstruction using only 40\%, 25\% and 16.6\% of the data.
-
-To assess the clinical usability of the reconstructed images we performed extended validation, anatomy and quantitative measurements.
-
-tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
-Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.
+IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding.
+To assess the clinical usability of the reconstructed images we perform an extended validation, composed of anatomy and quantitative measurements.
+In addition to the common used PSNR and Structure Similarity Index (SSIM) we perform tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
+Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
+The proposed method outperforms the other in 3T and 1.5T brain MRI reconstruction, using a large publicly available dataset, where only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
+Moreover, compared to the widely used CS-MRI, the proposed method is faster in a two orders of magnitude.
+This makes it possible to use it in a real time manner.
 
@@
 Conclusions and future directions are describes in section \ref{conclusions_section}.
-}
+
 %--------------------- METHOD --------------------%
@@
 In our case, $G$ estimates the missing k-space samples from a linear combination of the sampled data and a uniform noise with distribution $p_{u}\left(z\right)$.
-An L2 fidelity constraint is added to the adverbial loss of the generator, as follows:
+An L2 fidelity constraint is added to the adversarial loss of the generator, as follows:
 
@@
 The training data consists of 500 $3D$ brain MRI (T1) scans of different patients from the IXI dataset\footnote{\url{http://brain-development.org/ixi-dataset/}}.
-The data has been acquired by three MR machines, Philips 1.5T, 3T and GE 1.5.
+The data has been acquired by three MR machines, Philips 1.5T, 3T and GE 1.5T.
 All images padded to resolution of $256\times256$ pixels.
@@
 In order to create k-space images for training, inverse orthonormal
-2D FFT is applied to the fully-sampled MR images. We sample the k-space
-using $2D$ Gaussian mask with sampling factor of 2.5, 4 and 6. Data augmentation
-is created by random offsets of the proposed mask and image flipping.
-This leads us to reconstruction of the MR image from 40\%, 25\% and 16.6\% (Figure~\ref{fig:sampling_masks}) of
-the original k-space data.
+2D FFT is applied to the fully-sampled MR images. 
+Further to our work~\cite{shitrit2017accelerated}, which was focused on Cartesian 2D sampling mask along the phase axis, we sample the k-space using $2D$ Gaussian mask, and achieve higher sampling factors of 2.5, 4 and 6 (Figure~\ref{fig:sampling_masks}).
+Data augmentation is created by random offsets of the proposed mask and image flipping. This leads us to reconstruction of the MR image from 40\%, 25\% and 16.6\% of the original k-space data.
 
@@
 We used the U-net \cite{ronneberger2015u} architecture and the same reconstruction method as presented in~\cite{hyun2017deep}.
-Specifically, we apply an FFT on the U-net image to get an estimated k-space.
+Specifically, we apply an FFT on the U-net output image to get an estimated k-space.
 The fully k-space is then recovered by integrating the sampled k-space according to the sampling mask.
-The same sampling masks was used for all cases.
+The same sampling masks was used for all methods.
 
-A common metric used to quantify the reconstructed image quality is the PSNR and Struture Similarity Index (SSIM)~\cite{wang2004image}.
-In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, SSIM, brain's shape measure and tissue segmentation.
+To assess the clinical usability of the reconstructed images we perform an extended validation, composed of anatomy and quantitative measurements.
+In addition to the common used PSNR and Structure Similarity Index (SSIM)~\cite{wang2004image} metrics, we perform tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
+The segmentation compatibility is measured in terms of Dice scores and Hausdorff distances.
 
@@
 \subsection{PSNR and SSIM}
-PSNR and SSIM are the most commonly used measures for evaluate image quality.
+PSNR and SSIM are the most commonly used measures for evaluate image reconstruction quality.
 PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image.
-Therefore, this measure is not a sufficient metric for edges and general shape.
-For example, a model can provides a good reconstruction in the sense of PSNR but with blurry edges, which results in a poor performance of algorithms that use them, for example segmentation.
+Therefore, this measure is not a sufficient metric for edges and general objects shape.
+For example, a model can provides a good reconstruction in the sense of PSNR but with blurry edges and loss of anatomical fine details.
+This leads to a poor segmentation, which used for medical diagnostic.
 However, PSNR is still a good indication for the image quality, especially if an expert should view it.
@@
 
-An extended validation of our model done by calculating the PSNR measure on different brain tissues.
-We applied an image segmentation algorithm, FAST \cite{zhang2001segmentation}, on the original fully-sampled MR image and then use it for calculating the masked-PSNR on gray matters, white matters and the Cerebrospinal Fluid (CSF).
+An additional validation of our model done by calculating the PSNR measure on different brain tissues.
+We applied an image segmentation algorithm, FAST~\cite{zhang2001segmentation}, on the original fully-sampled MR image and then use it for calculating the masked-PSNR on gray matters, white matters and the Cerebrospinal Fluid (CSF).
 Results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}.
@@
 	}
-	\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK2}}}
+	\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
 \end{table}
@@
 
-Let $C_1,C_2\in R^2$ denotes the brain contours extract from skull stripping algorithm on two different reconstruction methods respectively. MHD measures the distance between the contours such that:
+Let $C_1,C_2\in R^2$ denotes the brain contours extract from skull stripping algorithm on two different reconstruction methods respectively (in our case the fully-sampled and the tested reconstruction method).
+MHD measures the distance between the contours such that:
 
@@
 This process is of a great importance for brain MR image analysis, especially for therapy planning and also for clinical research.
-Sampling artifacts, results in poor signal to noise and blurry edges, may hurts the algorithm performance.
+Sampling artifacts, results in poor signal to noise and blurry edges, and also loss of anatomical fine details, will probably leads to bad segmentation performance.
 We suggest a way to evaluate and compare different MRI reconstruction methods based on segmentation results.
-We create a reference by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and run a brain segmentation algorithm (FAST \cite{zhang2001segmentation}).
+We create a reference segmentation by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and run a brain segmentation algorithm (FAST \cite{zhang2001segmentation}).
 Then, we did the same process for all the reconstruction methods and compared the segmentation results to the reference.
@@
 \end{equation}
-Dice values for different sampling ratios are presented in~Table~\ref{tbl:DICE}. Our methods achieved the best Dice score in all brain tissues.
+Dice values for different sampling ratios are presented in~Table~\ref{tbl:DICE}. Our methods achieved the best Dice scores for all brain tissues.
 
@@
 \section{Discussion}\label{conclusions_section}
-{\color{red}HERE WE NEED TO WRITE THE CONCLUSIONS,
 
-BETTER PSNR AND SSIM
+We proposed a practical, software-only framework, based on deep learning, for accelerating MRI acquisition, while maintaining anatomically meaningful imaging.
+This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples (based on the real k-space distribution).
+Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from large publicly available dataset, where only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
 
-MORE REALISTIC AND FROM REAL DISTRIBUTION
+Our method produce more clinically acceptable reconstructions compared with the methods being tested in the terms of PSNR and SSIM.
+We also perform tissue segmentations and measure the performance using the Dice scores, with respect to those obtained by using the original fully-sampled images.
+Better Dice score for white matter, gray matter, and CSF were achieved for all sampling factors.
+Moreover, lower Hausdorff distances indicates the quality of the proposed method in terms of general brain shape.
+Comparing to CS, our reconstruction method preserve the brain shape better, as seen in Figures~\ref{fig:example_factor_6},~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}.
 
-K-SPACE VS IMAGE SPACE
+Additional advantage of the proposed method is the runtime.
+A few days are required for training the generator.
+Once the network is optimized, the reconstruction for a single test image is done in less than 10 msec, almost two orders of magnitude faster than the widely used CS.
+This fact makes it possible to use it in a real time manner.
+Future work will concentrate on generation of MRI in the presence of pathologies.
 
-EDGE VS BLURRY SOLUTION
-
-SO, WE NEED TO CHECK SEGMENTATIONS, BRAIN -> PRODUCE MEDICALLY ACCEPTABLE IMAGES
-
-ETC...
+{\color{red}
+Do we need to discuss about :
+K-SPACE VS IMAGE SPACE ??
 }
-
-We proposed a software-only framework, using GANs for accelerating MRI acquisition.
-Specifically, high-quality MRI reconstruction using only 40\%, 25\% and 16.6\% of the original k-space data is demonstrated.
-The key idea is based on utilizing an adversarial loss in addition to L2 loss.
-Extensive evaluation of the reconstruction quality was conducted in order to emphasize the advantage of proposed method.
-Future work will concentrate on generation of MRI in the presence of pathologies.
 

### 2018-01-23 paper.tex
Update acknow

@@
 \subsection{Acknowledgment}
-This research is partially supported by the Israel Science Foundation (T.R.R. 1638/16 ) and the IDF Medical Corps (T.R.R.)
+This study was partially supported by The Israel Science Foundation (1638/16); The Israel Defense Forces (IDF) Medical Corps and Directorate of Defense Research \& Development, Israeli Ministry of Defense (IMOD DDR\&D); The Israeli ministry of science, technology and space (63551).
+%This research is partially supported by the Israel Science Foundation (T.R.R. 1638/16 ) and the IDF Medical Corps (T.R.R.)
 

### 2018-01-25 paper.tex
Update with Tammy

@@
 %This, however, would require specified pulse programming.
+Recently different data driven, machine learning techniques were used for MRI acceleration. 
+Ravishankar and Bresler~\cite{ravishankar2011mr} proposed a dictionary-based learning method, to exploit the sparsity of overlapping image patches emphasizing local structure, to reconstruct MRI from highly under-sampled k-space data.
+In~\cite{caballero2014dictionary}, this concept was extended using spatio-temporal patches for dynamic MRI reconstruction.
+Compressed manifold learning based on Laplacian eigenmaps, has been applied to partially in~\cite{usman2014compressive} for respiratory motion estimation and in~\cite{bhatia2015fast} for cardiac MRI reconstruction.
 
-Recently different data driven, machine learning techniques were used for MRI acceleration. 
-Ravishankar and Bresler~\cite{ravishankar2011mr} proposed a patch dictionary learning based method, for exploit the correlation between image patches in a static image in order to reconstruct MRI from highly under-sampled k-space data.
-In~\cite{caballero2014dictionary}, an iterative algorithm for dictionary learning used for reconstruction of cardiac cine data with Cartesian k-space under sampling.
-
-Manifold learning has been applied to reconstruction of dynamic MRI in many works.
-In~\cite{bhatia2014hierarchical}, an hierarchical manifold learned from MR image patches, while each path manifold was consistent with the manifold trained on the entire image.
-In~\cite{usman2014compressive, bhatia2015fast}, a compressive manifold structure, based on Laplacian eigenmaps, is reconstructed directly from the k-space.
-The first aims to estimate respiratory motion while the second make use of kernel regression for estimate cardiac motion.
-
-A deep learning based methods open the gate to learn the reconstruction from a fully-sampled MR images.
-MRI reconstruction using convolutional neural networks (CNN) which learns the mapping between zero-filled and fully-sampled MR images was introduced in \cite{wang2016accelerating}.
-In \cite{Oktay2016}, residual CNN was proposed for MRI super-resolution.
-Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction.
-
-Both~\cite{lee2017deep,hyun2017deep} suggests a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} for reconstruction of MR images.
-In~\cite{lee2017deep}, the CS problem was formulate as a residual regression problem and solved by a deep convolutional neural network that learned the aliasing artifacts.
-In~\cite{hyun2017deep}, the U-net MR output image, is used for estimate the missing k-space samples.
-The fully k-space is then recovered by integrating the sampled k-space according to the sampling mask.
-Also for dynamic MRI reconstruction, a deep CNN has been successfully applied in~\cite{sandinodeep} and provides better results over the time-consuming CS method.
+Deep neural networks (DNN) allow to implicitly learn prior information from large datasets.
+This has been exploited in recent works for MRI reconstruction from sub-sampled data.
+A convolutional neural network (CNN) was introduced in~\cite{wang2016accelerating} to learn the mapping between zero-filled and fully-sampled MRI.
+In~\cite{Oktay2016}, MRI acceleration by super-resolution (SR) concepts was introduced.
+One of the key ideas is a siamese CNN structure that allows to receive multiple inputs acquired from different viewing planes.
+Improved low-resolution (LR) high-resolution (HR) mapping was obtained by residual architecture.
+A multi-scale residual network, also known as U-net~\cite{ronneberger2015u}, was used in~\cite{lee2017deep} to address the CS optimization, formulated as a residual regression problem.
+Hayun at el.~\cite{hyun2017deep}, applied U-net to perform anti-aliasing of MRI generated from sub-sampled k-space.
+The U-net output image is than enhanced by integrating its k-space domain with the originally acquired raw samples.
+U-net CNN has been also used in~\cite{sandinodeep} for dynamic MRI reconstruction.
+The spatio-temporal characteristics of sequential MRI data was recently exploited using recurrent neural network (RNN) by~\cite{qin2017convolutional}
+Another interesting approach, based on recurrent neural network (RNN) for temporal MRI reconstruction has been recently suggested by~\cite{qin2017convolutional}.
 All these works address the reconstruction problem in the image domain rather than the k-space domain.
 
-The proposed framework utilizes recent advances in deep learning, while similarly to the CS methods addresses MRI reconstruction directly from the k-space.
+The proposed framework utilizes recent advances in deep learning, while addressing MRI reconstruction directly from the k-space.
 Specifically, we use generative adversarial networks (GAN) \cite{goodfellow2014generative,radford2015unsupervised,pathak2016context}.
@@
 This powerful combination has been used for MRI acceleration in~\cite{yu2017deep,mardani2017deep}, and also for generating Computed Tomography (CT)-like images from MRIs~\cite{nie2016medical}.
-Here, the generator is used for reconstruction of the entire k-space grid from under-sampled data.
-Its loss is a combination of an adversarial loss, based on the discriminator output and a fidelity loss with respect to the fully sampled MRI.
+In contrast, here, the generator is used for reconstruction of the entire k-space grid from under-sampled data.
+Its loss is a combination of an adversarial loss, calculated on the image domain, based on the discriminator output, and a fidelity loss with respect to the fully sampled k-space.
+Unlike~\cite{hyun2017deep}, the entire process, including the IFFT, is carried out and optimized in an end-to-end manner by the proposed GAN architecture.
+As the MRI data is complex, both real and imaginary components are incorporated in both the generator and the discriminator.
 

### 2018-01-27 paper.tex
Small fixes

@@
 In~\cite{caballero2014dictionary}, this concept was extended using spatio-temporal patches for dynamic MRI reconstruction.
-Compressed manifold learning based on Laplacian eigenmaps, has been applied to partially in~\cite{usman2014compressive} for respiratory motion estimation and in~\cite{bhatia2015fast} for cardiac MRI reconstruction.
+Compressed manifold learning based on Laplacian eigenmaps, has been applied in~\cite{usman2014compressive} for respiratory motion estimation and in~\cite{bhatia2015fast} for cardiac MRI reconstruction.
 
@@
 U-net CNN has been also used in~\cite{sandinodeep} for dynamic MRI reconstruction.
-The spatio-temporal characteristics of sequential MRI data was recently exploited using recurrent neural network (RNN) by~\cite{qin2017convolutional}
-Another interesting approach, based on recurrent neural network (RNN) for temporal MRI reconstruction has been recently suggested by~\cite{qin2017convolutional}.
+The spatio-temporal characteristics of sequential MRI data was recently exploited using recurrent neural network (RNN) by~\cite{qin2017convolutional}.
 All these works address the reconstruction problem in the image domain rather than the k-space domain.
@@
 While sampling part of the k-space, using $M_{p}$ as a sampling mask, the reconstructed MR image suffers from artifacts and aliasing.
-An example artifacts caused by under-sampling in the phase axis using Gaussian mask (40\%) is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
+An example artifacts caused by under-sampling and zero padding in the phase axis using Gaussian mask (40\%) is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
 
@@
 The discriminator's input is the reconstructed MR image,\textbf{ }i.e.,\textbf{ }after IFFT.
-By that, we are integrating the reconstruction phase in our optimization.
-In this work, we use the Wasserstein distance as the GAN loss function~\cite{arjovsky2017wasserstein} which helps us to improve the training stability and provides better reconstruction than the classic GAN.
+By that, we are integrating the reconstruction phase and optimize it in an end-to-end manner.
+In this work, we use the Wasserstein distance as the GAN loss function~\cite{arjovsky2017wasserstein}, which helps us to improve the training stability and provides better reconstruction compared to the classic GAN used in~\cite{shitrit2017accelerated}.
 
@@
 2D FFT is applied to the fully-sampled MR images. 
-Further to our work~\cite{shitrit2017accelerated}, which was focused on Cartesian 2D sampling mask along the phase axis, we sample the k-space using $2D$ Gaussian mask, and achieve higher sampling factors of 2.5, 4 and 6 (Figure~\ref{fig:sampling_masks}).
+Further to our work~\cite{shitrit2017accelerated}, which was been focused on 1D Cartesian sampling mask along the phase axis, in this work, we sample the k-space using $2D$ random Gaussian mask.
+By that, we exploit the sparsity in both phase and frequency dimensions and achieve higher sampling factors of 2.5, 4 and 6 (Figure~\ref{fig:sampling_masks}).
 Data augmentation is created by random offsets of the proposed mask and image flipping. This leads us to reconstruction of the MR image from 40\%, 25\% and 16.6\% of the original k-space data.
@@
 \subsection{PSNR and SSIM}
-PSNR and SSIM are the most commonly used measures for evaluate image reconstruction quality.
+PSNR and SSIM are the most commonly used measures for evaluation of image reconstruction quality.
 PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image.
-Therefore, this measure is not a sufficient metric for edges and general objects shape.
-For example, a model can provides a good reconstruction in the sense of PSNR but with blurry edges and loss of anatomical fine details.
-This leads to a poor segmentation, which used for medical diagnostic.
+Therefore, this measure is not a sufficient metric for fine details and general objects shape.
+For example, a model can provides a good reconstruction in the sense of PSNR but with blurry edges and loss of anatomical fine details, results in a poor segmentation, which used for medical diagnostic.
 However, PSNR is still a good indication for the image quality, especially if an expert should view it.
@@
 We examine the different reconstruction methods by applying the Brain Extraction Tool (BET) \cite{smith2002fast} on each different MR reconstructed image.
-Then, we compared the skull stripping results to the fully-sampled result using the Modified Hausdorff Distance (MHD)~\cite{dubuisson1994modified}.
+Then, we compared the skull stripping to the fully-sampled results using the Modified Hausdorff Distance (MHD)~\cite{dubuisson1994modified}.
 
-Let $C_1,C_2\in R^2$ denotes the brain contours extract from skull stripping algorithm on two different reconstruction methods respectively (in our case the fully-sampled and the tested reconstruction method).
+Let $C_1,C_2\in R^2$ denotes the brain contours, extract from skull stripping algorithm, for a two different reconstruction methods respectively (in our case the fully-sampled and the tested reconstruction method).
 MHD measures the distance between the contours such that:
@@
 This process is of a great importance for brain MR image analysis, especially for therapy planning and also for clinical research.
-Sampling artifacts, results in poor signal to noise and blurry edges, and also loss of anatomical fine details, will probably leads to bad segmentation performance.
-We suggest a way to evaluate and compare different MRI reconstruction methods based on segmentation results.
-We create a reference segmentation by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and run a brain segmentation algorithm (FAST \cite{zhang2001segmentation}).
-Then, we did the same process for all the reconstruction methods and compared the segmentation results to the reference.
+Sampling artifacts, results in poor signal to noise ratio, blurry edges and loss of anatomical fine details, leads to bad segmentation performance.
+Segmentation compatibility demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
+We create a reference segmentation by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and perform a brain segmentation algorithm (FAST \cite{zhang2001segmentation}) on it.
+Then, we did the same process for all the reconstruction methods and compared the segmentation results.
 
@@
 Dice score is a measure of sets similarity which gets the values between 0 (no similarity) to 1.0 (max similarity).
-Denotes by $S_{i,j}$ the set of pixels in segment $j$ for reconstruction method $i$, the Dice score between this method to the reference is:
+Denotes by $S_{i,j}$ the set of pixels in segment $j$ for reconstruction method $i$, the Dice score is:
 \begin{equation}
@@
 \end{equation}
-Dice values for different sampling ratios are presented in~Table~\ref{tbl:DICE}. Our methods achieved the best Dice scores for all brain tissues.
+Dice values for different sampling factors are presented in~Table~\ref{tbl:DICE}. Our methods achieved the best Dice scores for all brain tissues.
 
@@
 We proposed a practical, software-only framework, based on deep learning, for accelerating MRI acquisition, while maintaining anatomically meaningful imaging.
-This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples (based on the real k-space distribution).
+This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples from the real k-space distribution.
 Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from large publicly available dataset, where only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
 
-Our method produce more clinically acceptable reconstructions compared with the methods being tested in the terms of PSNR and SSIM.
+Our method produce clinically acceptable reconstructions.
+Compared to the methods being tested, our method achieves the best PSNR and SSIM.
 We also perform tissue segmentations and measure the performance using the Dice scores, with respect to those obtained by using the original fully-sampled images.
 Better Dice score for white matter, gray matter, and CSF were achieved for all sampling factors.
-Moreover, lower Hausdorff distances indicates the quality of the proposed method in terms of general brain shape.
-Comparing to CS, our reconstruction method preserve the brain shape better, as seen in Figures~\ref{fig:example_factor_6},~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}.
+Moreover, lower Hausdorff distance indicates the quality of the proposed method in terms of general brain shape, especially comparing to CS, as seen in Figures~\ref{fig:example_factor_6},~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}.
 

### 2018-02-01 paper.tex
Tammy update - 01/02/2018

@@
 
-We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
-In addition, we optimize two networks: 1.
+We compare the proposed method reconstructions to those obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
+In addition, for comparison, we test two other networks: 1.
 CNN-L2 - a k-space generator (with same architecture as the proposed method) trained with only L2 loss.
 2.
-IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding.
+IM-CNN-L2 - a network which performs on the image-space and is optimized to remove the artifacts caused by under-sampling and zero padding.
+The method is applied to the Information eXtraction from Images (IXI) dataset, which is a large publicly available dataset, including 3T and 1.5T scans.
+Raw data is down-sampled such that only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
 To assess the clinical usability of the reconstructed images we perform an extended validation, composed of anatomy and quantitative measurements.
-In addition to the common used PSNR and Structure Similarity Index (SSIM) we perform tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
+In addition to the common used PSNR and Structure Similarity Index (SSIM) we perform tissue segmentation and compare the results to those obtained by using the original fully-sampled images.
 Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
-The proposed method outperforms the other in 3T and 1.5T brain MRI reconstruction, using a large publicly available dataset, where only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
-Moreover, compared to the widely used CS-MRI, the proposed method is faster in a two orders of magnitude.
-This makes it possible to use it in a real time manner.
+The proposed method outperforms all other tested methods in all evaluation metrics.
+Moreover, compared to the widely used CS-MRI, the proposed method is faster in two orders of magnitude.
+In fact, it can work in real time, and is therefore practical for routine uses.
 
-The paper is organized as follows.
-Section \ref{method_section} presents some theoretical foundation and our method.
-Section \ref{experiments_section} describes the experimental results.
-Conclusions and future directions are describes in section \ref{conclusions_section}.
+The rest of the paper is organized as follows.
+Section~\ref{method_section} provides a brief background on MRI acquisition and introduce the network architecture as well the training methodology.
+Section~\ref{experiments_section} presents the experimental results.
+Conclusions and future directions are given in section~\ref{conclusions_section}.
 
@@
 While sampling part of the k-space, using $M_{p}$ as a sampling mask, the reconstructed MR image suffers from artifacts and aliasing.
-An example artifacts caused by under-sampling and zero padding in the phase axis using Gaussian mask (40\%) is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
+An example artifacts caused by under-sampling and zero padding in the phase axis using a Gaussian mask (40\%) is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
 
@@
 
-The training data consists of 500 $3D$ brain MRI (T1) scans of different patients from the IXI dataset\footnote{\url{http://brain-development.org/ixi-dataset/}}.
-The data has been acquired by three MR machines, Philips 1.5T, 3T and GE 1.5T.
-All images padded to resolution of $256\times256$ pixels.
-From each $3D$ volume we extract 93 $2D$ saggital slices. We used $37.2k$ $(80\%)$ 2D slices for training and $9.2k$ $(20\%)$ for testing (100 $3D$ volumes).
+The training data consists of 500 $3D$ brain MRI (T1-weighed) scans of different patients from the IXI dataset\footnote{\url{http://brain-development.org/ixi-dataset/}}.
+The data has been acquired by three MR machines, Philips 1.5T, 3T and GE 1.5T using different imaging protocols.
+From each $3D$ volume we extract 93 $2D$ saggital slices.
+All slices were interpolated to $256\times256$ pixels.
+We used $37.2k$ $(80\%)$ 2D slices for training and $9.3k$ $(20\%)$ for testing (100 $3D$ volumes).
 In order to create k-space images for training, inverse orthonormal
 2D FFT is applied to the fully-sampled MR images. 
-Further to our work~\cite{shitrit2017accelerated}, which was been focused on 1D Cartesian sampling mask along the phase axis, in this work, we sample the k-space using $2D$ random Gaussian mask.
-By that, we exploit the sparsity in both phase and frequency dimensions and achieve higher sampling factors of 2.5, 4 and 6 (Figure~\ref{fig:sampling_masks}).
-Data augmentation is created by random offsets of the proposed mask and image flipping. This leads us to reconstruction of the MR image from 40\%, 25\% and 16.6\% of the original k-space data.
+Different from our preliminary work~\cite{shitrit2017accelerated}, which employed 1D Cartesian sampling mask along the phase axis, here, we perform k-space sampling using $2D$ random Gaussian mask.
+By this, we exploit the sparsity in both phase and frequency dimensions and therefore able to accommodate higher sampling factors (Figure~\ref{fig:sampling_masks}).
+MRI reconstruction is performed using 40\%, 25\% and 16.6\% of the original k-space data.
+%Data augmentation is created by random offsets of raw images (prior to the IFFT) and k-space flipping.
+This leads us to reconstruction of the MR image from 40\%, 25\% and 16.6\% of the original k-space data.
 
-The generator is composed of $5$ blocks of CONV-BatchNorm-ReLU, with output channels $16,32,64,32,8,$ respectively.
-The last layer is CONV with two outputs channels (for real and imaginary parts).
+The generator is composed of $5$ blocks of CONV-BatchNorm-ReLU, with output channels $16,32,64,32,8,$ respectively (see Figure~\ref{fig:architectures}).
+The last CONV layer is composed of two output channels for real and imaginary components.
 The discriminator is composed of $4$ blocks of CONV-Pool-BatchNorm-LReLU with output channels $8,16,32,16$ and one fully-connected layer.
-All CONV layers kernel size is $3\times3$.
+All CONV layer's kernel size is $3\times3$.
 All weights was initialized by Xavier \cite{glorot2010understanding}.
-We used RMSprop solver with fixed learning rate of $5\mathrm{e}{-6}$ and set $k_{d}$ to 1.
+We used RMSprop~\cite{tieleman2012lecture} solver with fixed learning rate of $5\mathrm{e}{-6}$ and set $k_{d}$ to 1.
 
-We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
-In addition, we optimized two networks: 1.
-CNN-L2 - a k-space generator (with same architecture as the proposed method) trained with only L2 loss.
-2.
-IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding.
-%We used the U-net \cite{ronneberger2015u} architecture inspired by \cite{lee2017deep}. 
-We used the U-net \cite{ronneberger2015u} architecture and the same reconstruction method as presented in~\cite{hyun2017deep}.
-Specifically, we apply an FFT on the U-net output image to get an estimated k-space.
-The fully k-space is then recovered by integrating the sampled k-space according to the sampling mask.
-The same sampling masks was used for all methods.
+We compared the proposed method reconstructions to those obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
+In addition, we tested two other networks.
+To asses the use of adversarial loss, we trained a k-space generator, with same architecture as the proposed method, with only L2 loss (CNN-L2).
+We also implemented the method proposed in~\cite{hyun2017deep} and constructed a network IM-CNN-L2 which is applied directly to the image space rather than k-space.
+Specifically, we used the U-net architecture~\cite{ronneberger2015u} and applied an FFT on each of its output images to get an estimated k-space.
+The complete k-space is then recovered by integrating estimated samples with the sampled raw data according to the sampling mask.
+The same sampling masks were used for all methods.
 

### 2018-02-05 paper.tex
Tammy update 05/02/2018

@@
 Raw data is down-sampled such that only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
-To assess the clinical usability of the reconstructed images we perform an extended validation, composed of anatomy and quantitative measurements.
+To assess the clinical usability of the reconstructed images we perform an extended validation, composed of anatomical quantitative measurements.
 In addition to the common used PSNR and Structure Similarity Index (SSIM) we perform tissue segmentation and compare the results to those obtained by using the original fully-sampled images.
@@
 
-We compared the proposed method reconstructions to those obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
+We compared the proposed method reconstructions to those obtained by using a conventional compressed sensing method-CS-MRI \cite{lustig2007sparse} and Zero-filling.
 In addition, we tested two other networks.
-To asses the use of adversarial loss, we trained a k-space generator, with same architecture as the proposed method, with only L2 loss (CNN-L2).
-We also implemented the method proposed in~\cite{hyun2017deep} and constructed a network IM-CNN-L2 which is applied directly to the image space rather than k-space.
-Specifically, we used the U-net architecture~\cite{ronneberger2015u} and applied an FFT on each of its output images to get an estimated k-space.
-The complete k-space is then recovered by integrating estimated samples with the sampled raw data according to the sampling mask.
+To asses the use of adversarial loss, we trained a k-space generator, with the same architecture as the proposed method, with only L2 loss (CNN-L2).
+We also implemented the method proposed in~\cite{hyun2017deep} and constructed a network IM-CNN-L2, which is applied directly to the image space rather than the k-space.
+Specifically, as in~\cite{hyun2017deep}, we used the U-net architecture~\cite{ronneberger2015u} and applied an FFT on each of its output images to get an estimated k-space.
+The complete k-space is then recovered by integrating the estimated samples with the sampled raw data according to the sampling mask.
 The same sampling masks were used for all methods.
 
-To assess the clinical usability of the reconstructed images we perform an extended validation, composed of anatomy and quantitative measurements.
+To demonstrate the clinical usability of the reconstructed images we perform an extended validation, composed of anatomical quantitative measurements.
 In addition to the common used PSNR and Structure Similarity Index (SSIM)~\cite{wang2004image} metrics, we perform tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
@@
 PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image.
-Therefore, this measure is not a sufficient metric for fine details and general objects shape.
-For example, a model can provides a good reconstruction in the sense of PSNR but with blurry edges and loss of anatomical fine details, results in a poor segmentation, which used for medical diagnostic.
-However, PSNR is still a good indication for the image quality, especially if an expert should view it.
 Quantitative evaluation is presented in~Table~\ref{tbl:PSNR_NO_MASK} and a graphical visualization in ~Figure~\ref{fig:error_psnr_errorbar}.
-The PSNR calculated on the whole image without masking.
-Note that the proposed method outperforms the other.
+The PSNR is calculated for the entire image without masking.
+Note that the proposed method outperforms the others.
+To support it, we also calculated the Two-sample t-Test for the table's scores.
+The differences are statistically significant (p-values~$<0.005$) for all pairwise comparisons between the results of our method and the others.
 
@@
 		\hline 
-		\textbf{PSNR} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6}} \tabularnewline
+		\textbf{PSNR} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5 (40\%)}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4 (25\%)}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6 (16.66\%)}} \tabularnewline
 		\textbf{Method} & \multicolumn{1}{c||}{} & \multicolumn{1}{c||}{} & \multicolumn{1}{c|}{} \tabularnewline \cline{1-4}
@@
 
-An additional validation of our model done by calculating the PSNR measure on different brain tissues.
-We applied an image segmentation algorithm, FAST~\cite{zhang2001segmentation}, on the original fully-sampled MR image and then use it for calculating the masked-PSNR on gray matters, white matters and the Cerebrospinal Fluid (CSF).
+An additional validation of our model is performed by calculating the PSNR measure on different brain tissues.
+We applied the commonly used FAST~\cite{zhang2001segmentation} image segmentation algorithm, on the original fully-sampled MR image and then used it for calculating the masked-PSNR on gray matter (GM), white matter (WM) and the Cerebrospinal Fluid (CSF).
 Results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}.
@@
 			\hline 
-			\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
+			\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5 (40\%)} & \multicolumn{3}{c||}{Factor 4 (25\%)} & \multicolumn{3}{c|}{Factor 6 (16.66\%)}\tabularnewline
 			\cline{2-10} 
@@
 
-SSIM is used for measuring the similarity between the original and the reconstructed images.
-It quantifies the degradation caused by sampling artifacts based on visible structures in the image. SSIM values for different sampling factors are presented in~Table~\ref{tbl:SSIM_NO_MASK}.
+We next used SSIM, which is a full reference metric, and is considered as a perception-based model, to measure the similarity between the original fully-sampled images and the reconstructed ones.
+It quantifies the degradation caused by sampling artifacts based on pixels' inter-dependencies in the image.
+SSIM scores for different sampling factors, for all methods compared, are presented in~Table~\ref{tbl:SSIM_NO_MASK}.
+The advantage of our method is clearly shown.
+All pairwise comparisons between the results obtained by our method and the others are statistically significant (p-values~$<0.0001$) for all sampling factors.
 
@@
 		\hline 
-		\textbf{SSIM} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6}} \tabularnewline
+		\textbf{SSIM} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5 (40\%)}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4 (25\%)}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6 (16.66\%)}} \tabularnewline
 		\textbf{Method} & \multicolumn{1}{c||}{} & \multicolumn{1}{c||}{} & \multicolumn{1}{c|}{} \tabularnewline \cline{1-4}
@@
 
+While PSNR and SSIM are widely used, these measures are not sensitive enough to differences in fine details and complex anatomical structure topologies.
+For example, a model can provide a good reconstruction in the sense of PSNR, yet with blurry edges and therefore loss of high frequency information.
+This may significantly affect diagnostic usability.
+We therefore further compared segmentation quality between the fully-sampled and the reconstruction images.
+Results of the analysis obtained for our method and all others are presented next.
+
 \subsection{Brain Extraction - Skull Stripping}
-Brain extraction (Skull stripping) is a an algorithm that delineates the brain boundary (Figure~ \ref{fig:brain_extraction}).
-It is necessary for almost every brain analysis algorithm.
+Brain extraction (skull stripping) is an algorithm that delineates the brain boundary (Figure~ \ref{fig:brain_extraction}).
+It is necessary perliminary step for almost every brain analysis algorithm.
 In tissue segmentation for example, skull stripping is a pre-processing step which affects directly on the segments partition.
@@
 		\hline 
-		\textbf{MHD} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6}} \tabularnewline
+		\textbf{MHD} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 2.5 (40\%)}} & \multicolumn{1}{c||}{\multirow{2}{*}{Factor 4 (25\%)}} & \multicolumn{1}{c|}{\multirow{2}{*}{Factor 6 (16.66\%)}} \tabularnewline
 		\textbf{Method} & \multicolumn{1}{c||}{} & \multicolumn{1}{c||}{} & \multicolumn{1}{c|}{} \tabularnewline \cline{1-4}
@@
 			\hline 
-			\textbf{DICE} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
+			\textbf{DICE} & \multicolumn{3}{c||}{Factor 2.5 (40\%)} & \multicolumn{3}{c||}{Factor 4 (25\%)} & \multicolumn{3}{c|}{Factor 6 (16.66\%)}\tabularnewline
 			\cline{2-10} 
@@
 
-Our method produce clinically acceptable reconstructions.
-Compared to the methods being tested, our method achieves the best PSNR and SSIM.
-We also perform tissue segmentations and measure the performance using the Dice scores, with respect to those obtained by using the original fully-sampled images.
-Better Dice score for white matter, gray matter, and CSF were achieved for all sampling factors.
+The proposed method outperforms all other tested methods in the common used PSNR and SSIM measures and produce clinically acceptable reconstructions.
+We also perform tissue segmentation and measure the performance using the Dice scores, with respect to those obtained by using the original fully-sampled images.
+Higher Dice score for white matter, gray matter, and CSF were achieved for all sampling factors.
 Moreover, lower Hausdorff distance indicates the quality of the proposed method in terms of general brain shape, especially comparing to CS, as seen in Figures~\ref{fig:example_factor_6},~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}.
@@
 Once the network is optimized, the reconstruction for a single test image is done in less than 10 msec, almost two orders of magnitude faster than the widely used CS.
-This fact makes it possible to use it in a real time manner.
+In fact, it can work in real time, and is therefore practical for routine uses.
 Future work will concentrate on generation of MRI in the presence of pathologies.
@@
 K-SPACE VS IMAGE SPACE ??
+
+Our method outperforms the other methods, and the advatnage of our methods becoms more apparant for higher acceleration factors (lower sampling ratios).
+
+Therefore, this measure is not a sufficient metric for fine details and general objects shape.
+For example, a model can provide a good reconstruction in the sense of PSNR yet with blurry edges and loss of anatomical fine details.
+This may significant affect diagnostic usability.
 }

### 2018-02-05 paper.tex
Tammy update Feb05

@@
 \subsection{Brain Extraction - Skull Stripping}
-Brain extraction (skull stripping) is an algorithm that delineates the brain boundary (Figure~ \ref{fig:brain_extraction}).
-It is necessary perliminary step for almost every brain analysis algorithm.
-In tissue segmentation for example, skull stripping is a pre-processing step which affects directly on the segments partition.
-We examine the different reconstruction methods by applying the Brain Extraction Tool (BET) \cite{smith2002fast} on each different MR reconstructed image.
-Then, we compared the skull stripping to the fully-sampled results using the Modified Hausdorff Distance (MHD)~\cite{dubuisson1994modified}.
+Brain extraction (skull stripping) is an algorithm that delineates the brain boundary (Figure~ \ref{fig:brain_extraction}). It is a necessary preliminary step for brain analysis algorithms.
+We examine the different reconstruction methods by applying the Brain Extraction Tool (BET) \cite{smith2002fast} to both MR reconstructed and original (fully-sampled) images.
+Compatibility of the skull stripping results between the original and the generated datasets is measured via the Modified Hausdorff Distance (MHD)~\cite{dubuisson1994modified}, defined as follows.
 
-Let $C_1,C_2\in R^2$ denotes the brain contours, extract from skull stripping algorithm, for a two different reconstruction methods respectively (in our case the fully-sampled and the tested reconstruction method).
-MHD measures the distance between the contours such that:
+Let $C_1,C_2\in R^2$ denote the brain boundaries extracted by the BET algorithm, using the original and the reconstructed scans respectively. The MHD between $C_1$ and $C_2$ is:
 
@@
 \begin{array}{cc}
-MHD(C_1,C_2) = \max \left\{\frac{1}{|C_1|} \sum_{\sigma_{1}\in C_1}^{}d(\sigma_1,C_2), ~ \frac{1}{|C_2|} \sum_{\sigma_{2}\in C_2}^{}d(\sigma_2,C_1)\right\} \\
+MHD(C_1,C_2) = 0.5 \left[{\frac{1}{|C_1|} \sum_{\sigma_{1}\in C_1}^{}d(\sigma_1,C_2) + \frac{1}{|C_2|} \sum_{\sigma_{2}\in C_2}^{}d(\sigma_2,C_1)}\right] \\
 d(\sigma_1,C_2) = \underset{\sigma_{2}\in C_{2}}{\min}||\sigma_1-\sigma_2|| \\
@@
 \end{equation}
-where $\sigma_1,\sigma_2$ are points on the contours $C_1,C_2$ respectively (Figure~\ref{fig:brain_extraction}.c). MHD values for different sampling ratios are presented in~Table~\ref{tbl:MHD}.
+where $\sigma_1,\sigma_2$ are points on the contours $C_1,C_2$ respectively (Figure~\ref{fig:brain_extraction}.c) and $|C_i|,~i=1,2$ are the respective cardinalities.
+MHD values for all tested methods and sampling ratios are presented in~Table~\ref{tbl:MHD}.
+The MHD results obtained by our methods are better than all others and are significant (p-values~$<0.0001$) for CS-MRI and Zero-filled.
 
@@
 \subsection{Brain Segmentation}
-Brain segmentation is the task of partitioning the brain image (MRI in our case), into the following segments: background, white matter, gray matter and CSF.
-This process is of a great importance for brain MR image analysis, especially for therapy planning and also for clinical research.
-Sampling artifacts, results in poor signal to noise ratio, blurry edges and loss of anatomical fine details, leads to bad segmentation performance.
-Segmentation compatibility demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
+We next tested and compared segmentation quality applying brain tissue partitioning algorithm (FAST \cite{zhang2001segmentation}) to the reconstructed images.
+Segmentation results were compared to those obtained for the original fully-sampled scans.
+We believe that these comparisons are indicative to the diagnostic quality of the reconstructed MRIs as tissue segmentation (WM, GM and CSF) plays a key role in clinical brain analysis.
+%Segmentation compatibility demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
 We create a reference segmentation by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and perform a brain segmentation algorithm (FAST \cite{zhang2001segmentation}) on it.
 Then, we did the same process for all the reconstruction methods and compared the segmentation results.
-
-The measure used for segmentations comparison is the Dice score \cite{dice1945measures} between the original and the reconstructed image segments.
-Dice score is a measure of sets similarity which gets the values between 0 (no similarity) to 1.0 (max similarity).
-Denotes by $S_{i,j}$ the set of pixels in segment $j$ for reconstruction method $i$, the Dice score is:
+We used the Dice score~\cite{dice1945measures} to measure the compatibility between the segments obtained for the original ($S_{\mbox{\tiny{REF}}}$) and the reconstructed ($S_{\mbox{\tiny{REC}}}$) images, defined as follows:
 \begin{equation}
 \begin{array}{c}
-DICE(S_{ref,j},S_{i,j}) = \frac{2\cdot|S_{ref,j} \cap S_{i,j}|} {|S_{ref,j}| + |S_{i,j}|}
+DICE(S_{\mbox{\tiny{REF}}}, S_{\mbox{\tiny{REC}}}) = 2\frac{S_{\mbox{\tiny{REF}}} \cap S_{\mbox{\tiny{REC}}}}{S_{\mbox{\tiny{REF}}} + S_{\mbox{\tiny{REC}}}}
 \end{array}
 \end{equation}
-Dice values for different sampling factors are presented in~Table~\ref{tbl:DICE}. Our methods achieved the best Dice scores for all brain tissues.
+Dice scores are between zero to one where one indicates complete overlap between the tested segments.
+Therefore, higher dice scores imply higher compatibility between reconstructed and original images.
+Dice scores for all tested methods and sampling factors are presented in~Table~\ref{tbl:DICE}.
+As fore previous tests, our method achieves the best scores for all brain tissues and all sampling factors.
+{\color{red} Statistical significant values (~~) found for [1,2,3,4].}
 
@@
 \end{table}
-
-Visual comparison for sampling factor 6 is shown in Figure~\ref{fig:example_factor_6}.
-The first and the second rows are the reconstructed images with zoom in of red ROI.
-The third row is the extracted brain and the last row is the calculated segmentation.
-Each column represents different reconstruction method.
-MRIs reconstructed by using the suggested adversarial method have stronger contrast and no significant aliasing or artifacts.
-In addition the brain extraction and the segmentation are more accurate.
-Additional examples for factor 4 and 2.5 can be found in Figures~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}.
+MR reconstruction results for factor 6~(16.66\%) as well as their respective brain segmentation results are visually presented in Figure~\ref{fig:example_factor_6}~for a single representative scan.
+The left most column corresponds to the original image and columns 2-5 correspond to the reconstructed images using Zero-filled, CS-MRI, IM-CNN-L2 and the proposed method, respectively.
+The first row presents a $2D$ slice of the original and the reconstructed MRIs.
+The second row presents the zoom-in of brain regions in the red frames shown in the first row.
+The third row presents the corresponding brain extraction.
+The forth row presents the automatic tissue segmentation where, dark blue is used for WM, blue for GM and light blue for CSF.
+Note that, MRIs reconstructed by using the suggested adversarial method have stronger contrast and no significant aliasing or artifacts.
+In addition the brain extraction and tissue segmentation results are more compatible with those obtained from the original fully-sampled MRIs.
+Additional examples of different cases, using sampling factors of 4~(25\%) and 2.5~(40\%) are shown in Figures~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}, respectively.
 
@@
 \section{Discussion}\label{conclusions_section}
+The proposed deep learning framework for MRI reconstruction from highly under-sampled k-space (up to 16.66\%), can be used as the foundation of a real-time, software-only solution for MRI acceleration.
+Combining both adversarial and fidelity loss in the DNN training, the method suggested provides high PSNR reconstructions for large and diverse brain MRI dataset acquired by different MRI machines (1.5T and 3.T) and different imaging protocols.
 
-We proposed a practical, software-only framework, based on deep learning, for accelerating MRI acquisition, while maintaining anatomically meaningful imaging.
-This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples from the real k-space distribution.
-Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from large publicly available dataset, where only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
+Clinical usability of the reconstructed data plays a key role in the quality analysis performed as part of this research.
+We choose to test it by using standard tissue segmentation measures (such as Dice and MHD), as we believe that compatibility of the extracted brain regions with those obtained by using the original fully-sampled MRIs indicate fine detail reconstructions which have apparent diagnostic significance.
 
+Until recently, CS techniques were considered the state-of-the-art for MRI reconstruction.
 The proposed method outperforms all other tested methods in the common used PSNR and SSIM measures and produce clinically acceptable reconstructions.

### 2018-02-05 paper.tex
Tammy update - conclusion

@@
 The proposed deep learning framework for MRI reconstruction from highly under-sampled k-space (up to 16.66\%), can be used as the foundation of a real-time, software-only solution for MRI acceleration.
-Combining both adversarial and fidelity loss in the DNN training, the method suggested provides high PSNR reconstructions for large and diverse brain MRI dataset acquired by different MRI machines (1.5T and 3.T) and different imaging protocols.
+The inter-play between the generator and the discriminator plays a key role here.
+The generator is trained directly on the k-space, thus avoiding aliasing correction (due to under-sampling) as done in other methods.
+Instead, the k-space distribution, and not its IFFT, is learned and generated.
+Moreover, combining both adversarial and fidelity loss in the DNN training, the method suggested provides high PSNR reconstructions for large and diverse brain MRI dataset acquired by different MRI machines (1.5T and 3.T) and different imaging protocols.
 
-Clinical usability of the reconstructed data plays a key role in the quality analysis performed as part of this research.
-We choose to test it by using standard tissue segmentation measures (such as Dice and MHD), as we believe that compatibility of the extracted brain regions with those obtained by using the original fully-sampled MRIs indicate fine detail reconstructions which have apparent diagnostic significance.
+Until just a few years ago, CS techniques were considered the state-of-the-art for MRI reconstruction.
+Recently, deep learning methods, capable of learning imaging samples distribution from training datasets, were shown to obtain reconstruction with comparable or even higher quality.
+The strength of the proposed DNN is three-fold, combining direct k-space reconstruction, GAN architecture and end-to-end optimization.
+This allows anatomically meaningful reconstruction with high fidelity to the original scan.
+Extensive comparative analysis shows that our method outperforms all other tested MRI reconstruction methods (CS and other DNN-based) for various quality metrics, showing more robustness for high acceleration factors.
 
-Until recently, CS techniques were considered the state-of-the-art for MRI reconstruction.
-The proposed method outperforms all other tested methods in the common used PSNR and SSIM measures and produce clinically acceptable reconstructions.
-We also perform tissue segmentation and measure the performance using the Dice scores, with respect to those obtained by using the original fully-sampled images.
-Higher Dice score for white matter, gray matter, and CSF were achieved for all sampling factors.
-Moreover, lower Hausdorff distance indicates the quality of the proposed method in terms of general brain shape, especially comparing to CS, as seen in Figures~\ref{fig:example_factor_6},~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}.
+A key advantage of the proposed method is its short runtime at test phase (less than 10 msec per slice), which is almost two orders of magnitude faster than CS.
+This makes it applicable for routine uses.
+As training can be performed off-line, prior to the acquisition sessions, the fact that it lasts a few days has no practical relevance.
 
-Additional advantage of the proposed method is the runtime.
-A few days are required for training the generator.
-Once the network is optimized, the reconstruction for a single test image is done in less than 10 msec, almost two orders of magnitude faster than the widely used CS.
-In fact, it can work in real time, and is therefore practical for routine uses.
-Future work will concentrate on generation of MRI in the presence of pathologies.
+Assessing clinical usability of the reconstructed data takes a considerable part in the quality analysis performed as part of this research.
+We choose to test it by using standard tissue segmentation measures (such as Dice and MHD), as we argue that compatibility of the extracted brain regions with those obtained by using the original fully-sampled MRIs indicate fine detail reconstructions which have apparent diagnostic significance.
 
-{\color{red}
-Do we need to discuss about :
-K-SPACE VS IMAGE SPACE ??
+Nevertheless, pathological cases were not considered in this study and to the best of our knowledge are seldom addressed.
+We believe that high quality reconstruction in the presence of brain atrophies is the true success criteria.
+In fact, addressing this challenge and measuring performances in this sense, should be the gold standard in future benchmarks.
 
-Our method outperforms the other methods, and the advatnage of our methods becoms more apparant for higher acceleration factors (lower sampling ratios).
-
-Therefore, this measure is not a sufficient metric for fine details and general objects shape.
+%Therefore, this measure is not a sufficient metric for fine details and general objects shape.
 For example, a model can provide a good reconstruction in the sense of PSNR yet with blurry edges and loss of anatomical fine details.
 This may significant affect diagnostic usability.
-}
 

### 2018-02-05 paper.tex
update

@@
 \section{Method}\label{method_section}
-
-\subsection{K-space}
-Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained by the IFFT of the complex k-space signal $s_{0}$. Let $M_{F}$ denote a full sampling mask such that the reconstructed MR image is: 
+We aim to address MRI reconstruction from under-sampled k-space data using DNN. We hereby present the proposed methodology as well as the network architecture.
+\subsection{Notations and Problem Definition}
+Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained by IFFT of the complex k-space signal $s_{0}$ i.e, 
 \begin{equation}
-\bm{u}=F^{H}M_{F}\odot s_{0}
+\bm{u}=F^{H}s_{0}
 \end{equation} 
-where $H$ is the Hermitian transpose operation, $\odot$ denotes element-wise multiplication, and $F^{H}$ is an orthonormal 2D IFFT operator, such that $F^{H}F=I$. 
-While sampling part of the k-space, using $M_{p}$ as a sampling mask, the reconstructed MR image suffers from artifacts and aliasing.
-An example artifacts caused by under-sampling and zero padding in the phase axis using a Gaussian mask (40\%) is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.
+where $H$ is the Hermitian transpose operation and $F^{H}$ is an orthonormal 2D IFFT operator, such that $F^{H}F=I$. 
+Partial k-space sampling, results in MR images that are subject to artifacts and aliasing. 
+Figure~\textbf{\ref{fig:pair_of_k_space_mri}}.d exemplifies artifacts caused by under-sampling and zero padding in the phase axis using a Gaussian mask (40\%).
 
@@
 
-		} & \subfloat[\textcolor{black}{\scriptsize{}fully sampled MRI}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_original.png}
+		} & \subfloat[\textcolor{black}{\scriptsize{}original }]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_original.png}
 
@@
 
-		} & \subfloat[\textcolor{black}{\scriptsize{}Zero-filled}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_zeroPadding.png}
+		} & \subfloat[\textcolor{black}{\scriptsize{}reconstructed}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_zeroPadding.png}
 }\tabularnewline
 \end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Under-sampling artifacts: the
-	arrows illustrate the sampling methodology}}
+	arrows illustrate Cartesian sampling}}
 \label{fig:pair_of_k_space_mri} 
@@
 
-\subsection{Objective}
-
-Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space.
-Given a sampling mask and a model $f$, defined by the set of parameters $\Theta$, our goal is to estimate the missing k-space samples such that:
+Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space, where $\odot$ denotes element-wise multiplication and $M_{p}$ is the sampling mask.
+Given a model $f$, defined by the set of parameters $\Theta$, our goal is to estimate the missing k-space samples such that:
 \begin{equation}
@@
 \end{equation}
-where $L\left(\cdot\right)$ is the loss function.
-While choosing the loss to be L2 norm is reasonable for natural images, for the k-space, which has different spatial features, this may not be enough.
-As mentioned in \cite{pathak2016context}, L2 minimization provides a blurry solution, results in a loss of fine details.
-Averaging the high frequency details in the k-space domain results in very poor reconstruction. In order to address this problem, we used the adversarial loss, based on GAN.
+where $L\left(\cdot\right)$ is a loss function.
+L2 loss is widely used for natural image reconstruction.
+However, as mentioned in \cite{pathak2016context}, L2 minimization provides a blurry solution, results in a loss of fine details.
+In our case, where spatial frequencies in the form of k-space are considered, using this loss alone may be inappropriate, resulting in poor reconstruction.
+To address this problem, we proposed using in addition an adversarial loss, based on GAN.
 
-We trained our model using the adversarial strategy, as described in \cite{goodfellow2014generative,radford2015unsupervised}. 
-This method is based on a generator $G$, which takes noise \textbf{$z$ }with uniform distribution \textbf{$p_{u}\left(z\right)$} as input and generates samples from the data distribution.
-A discriminator $D$ is trained to distinguish between ``real'' examples from the data and generated (``fake'') examples from $G.$ During the training process, we optimize $G$ to maximize the discriminator's probability of error.
-Simultaneously, $D$ is getting better and provides more
-accurate predictions.
+\subsection{K-space GAN}
+We train our model using an adversarial strategy, as described in \cite{goodfellow2014generative,radford2015unsupervised}. 
+This method is based on a generator $G$, which gets noise \textbf{$z$ }with uniform distribution \textbf{$p_{u}\left(z\right)$} as input and generates samples from the observed data distribution.
+A discriminator $D$ is trained to distinguish between ``true'' examples from the data and generated (``fake'') examples from $G.$ During the training process, we optimize $G$ to maximize the discriminator's probability of error.
+Simultaneously, $D$ is enhanced and provides more accurate predictions.
 
-Let $s_{0}$ denote a ``real'' k-space sample from the distribution $p_{r}\left(s_{0}\right)$. The following optimization process can be described by two-players min-max game:
+Let $s_{0}$ denote a true k-space sample from the distribution $p_{r}\left(s_{0}\right)$. The following optimization process can be described by two-players min-max value function $V(G,D)$:
 
 \begin{equation}
-\min_{G}\max_{D}\mathbb{E_{\mathrm{s_{0}\sim p_{r}\left(s_{0}\right)}}\mathrm{\log\left[D\left(x\right)\right]}}+\mathbb{E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(G(z)\right)\right]}}
+\min_{G}\max_{D}V(G,D) = \mathbb{E_{\mathrm{s_{0}\sim p_{r}\left(s_{0}\right)}}\mathrm{\log\left[D\left(x\right)\right]}}+\mathbb{E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(G(z)\right)\right]}}
 \end{equation}
@@
 
-\subsection{Network Architecture}
+\subsection{System Architecture}
 

### 2018-02-05 paper.tex
Update chart + statisticlly significat

@@
 
-In equilibrium, the generator $G$ is able to generate samples that look like the real data.
+In equilibrium, the generator $G$ is able to generate samples that look like the true data.
 In our case, $G$ estimates the missing k-space samples from a linear combination of the sampled data and a uniform noise with distribution $p_{u}\left(z\right)$.
@@
 
-%\begin{figure}[H]
-%	\centering{}\includegraphics[width=7.8cm,height=4cm]{include/grp1/chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
-%			architecture: $G$ and $D$ are the generator and discriminator networks,
-%			respectively. $F$ is a $2D$ IFFT operator.}}
-%\end{figure}
-
 \begin{figure}[H]
-	\centering{}\includegraphics[width=12.0cm,height=4cm]{include/grp2/system_chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
+	\centering{}\includegraphics[width=12.0cm,height=4.5cm]{include/grp2/system_chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
 			architecture: $G$ and $D$ are the generator and discriminator networks,
@@
 Results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}.
+The differences are statistically significant with p-values~$<0.0005$ for CS-MRI and Zero-filled for sampling factors 2.5 and 4, and also for IM-CNN-L2 with p-values~$<0.0001$ for sampling factor 6.
 
@@
 It quantifies the degradation caused by sampling artifacts based on pixels' inter-dependencies in the image. 
+%The SSIM between images $I_{\mbox{\tiny{REF}}}$ and $I_{\mbox{\tiny{REC}}}$ is calculated on a multiples sliding windows with size of $N\times N$ as follows:
+%\begin{equation}
+%\begin{array}{cc}
+%  SSIM(I_{\mbox{\tiny{REF}}},I_{\mbox{\tiny{REC}}}) = \frac{(2\mu_{I_{\mbox{\tiny{REF}}}}\mu_{I_{\mbox{\tiny{REC}}}} + c_1) (2\sigma_{I_{\mbox{\tiny{REF,REC}}}} + c_2)}{(\mu_{I_{\mbox{\tiny{REF}}}}^2 + \mu_{I_{\mbox{\tiny{REC}}}}^2 + c_1) (\sigma_{I_{\mbox{\tiny{REF}}}}^2) + \sigma_{I_{\mbox{\tiny{REC}}}}^2) + c_2} \\
+% second = 2\\
+% ohad
+%\end{array}
+%\end{equation}
+%Let $\mu_1,\mu_2$ denote the brain boundaries ext
 SSIM scores for different sampling factors, for all methods compared, are presented in~Table~\ref{tbl:SSIM_NO_MASK}.
@@
 As fore previous tests, our method achieves the best scores for all brain tissues and all sampling factors.
-{\color{red} Statistical significant values (~~) found for [1,2,3,4].}
+Statistical significant values (p-values~$<0.0005$) found for all methods using sampling factor of 2.5.
+In addition to the CS-MRI and Zero-filled, the differences are statistically significant with p-values~$<0.0001$ for CNN-L2 using sampling factor 4 and for IM-CNN-L2 using sampling factor 6.
 

### 2018-02-05 paper.tex
Update tammy - night Feb 2018

@@
 \end{equation}
+where, $z$ is a noise drawn from a uniform distribution $p_{u}\left(z\right)$.
 
-In equilibrium, the generator $G$ is able to generate samples that look like the true data.
-In our case, $G$ estimates the missing k-space samples from a linear combination of the sampled data and a uniform noise with distribution $p_{u}\left(z\right)$.
-An L2 fidelity constraint is added to the adversarial loss of the generator, as follows:
+In equilibrium, the generator $G$ imitates the true data, which is in our the missing k-space samples.
+The generator loss is a linear combination of L2 fidelity loss and an adversarial loss as follows:
 
@@
 \end{equation}
-where $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=1$ are hyperparameters tuned by a cross-validation process.
-The discriminator's input is the reconstructed MR image,\textbf{ }i.e.,\textbf{ }after IFFT.
-By that, we are integrating the reconstruction phase and optimize it in an end-to-end manner.
-In this work, we use the Wasserstein distance as the GAN loss function~\cite{arjovsky2017wasserstein}, which helps us to improve the training stability and provides better reconstruction compared to the classic GAN used in~\cite{shitrit2017accelerated}.
+where, $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=1$ are hyperparameters tuned by a cross-validation process.
+We choose to use the Wasserstein distance as the GAN loss function (WGAN)~\cite{arjovsky2017wasserstein}, which improves the training stability and provides better reconstruction compared to the classic GAN loss we used in our preliminary work~\cite{shitrit2017accelerated}.
 
 \subsection{System Architecture}
+The proposed framework is illustrated in~Figure \ref{fig:system}.
+\begin{figure}[H]
+	\centering{}\includegraphics[width=12.0cm,height=4.5cm]{include/grp2/system_chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
+			architecture: $G$ and $D$ are the generator and discriminator networks,
+			respectively. See text for details.}}
+\end{figure}
 
-The generator input is a two-channel image representing the real and the imaginary parts of the partially sampled k-space image, $s_{p}$.
-Each missing sample is initialized by uniform i.i.d.
-noise.
-The pixel $\left(i,j\right)$ in the generator input image is:
+The generator input is a two-channel representing the real and the imaginary parts of the partially sampled k-space image, $s_{p}$.
+Each missing sample $\left(i,j\right)$ is initialized by uniform i.i.d.
+noise as follows:
 \begin{equation}
@@
 
-Due to the combination of the adversarial and the fidelity loss, $G$ produces reasonable k-space samples from a given samples and noise distribution $p_{u}\left(z\right)$.
-In order to use the sampled data, $s_{p}$, and estimate only the missing samples we used a residual network \cite{he2016deep} as used in \cite{Oktay2016}, such that:
+$G$ produces reasonable k-space samples from a given samples and noise distribution $p_{u}\left(z\right)$.
+In order to utilize the remaining sampled data, $s_{p}$, and estimate only the missing samples we use a residual network \cite{he2016deep} as in \cite{Oktay2016}, such that:
 \begin{equation}
@@
 \end{equation}
-where $G_{out}$ is the generator output. Figure \ref{fig:system} describes our framework:
+where $G_{out}$ is the generator output.
+The discriminator's two-channel (real and imaginary) input is either the reconstructed or the true MR image obtained by IFFT of the generator's estimated or the original fully-sampled k-space data, respectively.
+By that, we are incorporating the IFFT into the network performing end-to-end optimization.
+The discriminator's output defines the WGAN loss.
 
-\begin{figure}[H]
-	\centering{}\includegraphics[width=12.0cm,height=4.5cm]{include/grp2/system_chart}\caption{\label{fig:system} \textcolor{black}{\footnotesize{}{}Framework
-			architecture: $G$ and $D$ are the generator and discriminator networks,
-			respectively.}}
-\end{figure}
-
-A common architecture is used for the discriminator, composed of convolutional layers, batch normalization, and leaky-ReLU as suggested in \cite{radford2015unsupervised}.
-For the generator, we compose a dedicated architecture based on multi-channel input for representing the real and imaginary components.
-Both architectures are shown in Figure \ref{fig:architectures}.\textbf{ }The training methodology is doing $k_{d}$ discriminator update steps for each generator single step.
+We use a standard discriminator architecture, composed of convolutional layers, batch normalization, and leaky-ReLU as suggested in \cite{radford2015unsupervised}.
+For the generator, we compose a dedicated architecture, detailed in Section~\ref{experiments_section}.
+Both the discriminator and the generator inputs are two-channel image for the real and imaginary components.
+Figure~\ref{fig:architectures} illustrates their architectures.
+During the training phase, $k_{d}$ discriminator update steps are carried out for every step of the generator.
+The training ends when the discriminator cannot accurately distinguish between the reconstructed (``fake'') and the true inputs.
 
@@
 	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Networks architecture.
-Both generator and discriminator input is a two-channel signal, real and imaginary.
-The number above each layer represents the output channels and all convolutional kernels are $3\times3$.}}
+Both the discriminator and the generator inputs are two-channel image for the real and imaginary components.
+The number above each layer represents the output channels.
+All convolutional kernels are $3\times3$.}}
 \label{fig:architectures} 

### 2018-02-07 paper.tex
Update paper, graphical abastarct

@@
 Spatial distances between adjacent slices of fetal MRI or fMRI, for example, are often as high as 0.5 centimeters.
-Therefore, a significant portion of the potential input is not conveyed through imaging.
+Therefore, a significant portion of the potential input is not covered through imaging.
 On the other hand, under-sampling in the x-y domain leads to aliasing, as predicted by the Nyquist sampling theorem.
@@
 %This, however, would require specified pulse programming.
-Recently different data driven, machine learning techniques were used for MRI acceleration. 
+Recently, different data driven machine learning techniques were used for MRI acceleration. 
 Ravishankar and Bresler~\cite{ravishankar2011mr} proposed a dictionary-based learning method, to exploit the sparsity of overlapping image patches emphasizing local structure, to reconstruct MRI from highly under-sampled k-space data.
 In~\cite{caballero2014dictionary}, this concept was extended using spatio-temporal patches for dynamic MRI reconstruction.
-Compressed manifold learning based on Laplacian eigenmaps, has been applied in~\cite{usman2014compressive} for respiratory motion estimation and in~\cite{bhatia2015fast} for cardiac MRI reconstruction.
+Compressed manifold learning based on Laplacian eigenmaps has been applied in~\cite{usman2014compressive} for respiratory motion estimation and in~\cite{bhatia2015fast} for cardiac MRI reconstruction.
 
@@
 The U-net output image is than enhanced by integrating its k-space domain with the originally acquired raw samples.
-U-net CNN has been also used in~\cite{sandinodeep} for dynamic MRI reconstruction.
+U-net CNN have been also used in~\cite{sandinodeep} for dynamic MRI reconstruction.
 The spatio-temporal characteristics of sequential MRI data was recently exploited using recurrent neural network (RNN) by~\cite{qin2017convolutional}.
@@
 To assess the clinical usability of the reconstructed images we perform an extended validation, composed of anatomical quantitative measurements.
-In addition to the common used PSNR and Structure Similarity Index (SSIM) we perform tissue segmentation and compare the results to those obtained by using the original fully-sampled images.
+In addition to the commonly used PSNR and Structure Similarity Index (SSIM) we perform tissue segmentation and compare the results to those obtained by using the original fully-sampled images.
 Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
 The proposed method outperforms all other tested methods in all evaluation metrics.
-Moreover, compared to the widely used CS-MRI, the proposed method is faster in two orders of magnitude.
+Moreover, compared to the widely used CS-MRI, the proposed method is faster by two orders of magnitude.
 In fact, it can work in real time, and is therefore practical for routine uses.
 
-The rest of the paper is organized as follows.
-Section~\ref{method_section} provides a brief background on MRI acquisition and introduce the network architecture as well the training methodology.
+The rest of the paper is organized as follows: Section~\ref{method_section} provides a brief background on MRI acquisition and introduce the network architecture as well as the training methodology.
 Section~\ref{experiments_section} presents the experimental results.
@@
 In our case, where spatial frequencies in the form of k-space are considered, using this loss alone may be inappropriate, resulting in poor reconstruction.
-To address this problem, we proposed using in addition an adversarial loss, based on GAN.
+To address this problem, we propose using in addition an adversarial loss, based on a GAN.
 
@@
 \begin{equation}
-\min_{G}\max_{D}V(G,D) = \mathbb{E_{\mathrm{s_{0}\sim p_{r}\left(s_{0}\right)}}\mathrm{\log\left[D\left(x\right)\right]}}+\mathbb{E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(G(z)\right)\right]}}
+\min_{G}\max_{D}V(G,D) = \mathbb{E_{\mathrm{s_{0}\sim p_{r}\left(s_{0}\right)}}\mathrm{\log\left[D\left(s_{0}\right)\right]}}+\mathbb{E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(G(z)\right)\right]}}
 \end{equation}
@@
 
-In equilibrium, the generator $G$ imitates the true data, which is in our the missing k-space samples.
+In equilibrium, the generator $G$ imitates the true data, which is in our case the missing k-space samples.
 The generator loss is a linear combination of L2 fidelity loss and an adversarial loss as follows:
@@
 
-The generator input is a two-channel representing the real and the imaginary parts of the partially sampled k-space image, $s_{p}$.
+The generator's input is a two-channel signal representing the real and the imaginary parts of the partially sampled k-space image, $s_{p}$.
 Each missing sample $\left(i,j\right)$ is initialized by uniform i.i.d.
@@
 where $G_{out}$ is the generator output.
-The discriminator's two-channel (real and imaginary) input is either the reconstructed or the true MR image obtained by IFFT of the generator's estimated or the original fully-sampled k-space data, respectively.
+The discriminator's two-channel (real and imaginary) input is either the reconstructed MR image obtained by IFFT of the generator's estimated or the true MR image obtained by IFFT of the original fully-sampled k-space data.
 By that, we are incorporating the IFFT into the network performing end-to-end optimization.
@@
 The training data consists of 500 $3D$ brain MRI (T1-weighed) scans of different patients from the IXI dataset\footnote{\url{http://brain-development.org/ixi-dataset/}}.
-The data has been acquired by three MR machines, Philips 1.5T, 3T and GE 1.5T using different imaging protocols.
+The data was acquired by three MR machines, Philips 1.5T, 3T and GE 1.5T using different imaging protocols.
 From each $3D$ volume we extract 93 $2D$ saggital slices.
@@
 In order to create k-space images for training, inverse orthonormal
-2D FFT is applied to the fully-sampled MR images. 
-Different from our preliminary work~\cite{shitrit2017accelerated}, which employed 1D Cartesian sampling mask along the phase axis, here, we perform k-space sampling using $2D$ random Gaussian mask.
-By this, we exploit the sparsity in both phase and frequency dimensions and therefore able to accommodate higher sampling factors (Figure~\ref{fig:sampling_masks}).
+2D FFT was applied to the fully-sampled MR images. 
+Unlike our preliminary work~\cite{shitrit2017accelerated}, which employed 1D Cartesian sampling mask along the phase axis, here, we perform k-space sampling using $2D$ random Gaussian mask.
+By this, we exploit the sparsity in both phase and frequency dimensions and are therefore able to accommodate higher sampling factors (Figure~\ref{fig:sampling_masks}).
 MRI reconstruction is performed using 40\%, 25\% and 16.6\% of the original k-space data.
@@
 All CONV layer's kernel size is $3\times3$.
-All weights was initialized by Xavier \cite{glorot2010understanding}.
-We used RMSprop~\cite{tieleman2012lecture} solver with fixed learning rate of $5\mathrm{e}{-6}$ and set $k_{d}$ to 1.
+All weights were initialized using Xavier \cite{glorot2010understanding}.
+We used the RMSprop~\cite{tieleman2012lecture} solver with a fixed learning rate of $5\mathrm{e}{-6}$ and set $k_{d}$ to 1.
 
@@
 In addition, we tested two other networks.
-To asses the use of adversarial loss, we trained a k-space generator, with the same architecture as the proposed method, with only L2 loss (CNN-L2).
+To asses the use of an adversarial loss, we trained a k-space generator, with the same architecture as the proposed method, with only a L2 loss (CNN-L2).
 We also implemented the method proposed in~\cite{hyun2017deep} and constructed a network IM-CNN-L2, which is applied directly to the image space rather than the k-space.
@@
 Note that the proposed method outperforms the others.
-To support it, we also calculated the Two-sample t-Test for the table's scores.
+To support this, we also calculated the Two-sample t-Test for the table's scores.
 The differences are statistically significant (p-values~$<0.005$) for all pairwise comparisons between the results of our method and the others.
@@
 This may significantly affect diagnostic usability.
-We therefore further compared segmentation quality between the fully-sampled and the reconstruction images.
+We therefore further compare segmentation quality between the fully-sampled and the reconstruction images.
 Results of the analysis obtained for our method and all others are presented next.
@@
 Segmentation results were compared to those obtained for the original fully-sampled scans.
-We believe that these comparisons are indicative to the diagnostic quality of the reconstructed MRIs as tissue segmentation (WM, GM and CSF) plays a key role in clinical brain analysis.
+We believe that these comparisons are indicative of the diagnostic quality of the reconstructed MRIs as tissue segmentation (WM, GM and CSF) plays a key role in clinical brain analysis.
 %Segmentation compatibility demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
@@
 Dice scores for all tested methods and sampling factors are presented in~Table~\ref{tbl:DICE}.
-As fore previous tests, our method achieves the best scores for all brain tissues and all sampling factors.
+As for previous tests, our method achieves the best scores for all brain tissues and all sampling factors.
 Statistical significant values (p-values~$<0.0005$) found for all methods using sampling factor of 2.5.
@@
 The third row presents the corresponding brain extraction.
-The forth row presents the automatic tissue segmentation where, dark blue is used for WM, blue for GM and light blue for CSF.
+The fourth row presents the automatic tissue segmentation where, dark blue is used for WM, blue for GM and light blue for CSF.
 Note that, MRIs reconstructed by using the suggested adversarial method have stronger contrast and no significant aliasing or artifacts.
@@
 The inter-play between the generator and the discriminator plays a key role here.
-The generator is trained directly on the k-space, thus avoiding aliasing correction (due to under-sampling) as done in other methods.
+The generator is trained directly on the k-space, thus avoiding aliasing correction (due to under-sampling) as is done in other methods.
 Instead, the k-space distribution, and not its IFFT, is learned and generated.
@@
 This allows anatomically meaningful reconstruction with high fidelity to the original scan.
-Extensive comparative analysis shows that our method outperforms all other tested MRI reconstruction methods (CS and other DNN-based) for various quality metrics, showing more robustness for high acceleration factors.
+Extensive comparative analysis shows that our method outperforms all other tested MRI reconstruction methods (CS and other DNN-based) for various quality metrics, showing more robustness to high acceleration factors.
 

### 2018-02-17 paper.tex
English editing

@@
 This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples.
-The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to a fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR).
-Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from large publicly available dataset, where only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
+The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR).
+Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from a large publicly available dataset, where only 40\%, 25\%, and 16.6\% of the raw samples of each scan are used.
 To assess the clinical usability of the reconstructed images we also performed tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
@@
 The discretized RF output is presented in a Fourier space
-(called K-space), where the x-axis is refers to the frequency and the y-axis to the phase.
-An inverse fast Fourier transform (IFFT) of the K-space is then used for generating anatomically meaningful MRI scans.
-Figure \ref{fig:pair_of_k_space_mri} presents K-space traversal patterns used in conventional imaging.
+(called k-space), where the x-axis refers to the frequency and the y-axis to the phase.
+An inverse fast Fourier transform (IFFT) of the k-space is then used for generating anatomically meaningful MRI scans.
+Figure \ref{fig:pair_of_k_space_mri} presents k-space traversal patterns used in conventional imaging.
 Each row of the k-space is acquired after one RF excitation pulse.
@@
 Usually, several scans of different modalities or a sequence of scans are acquired such that the overall scan time is much longer.
-Lengthy imaging process reduces patient comfort and is more vulnerable to motion artifacts.
+The lengthy imaging process reduces patient comfort and is more vulnerable to motion artifacts.
 In cases where motion is inevitable, e.g., fetal MRI, cardiac cine, and lungs imaging, scan time must be significantly shortened, otherwise the produced images might be useless.
@@
 A straight forward reduction of the scan time can be obtained by sampling fewer slices, thus reducing the spatial resolution in the z-axis.
-Spatial distances between adjacent slices of fetal MRI or fMRI, for example, are often as high as 0.5 centimeters.
+Spatial distances between adjacent slices of fetal MRI or fMRI, for example, are often as large as 0.5 centimeters.
 Therefore, a significant portion of the potential input is not covered through imaging.
@@
 The underlying assumption is that the undersampling is random, such that the zero-filled Fourier reconstruction exhibits incoherent artifacts that behave similarly to additive random noise.
-The smooth reconstruction obtained by the CS, may result in a loss of noise-like texture that can be anatomically meaningful.
+The smooth reconstruction obtained by the CS may result in a loss of noise-like texture that can be anatomically meaningful.
 
@@
 
-Deep neural networks (DNN) allow to implicitly learn prior information from large datasets.
+Deep neural networks (DNN) allow implicitly learning prior information from large datasets.
 This has been exploited in recent works for MRI reconstruction from sub-sampled data.
-A convolutional neural network (CNN) was introduced in~\cite{wang2016accelerating} to learn the mapping between zero-filled and fully-sampled MRI.
+A convolutional neural network (CNN) was introduced in~\cite{wang2016accelerating} to learn the mapping between zero-filled and fully-sampled MRIs.
 In~\cite{Oktay2016}, MRI acceleration by super-resolution (SR) concepts was introduced.
-One of the key ideas is a siamese CNN structure that allows to receive multiple inputs acquired from different viewing planes.
+One of the key ideas is a siamese CNN structure that allows receiving multiple inputs acquired from different viewing planes.
 Improved low-resolution (LR) high-resolution (HR) mapping was obtained by residual architecture.
 A multi-scale residual network, also known as U-net~\cite{ronneberger2015u}, was used in~\cite{lee2017deep} to address the CS optimization, formulated as a residual regression problem.
-Hayun at el.~\cite{hyun2017deep}, applied U-net to perform anti-aliasing of MRI generated from sub-sampled k-space.
-The U-net output image is than enhanced by integrating its k-space domain with the originally acquired raw samples.
+Hayun et el.~\cite{hyun2017deep}, applied U-net to perform anti-aliasing of an MRI generated from sub-sampled k-space.
+The U-net output image is then enhanced by integrating its k-space domain with the originally acquired raw samples.
 U-net CNN have been also used in~\cite{sandinodeep} for dynamic MRI reconstruction.
@@
 In contrast, here, the generator is used for reconstruction of the entire k-space grid from under-sampled data.
-Its loss is a combination of an adversarial loss, calculated on the image domain, based on the discriminator output, and a fidelity loss with respect to the fully sampled k-space.
+Its loss is a combination of an adversarial loss, calculated on the image domain based on the discriminator output, and a fidelity loss with respect to the fully sampled k-space.
 Unlike~\cite{hyun2017deep}, the entire process, including the IFFT, is carried out and optimized in an end-to-end manner by the proposed GAN architecture.
@@
 
-We compare the proposed method reconstructions to those obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling.
-In addition, for comparison, we test two other networks: 1.
-CNN-L2 - a k-space generator (with same architecture as the proposed method) trained with only L2 loss.
-2.
-IM-CNN-L2 - a network which performs on the image-space and is optimized to remove the artifacts caused by under-sampling and zero padding.
+We compare the proposed method reconstructions to those obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and zero-filling.
+In addition, for comparison, we tested two other networks: 1.
+CNN-L2 - a k-space generator (with same architecture as the proposed method) trained with only L2 loss; 2.
+IM-CNN-L2 - a network that performs on the image-space and is optimized to remove the artifacts caused by under-sampling and zero padding.
 The method is applied to the Information eXtraction from Images (IXI) dataset, which is a large publicly available dataset, including 3T and 1.5T scans.
-Raw data is down-sampled such that only 40\%, 25\% and 16.6\% of the raw samples of each scan are used.
+Raw data is down-sampled such that only 40\%, 25\%, and 16.6\% of the raw samples of each scan are used.
 To assess the clinical usability of the reconstructed images we perform an extended validation, composed of anatomical quantitative measurements.
-In addition to the commonly used PSNR and Structure Similarity Index (SSIM) we perform tissue segmentation and compare the results to those obtained by using the original fully-sampled images.
+In addition to the commonly used PSNR and Structure Similarity Index (SSIM), we perform tissue segmentation and compare the results to those obtained by using the original fully-sampled images.
 Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
@@
 
-The rest of the paper is organized as follows: Section~\ref{method_section} provides a brief background on MRI acquisition and introduce the network architecture as well as the training methodology.
+The rest of the paper is organized as follows: Section~\ref{method_section} provides a brief background on MRI acquisition and introduces the network architecture as well as the training methodology.
 Section~\ref{experiments_section} presents the experimental results.
@@
 \subsection{Notations and Problem Definition}
-Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained by IFFT of the complex k-space signal $s_{0}$ i.e, 
+Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained by IFFT of the complex k-space signal $s_{0}$, i.e., 
 \begin{equation}
@@
 L2 loss is widely used for natural image reconstruction.
-However, as mentioned in \cite{pathak2016context}, L2 minimization provides a blurry solution, results in a loss of fine details.
+However, as mentioned in \cite{pathak2016context}, L2 minimization provides a blurry solution, resulting in a loss of fine details.
 In our case, where spatial frequencies in the form of k-space are considered, using this loss alone may be inappropriate, resulting in poor reconstruction.
@@
 \end{equation}
-where, $z$ is a noise drawn from a uniform distribution $p_{u}\left(z\right)$.
+where $z$ is a noise drawn from a uniform distribution $p_{u}\left(z\right)$.
 
@@
 \end{equation}
-where, $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=1$ are hyperparameters tuned by a cross-validation process.
+where $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=1$ are hyperparameters tuned by a cross-validation process.
 We choose to use the Wasserstein distance as the GAN loss function (WGAN)~\cite{arjovsky2017wasserstein}, which improves the training stability and provides better reconstruction compared to the classic GAN loss we used in our preliminary work~\cite{shitrit2017accelerated}.
@@
 
-The training data consists of 500 $3D$ brain MRI (T1-weighed) scans of different patients from the IXI dataset\footnote{\url{http://brain-development.org/ixi-dataset/}}.
-The data was acquired by three MR machines, Philips 1.5T, 3T and GE 1.5T using different imaging protocols.
-From each $3D$ volume we extract 93 $2D$ saggital slices.
+The training data consists of 500 3D brain MRI (T1-weighted) scans of different patients from the IXI dataset.\footnote{\url{http://brain-development.org/ixi-dataset/}} The data was acquired by three MR machines, Philips 1.5T, 3T and GE 1.5T using different imaging protocols.
+From each 3D volume we extracted 93 2D saggital slices.
 All slices were interpolated to $256\times256$ pixels.
-We used $37.2k$ $(80\%)$ 2D slices for training and $9.3k$ $(20\%)$ for testing (100 $3D$ volumes).
+We used $37.2k$ $(80\%)$ 2D slices for training and $9.3k$ $(20\%)$ for testing (100 3D volumes).
 In order to create k-space images for training, inverse orthonormal
 2D FFT was applied to the fully-sampled MR images. 
-Unlike our preliminary work~\cite{shitrit2017accelerated}, which employed 1D Cartesian sampling mask along the phase axis, here, we perform k-space sampling using $2D$ random Gaussian mask.
+Unlike our preliminary work~\cite{shitrit2017accelerated}, which employed a 1D Cartesian sampling mask along the phase axis; here, we perform k-space sampling using a 2D random Gaussian mask.
 By this, we exploit the sparsity in both phase and frequency dimensions and are therefore able to accommodate higher sampling factors (Figure~\ref{fig:sampling_masks}).
-MRI reconstruction is performed using 40\%, 25\% and 16.6\% of the original k-space data.
+MRI reconstruction is performed using 40\%, 25\%, and 16.6\% of the original k-space data.
 %Data augmentation is created by random offsets of raw images (prior to the IFFT) and k-space flipping.
@@
 The discriminator is composed of $4$ blocks of CONV-Pool-BatchNorm-LReLU with output channels $8,16,32,16$ and one fully-connected layer.
-All CONV layer's kernel size is $3\times3$.
+All CONV layers' kernel size is $3\times3$.
 All weights were initialized using Xavier \cite{glorot2010understanding}.
@@
 
-We compared the proposed method reconstructions to those obtained by using a conventional compressed sensing method-CS-MRI \cite{lustig2007sparse} and Zero-filling.
+We compared the proposed method reconstructions to those obtained by using a conventional compressed sensing method-CS-MRI \cite{lustig2007sparse} and zero-filling.
 In addition, we tested two other networks.
-To asses the use of an adversarial loss, we trained a k-space generator, with the same architecture as the proposed method, with only a L2 loss (CNN-L2).
+To assess the use of an adversarial loss, we trained a k-space generator, with the same architecture as the proposed method, with only an L2 loss (CNN-L2).
 We also implemented the method proposed in~\cite{hyun2017deep} and constructed a network IM-CNN-L2, which is applied directly to the image space rather than the k-space.
@@
 
-To demonstrate the clinical usability of the reconstructed images we perform an extended validation, composed of anatomical quantitative measurements.
-In addition to the common used PSNR and Structure Similarity Index (SSIM)~\cite{wang2004image} metrics, we perform tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
+To demonstrate the clinical usability of the reconstructed images we performed an extended validation, composed of anatomical quantitative measurements.
+In addition to the commonly used PSNR and Structure Similarity Index (SSIM)~\cite{wang2004image} metrics, we performed tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
 The segmentation compatibility is measured in terms of Dice scores and Hausdorff distances.
@@
 Note that the proposed method outperforms the others.
-To support this, we also calculated the Two-sample t-Test for the table's scores.
+To support this, we also calculated the two-sample t-Test for the table's scores.
 The differences are statistically significant (p-values~$<0.005$) for all pairwise comparisons between the results of our method and the others.
@@
 An additional validation of our model is performed by calculating the PSNR measure on different brain tissues.
-We applied the commonly used FAST~\cite{zhang2001segmentation} image segmentation algorithm, on the original fully-sampled MR image and then used it for calculating the masked-PSNR on gray matter (GM), white matter (WM) and the Cerebrospinal Fluid (CSF).
+We applied the commonly used FAST~\cite{zhang2001segmentation} image segmentation algorithm on the original fully-sampled MR image and then used it for calculating the masked-PSNR on gray matter (GM), white matter (WM), and the Cerebrospinal Fluid (CSF).
 Results are presented in~Table~\ref{tbl:PSNR_WITH_MASK}.
-The differences are statistically significant with p-values~$<0.0005$ for CS-MRI and Zero-filled for sampling factors 2.5 and 4, and also for IM-CNN-L2 with p-values~$<0.0001$ for sampling factor 6.
+The differences are statistically significant with p-values~$<0.0005$ for CS-MRI and zero-filled for sampling factors 2.5 and 4, and also for IM-CNN-L2 with p-values~$<0.0001$ for sampling factor 6.
 
@@
 
-We next used SSIM, which is a full reference metric, and is considered as a perception-based model, to measure the similarity between the original fully-sampled images and the reconstructed ones.
+We next used SSIM, which is a full reference metric, and is considered a perception-based model, to measure the similarity between the original fully-sampled images and the reconstructed ones.
 It quantifies the degradation caused by sampling artifacts based on pixels' inter-dependencies in the image. 
@@
 
-Let $C_1,C_2\in R^2$ denote the brain boundaries extracted by the BET algorithm, using the original and the reconstructed scans respectively. The MHD between $C_1$ and $C_2$ is:
+Let $C_1,C_2\in R^2$ denote the brain boundaries extracted by the BET algorithm, using the original and the reconstructed scans, respectively. The MHD between $C_1$ and $C_2$ is:
 
@@
 \end{equation}
-where $\sigma_1,\sigma_2$ are points on the contours $C_1,C_2$ respectively (Figure~\ref{fig:brain_extraction}.c) and $|C_i|,~i=1,2$ are the respective cardinalities.
+where $\sigma_1,\sigma_2$ are points on the contours $C_1,C_2$, respectively (Figure~\ref{fig:brain_extraction}.c) and $|C_i|,~i=1,2$, are the respective cardinalities.
 MHD values for all tested methods and sampling ratios are presented in~Table~\ref{tbl:MHD}.
-The MHD results obtained by our methods are better than all others and are significant (p-values~$<0.0001$) for CS-MRI and Zero-filled.
+The MHD results obtained by our methods are better than all others and are significant (p-values~$<0.0001$) for CS-MRI and zero-filled.
 
@@
 \subsection{Brain Segmentation}
-We next tested and compared segmentation quality applying brain tissue partitioning algorithm (FAST \cite{zhang2001segmentation}) to the reconstructed images.
+We next tested and compared segmentation quality applying a brain tissue partitioning algorithm (FAST \cite{zhang2001segmentation}) to the reconstructed images.
 Segmentation results were compared to those obtained for the original fully-sampled scans.
-We believe that these comparisons are indicative of the diagnostic quality of the reconstructed MRIs as tissue segmentation (WM, GM and CSF) plays a key role in clinical brain analysis.
+We believe that these comparisons are indicative of the diagnostic quality of the reconstructed MRIs as tissue segmentation (WM, GM, and CSF) plays a key role in clinical brain analysis.
 %Segmentation compatibility demonstrate the quality of the proposed MRI reconstruction with respect to other methods.
@@
 \end{equation}
-Dice scores are between zero to one where one indicates complete overlap between the tested segments.
+Dice scores are between zero and one, where one indicates complete overlap between the tested segments.
 Therefore, higher dice scores imply higher compatibility between reconstructed and original images.
@@
 As for previous tests, our method achieves the best scores for all brain tissues and all sampling factors.
-Statistical significant values (p-values~$<0.0005$) found for all methods using sampling factor of 2.5.
-In addition to the CS-MRI and Zero-filled, the differences are statistically significant with p-values~$<0.0001$ for CNN-L2 using sampling factor 4 and for IM-CNN-L2 using sampling factor 6.
+Statistically significant values (p-values~$<0.0005$) were found for all methods using sampling factor of 2.5.
+In addition to the CS-MRI and zero-filled, the differences are statistically significant with p-values~$<0.0001$ for CNN-L2 using sampling factor 4 and for IM-CNN-L2 using sampling factor 6.
 
@@
 
-	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice score for different sampling ratios}{\footnotesize{}\label{tbl:DICE}}}
+	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice scores for different sampling ratios}{\footnotesize{}\label{tbl:DICE}}}
 
 \end{table}
-MR reconstruction results for factor 6~(16.66\%) as well as their respective brain segmentation results are visually presented in Figure~\ref{fig:example_factor_6}~for a single representative scan.
-The left most column corresponds to the original image and columns 2-5 correspond to the reconstructed images using Zero-filled, CS-MRI, IM-CNN-L2 and the proposed method, respectively.
+MR reconstruction results for factor 6~(16.66\%) as well as their respective brain segmentation results are visually presented in Figure~\ref{fig:example_factor_6} for a single representative scan.
+The left most column corresponds to the original image and columns 2-5 correspond to the reconstructed images using Zero-filled, CS-MRI, IM-CNN-L2, and the proposed method, respectively.
 The first row presents a $2D$ slice of the original and the reconstructed MRIs.
@@
 The fourth row presents the automatic tissue segmentation where, dark blue is used for WM, blue for GM and light blue for CSF.
-Note that, MRIs reconstructed by using the suggested adversarial method have stronger contrast and no significant aliasing or artifacts.
-In addition the brain extraction and tissue segmentation results are more compatible with those obtained from the original fully-sampled MRIs.
-Additional examples of different cases, using sampling factors of 4~(25\%) and 2.5~(40\%) are shown in Figures~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}, respectively.
+Note that MRIs reconstructed using the suggested adversarial method have stronger contrast and no significant aliasing or artifacts.
+In addition, the brain extraction and tissue segmentation results are more compatible with those obtained from the original fully-sampled MRIs.
+Additional examples of different cases, using sampling factors of 4~(25\%), and 2.5~(40\%) are shown in Figures~\ref{fig:example_factor_4},~\ref{fig:example_factor_2.5}, respectively.
 
@@
 Instead, the k-space distribution, and not its IFFT, is learned and generated.
-Moreover, combining both adversarial and fidelity loss in the DNN training, the method suggested provides high PSNR reconstructions for large and diverse brain MRI dataset acquired by different MRI machines (1.5T and 3.T) and different imaging protocols.
+Moreover, combining both adversarial and fidelity loss in the DNN training, the method suggested provides high PSNR reconstructions for large and diverse brain MRI datasets acquired by different MRI machines (1.5T and 3.T) and different imaging protocols.
 
@@
 Recently, deep learning methods, capable of learning imaging samples distribution from training datasets, were shown to obtain reconstruction with comparable or even higher quality.
-The strength of the proposed DNN is three-fold, combining direct k-space reconstruction, GAN architecture and end-to-end optimization.
+The strength of the proposed DNN is three-fold, combining direct k-space reconstruction, GAN architecture, and end-to-end optimization.
 This allows anatomically meaningful reconstruction with high fidelity to the original scan.
@@
 
-Assessing clinical usability of the reconstructed data takes a considerable part in the quality analysis performed as part of this research.
-We choose to test it by using standard tissue segmentation measures (such as Dice and MHD), as we argue that compatibility of the extracted brain regions with those obtained by using the original fully-sampled MRIs indicate fine detail reconstructions which have apparent diagnostic significance.
+Assessing clinical usability of the reconstructed data is takes a considerable part in the quality analysis performed as part of this research.
+We chose to test it by using standard tissue segmentation measures (such as Dice and MHD), as we argue that compatibility of the extracted brain regions with those obtained by using the original fully-sampled MRIs indicate fine detail reconstructions that have apparent diagnostic significance.
 
 Nevertheless, pathological cases were not considered in this study and to the best of our knowledge are seldom addressed.
-We believe that high quality reconstruction in the presence of brain atrophies is the true success criteria.
+We believe that high quality reconstruction in the presence of brain atrophies is the true success criterion.
 In fact, addressing this challenge and measuring performances in this sense, should be the gold standard in future benchmarks.
@@
 \subsection{Acknowledgment}
-This study was partially supported by The Israel Science Foundation (1638/16); The Israel Defense Forces (IDF) Medical Corps and Directorate of Defense Research \& Development, Israeli Ministry of Defense (IMOD DDR\&D); The Israeli ministry of science, technology and space (63551).
+This study was partially supported by The Israel Science Foundation (1638/16); The Israel Defense Forces (IDF) Medical Corps and Directorate of Defense Research \& Development, Israeli Ministry of Defense (IMOD DDR\&D); Israel Ministry of Science, Technology and Space (63551).
 %This research is partially supported by the Israel Science Foundation (T.R.R. 1638/16 ) and the IDF Medical Corps (T.R.R.)

### 2018-02-19 paper.tex
Update title

@@
 
-\title{Accelerated Magnetic Resonance Imaging by Adversarial Neural Network}
+\title{Accelerated Magnetic Resonance Imaging by Generative Adversarial Neural Networks}
 
@@
 We introduce a practical, software-only framework, based on deep learning, for accelerating MRI acquisition, while maintaining anatomically meaningful imaging.
-This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples.
+This is accomplished by partial MRI sampling, while using an generative adversarial neural network to directly estimate the missing k-space samples.
 The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR).
@@
 PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image.
-Quantitative evaluation is presented in~Table~\ref{tbl:PSNR_NO_MASK} and a graphical visualization in ~Figure~\ref{fig:error_psnr_errorbar}.
+Quantitative evaluation is presented in~Table~\ref{tbl:PSNR_NO_MASK} and a graphical visualization in~Figure~\ref{fig:error_psnr_errorbar}.
 The PSNR is calculated for the entire image without masking.
@@
 \caption{PSNR without masking error-bar}
-\end{figure}\label{fig:error_psnr_errorbar}
+\label{fig:error_psnr_errorbar}
+\end{figure}
 
